### 2025-01-20 论文/PAPER.tex
提交了论文模板

%% 美赛模板：正文部分

\documentclass[12pt]{article}  % 官方要求字号不小于 12 号，此处选择 12 号字体

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[1234567]{easymcm}  % 载入 EasyMCM 模板文件
\problem{A}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包

\title{An MCM Paper Made by Team 1234567}  % 标题

% 如需要修改题头（默认为 MCM/ICM），请使用以下命令（此处修改为 MCM）
%\renewcommand{\contest}{MCM}

% 文档开始
\begin{document}

% 此处填写摘要内容
\begin{abstract}
	Hello, MCM.

    Here is the abstract of your paper.

    Firstly, that is ...

    Secondly, that is ...

    Finally, that is ...

$F(\omega) = \int_{-\infty}^{\infty} f(t) e^{-i \omega t} \, dt$

$f(t) = \frac{1}{2\pi} \int_{-\infty}^{\infty} F(\omega) e^{i \omega t} \, d\omega$

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
    % \vspace{5pt}
    % \textbf{Keywords}: MATLAB, mathematics, LaTeX.

\end{abstract}

\maketitle  % 生成 Summary Sheet
\tableofcontents  % 生成目录

% 正文开始
\section{Introduction}
\subsection{Problem Background}
Here is the problem background ...

Two major problems are discussed in this paper, which are:
\begin{itemize}
    \item Doing the first thing.
    \item Doing the second thing.
\end{itemize}

\subsection{Literature Review}
A literatrue\cite{1} say something about this problem ...

\subsection{Our work}
We do such things ...

\begin{enumerate}[\bfseries 1.]
    \item We do ...
    \item We do ...
    \item We do ...
\end{enumerate}

\section{Preparation of the Models}
\subsection{Assumptions}

\subsection{Notations}
The primary notations used in this paper are listed in Table \ref{tb:notation}.

% 三线表示例
\begin{table}[!htbp]
\begin{center}
\caption{Notations}
\begin{tabular}{cl}
	\toprule
	\multicolumn{1}{m{3cm}}{\centering Symbol}
	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
	\midrule
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	\bottomrule
\end{tabular}\label{tb:notation}
\end{center}
\end{table}

\section{The Models}
\subsection{Model 1}
\subsubsection{Details about Model 1}
The detail can be described by equation \eqref{eq:heat}:
\begin{equation}\label{eq:heat}
\frac{\partial u}{\partial t} - a^2 \left( \frac{\partial^2 u}{\partial x^2} + \frac{\partial^2 u}{\partial y^2} + \frac{\partial^2 u}{\partial z^2} \right) = f(x, y, z, t)
\end{equation}

\subsection{Model 2}
\subsubsection{Conclusion of Model 2}
The results are shown in Figure \ref{fig:result}, where $t$ denotes the time in seconds, and $c$ refers to the concentration of water in the boiler.

\begin{figure}[htbp]
\centering
\includegraphics[width=.8\textwidth]{water.png}
\caption{The result of Model 2}\label{fig:result}
\end{figure}

\clearpage
\subsubsection{Commetary on Model 2}
The instance of long and wide tables are shown in Table \ref{tb:longtable}.

% 长表格示例，更多用法请参考 longtable 宏包文档
% 以下环境及对应参数可实现表格内的自动换行与表格的自动断页
% 您也可以选择自行载入 tabularx 宏包，并通过 X 参数指定对应列自动换行
\begin{longtable}{ p{4em} p{14em} p{14em} }
\caption{Basic Information about Three Main Continents (scratched from Wikipedia)}
\label{tb:longtable}\\
\toprule
Continent & Description & Information \\
\midrule
Africa & Africa Continent is surrounded by the Mediterranean Sea to the
north, the Isthmus of Suez and the Red Sea to the northeast, the Indian
Ocean to the southeast and the Atlantic Ocean to the west. &
At about 30.3 million km$^2$ including adjacent islands, it covers 6\%
of Earth's total surface area and 20\% of its land area. With 1.3
billion people as of 2018, it accounts for about 16\% of the world's
human population. \\
\midrule
Asia & Asia is Earth's largest and most populous continent which
located primarily in the Eastern and Northern Hemispheres.
It shares the continental landmass of Eurasia with the continent
of Europe and the continental landmass of Afro-Eurasia with both
Europe and Africa. &
Asia covers an area of 44,579,000 square kilometres, about 30\%
of Earth's total land area and 8.7\% of the Earth's total surface
area. Its 4.5 billion people (as of June 2019) constitute roughly
60\% of the world's population. \\
\midrule
Europe & Europe is a continent located entirely in the Northern
Hemisphere and mostly in the Eastern Hemisphere. It comprises the
westernmost part of Eurasia and is bordered by the Arctic Ocean to
the north, the Atlantic Ocean to the west, the Mediterranean Sea to
the south, and Asia to the east. &
Europe covers about 10,180,000 km$^2$, or 2\% of the Earth's surface
(6.8\% of land area), making it the second smallest
continent. Europe had a total population of about 741 million (about
11\% of the world population) as of 2018. \\
\bottomrule
\end{longtable}

Figure \ref{fig:subfigures} gives an example of subfigures. Figure \ref{subfig:left} is on the left, and Figure \ref{subfig:right} is on the right.

% 子图（多图并列）示例，更多用法请参考 subfigure 宏包文档
% 如果您只希望几张图并列，不需要额外的 caption，那么在 figure 环境中
% 连续插入总宽度不超过 \textwidth 的多个 \includegraphics 命令即可
\begin{figure}[htbp]
\centering
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{water.png}
\caption{Image on the left}\label{subfig:left}
\end{subfigure}
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{water.png}
\caption{Image on the right}\label{subfig:right}
\end{subfigure}
\caption{Two images}\label{fig:subfigures}
\end{figure}

\section{Strengths and Weaknesses}
\subsection{Strengths}
\begin{itemize}
    \item First one...
    \item Second one ...
\end{itemize}

\subsection{Weaknesses}
\begin{itemize}
    \item Only one ...
 \end{itemize}

% 以下为信件/备忘录部分，不需要可自行去掉
% 如有需要可将整个 letter 环境移动到文章开头或中间
% 请在第二个花括号内填写标题，如「信件」（Letter）或「备忘录」（Memorandum）
\begin{letter}{Memorandum}
\begin{flushleft}  % 左对齐环境，无首行缩进
\textbf{To:} Heishan Yan\\
\textbf{From:} Team 1234567\\
\textbf{Date:} October 1st, 2019\\
\textbf{Subject:} A better choice than MS Word: \LaTeX
\end{flushleft}

In the memo, we want to introduce you an alternate typesetting program to the prevailing MS Word: \textbf{\LaTeX}. In fact, the history of \LaTeX\ is even longer than that of MS Word. In 1970s, the famous computer scientist Donald Knuth first came out with a typesetting program, which named \TeX\ \ldots

Firstly, \ldots

Secondly, \ldots

Lastly, \ldots

According to all those mentioned above, it is really worth to have a try on \LaTeX! 
\end{letter}

% 参考文献，此处以 MLA 引用格式为例
\begin{thebibliography}{99}
\bibitem{1} Einstein, A., Podolsky, B., \& Rosen, N. (1935). Can quantum-mechanical description of physical reality be considered complete?. \emph{Physical review}, 47(10), 777.
\bibitem{2} \emph{A simple, easy \LaTeX\ template for MCM/ICM: EasyMCM}. (2018). Retrieved December 1, 2019, from\url{https://www.cnblogs.com/xjtu-blacksmith/p/easymcm.html}
\end{thebibliography}

% 以下为附录内容
% 如您的论文中不需要附录，请自行删除
\begin{subappendices}  % 附录环境

\section{Appendix A: Further on \LaTeX}
To clarify the importance of using \LaTeX\ in MCM or ICM, several points need to be covered, which are \ldots

To be more specific, \ldots

All in all, \ldots

Anyway, nobody \textbf{really} needs such appendix \ldots

\section{Appendix B: Program Codes}
Here are the program codes we used in our research.

% 代码环境示例三则
% 如您的论文不需要展示代码，请删除
% 更多用法，请参考 listings 宏包文档

% Python 代码示例
\begin{lstlisting}[language=Python, name={test.py}]
# Python code example
for i in range(10):
    print('Hello, world!')
\end{lstlisting}

% MATLAB 代码示例
\begin{lstlisting}[language=MATLAB, name={test.m}]
% MATLAB code example
for i = 1:10
    disp("hello, world!");
end
\end{lstlisting}

% C++ 代码示例
\begin{lstlisting}[language=C++, name={test.cpp}]
// C++ code example
#include <iostream>
using namespace std;

int main() {
    for (int i = 0; i < 10; i++)
        cout << "hello, world" << endl;
    return 0;
}
\end{lstlisting}

\end{subappendices}  % 附录内容结束

\end{document}  % 结束

### 2025-01-20 代码/main.py
测试文件
测试文件

@@ -1,0 +1,26 @@
+#写一个用于区分鸢尾花的程序，使用KNN算法
+#导入数据集
+from sklearn.datasets import load_iris
+from sklearn.model_selection import train_test_split
+from sklearn.neighbors import KNeighborsClassifier
+import numpy as np
+
+#导入数据集
+iris_dataset = load_iris()
+#划分数据集
+X_train, X_test, y_train, y_test = train_test_split(iris_dataset['data'], iris_dataset['target'], random_state=0)
+#创建模型
+knn = KNeighborsClassifier(n_neighbors=1)
+#训练模型
+knn.fit(X_train, y_train)
+#预测
+X_new = np.array([[5, 2.9, 1, 0.2]])
+prediction = knn.predict(X_new)
+print("预测结果：{}".format(prediction))
+print("预测花的种类：{}".format(iris_dataset['target_names'][prediction]))
+#评估模型
+print("模型评分：{:.2f}".format(knn.score(X_test, y_test)))
+
+
+
+#这是一个测试文件

### 2025-01-23 论文/PAPER.tex
修改了论文
更新论文
叶徐俊更新了论文
合并了PAPER和PAPER模板

@@
 % 请在以下的方括号中填写队伍控制号
-\usepackage[1234567]{easymcm}  % 载入 EasyMCM 模板文件
-\problem{A}  % 请在此处填写题号
+\usepackage[2506135]{easymcm}  % 载入 EasyMCM 模板文件
+\problem{C}  % 请在此处填写题号
 \usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
 %\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包
+\usepackage{amsmath}
 
@@
 % 文档开始
+\newtheorem{keywords}{Keywords}
 \begin{document}
@@
 \begin{abstract}
-	Hello, MCM.
 
@@
     % \textbf{Keywords}: MATLAB, mathematics, LaTeX.
-
+\begin{keywords}
+\end{keywords}
 \end{abstract}
@@
     \item Doing the first thing.
-    \item Doing the second thing.
+    \item Doing the second thing.\\doing\\    doing11
+
 \end{itemize}
 
-\subsection{Literature Review}
+\subsection{Restatement of Problem}
 A literatrue\cite{1} say something about this problem ...
@@
 
-\section{Preparation of the Models}
-\subsection{Assumptions}
+\section{Assumptions}
 
-\subsection{Notations}
+\section{Notations}
 The primary notations used in this paper are listed in Table \ref{tb:notation}.
@@
 
-\section{The Models}
-\subsection{Model 1}
+\section{Data Preprocessing}
+\subsection{Basic Data Preprocessing}
+\subsection{Data Mining}
+\section{Task1:}
 \subsubsection{Details about Model 1}
-The detail can be described by equation \eqref{eq:heat}:
-\begin{equation}\label{eq:heat}
-\frac{\partial u}{\partial t} - a^2 \left( \frac{\partial^2 u}{\partial x^2} + \frac{\partial^2 u}{\partial y^2} + \frac{\partial^2 u}{\partial z^2} \right) = f(x, y, z, t)
+The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
+%带标签的方程
+\begin{equation}\label{eq1}
+\alpha+\beta=\gamma
+\end{equation}
+%不带标签的方程
+\[
+\alpha+\beta=\gamma
+\]
+$$\alpha$$
+
+%长等式
+\begin{equation}\label{eq2}
+	\begin{split}
+	&A+B+C+D+E+F\\
+	&=G+Q+W+E+R+T+Y\\
+	&=A+S+D+F+G+H+J
+	\end{split}
+\end{equation}
+%分段方程
+\begin{equation}\label{eq3}
+	F(x)=
+	\begin{cases}
+		0&,\text{if $x<0$}\\
+		x+1&,\text{if $x>0$}\\
+		1&,\text{otherwise}
+			\end{cases}
 \end{equation}
 
-\subsection{Model 2}
-\subsubsection{Conclusion of Model 2}
+\section{Task2:}
+\subsection{Conclusion of Model 2}
 The results are shown in Figure \ref{fig:result}, where $t$ denotes the time in seconds, and $c$ refers to the concentration of water in the boiler.
@@
 \clearpage
-\subsubsection{Commetary on Model 2}
+\subsection{Commetary on Model 2}
 The instance of long and wide tables are shown in Table \ref{tb:longtable}.
@@
 
-\section{Strengths and Weaknesses}
+\section{Task3}
+
+\section{Task4}
+
+\section{Sensitivity Analysis}
+
+\section{Model Evaluation}
 \subsection{Strengths}
@@
  \end{itemize}
+
+\section{Conclusion}
 

### 2025-01-24 代码/国家level聚类.py
国家排序

@@ -1,0 +1,89 @@
+#写一个k-means聚类算法，自变量为某国家总共在奥运会上获得的铜牌，银牌，金牌数，总数因变量为该国家的level（1-5）
+#导入数据集
+from sklearn.cluster import KMeans
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+import pandas as pd
+
+#导入数据集
+data = pd.read_csv('./data/summerOly_medal_counts.csv')
+data = data.dropna()
+
+#Year<1992的数据不要
+data = data[data['Year']>=1992]
+
+
+#首先对数据进行求和，里面包含了历届奥运会的数据，我们需要groupby国家，然后对铜牌列，银牌列，金牌列，总数进行求和
+data = data.groupby('NOC').sum()
+
+
+
+#只需要Gold	Silver	Bronze	Total这四列
+data = data[['Gold', 'Silver', 'Bronze', 'Total']]
+
+
+#创建模型
+kmeans = KMeans(n_clusters=5)
+#训练模型
+kmeans.fit(data)
+#预测
+prediction = kmeans.predict(data)
+#输出
+data['level'] = prediction
+print(data)
+
+#画图，画3D的聚类图，x轴为铜牌数，y轴为银牌数，z轴为金牌数，不同level的国家用不同颜色表示
+fig = plt.figure()
+ax = fig.add_subplot(111, projection='3d')
+ax.scatter(data['Bronze'], data['Silver'], data['Gold'], c=prediction)
+
+
+#每个散点要显示国家名，这里只显示总奖牌数前10的国家
+top10 = data.sort_values(by='Total', ascending=False).head(10)
+
+#对前十名国家，要从坐标轴三个面上，作三条垂直于平面，并经过散点的黑色直线，例如散点(1,2,3)，则要画三条线，分别是(1,0,0),(0,2,0),(0,0,3)，经过(1,2,3)
+idx=0
+for index, row in top10.iterrows():
+    #画一条垂直于Silver和Bronze平面的线，经过散点(row['Bronze'], row['Silver'], 0)
+    #ax.plot([row['Bronze'], row['Bronze']], [row['Silver'], row['Silver']], [0, row['Gold']], color='black')
+   
+    #在该国家坐标轴周围偏20%的位置显示国家名，并用线连接国家名与散点
+    #交错显示，如果index%2==0，则偏转20%，否则偏转-20%
+    if idx%2==0:        
[…]

### 2025-01-24 代码/不同国家擅长的体育项目分析.py
不同国家擅长的不同运动种类数据表

@@ -1,0 +1,91 @@
+#数据集格式：Name,Sex,Team,NOC,Year,City,Sport,Event,Medal
+#为了探索不同国家擅长的体育项目，我们需要对数据集进行分析，对于同一个项目(以Sport为单位)，所有国家获得的奖牌中，根据目标国家奖牌数的占比确定该项目是否是目标国家擅长的项目。
+#summerOly_athletes.csv
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+# #读取数据
+# data=pd.read_csv('./data/summerOly_athletes.csv')
+
+# #数据预处理
+# #去除重复值
+# data.drop_duplicates(inplace=True)
+# #去除缺失值
+# data.dropna(inplace=True)
+
+
+# #数据分析
+# #不同国家擅长的体育项目
+# #目标国家
+# target_country='United States'#对应列为Team
+
+# #目标国家奖牌数
+# #Medal列中，No medal表示没有奖牌，Bronze表示铜牌，Silver表示银牌，Gold表示金牌
+# #筛选出目标国家不同项目的奖牌数，注意要排除No medal
+# target_country_medals=data[(data['Team']==target_country)&(data['Medal']!='No medal')].groupby('Sport').size()
+# #所有国家奖牌数
+# all_country_medals=data[data['Medal']!='No medal'].groupby('Sport').size()
+# #目标国家奖牌数占比
+# medal_rate=target_country_medals/all_country_medals
+# #排序
+# medal_rate=medal_rate.sort_values(ascending=False)
+
+
+# #如果小于0.005，不显示
+# medal_rate=medal_rate[medal_rate>0.005]
+# #只显示前20个
+# medal_rate=medal_rate[:20]
+# #绘制图表
+# plt.figure(figsize=(10,6))
+# sns.barplot(x=medal_rate.values,y=medal_rate.index)
+# plt.title('Percentage of Medals of Different Sports in '+target_country)
+
+# plt.show()
+
+# pass
+
+
+
+#用同样的方法，分别计算每个国家擅长的体育项目，导出csv文件
+#列为Team，Sport，Adeptness
+#Adeptness表示擅长程度，即该国家在该项目的奖牌数占所有国家奖牌数的比例
+#数据集格式：Team,Sport,Adeptness
+#country_adeptness.csv
+#读取数据
[…]

### 2025-01-24 代码/国家level聚类.py

@@ -82,8 +82,4 @@ fig.set_size_inches(18.5, 10.5)
 plt.show()
 
 
-#由于kmeans的标签是无序的，我们需要对标签进行排序，例如level=5的国家是总奖牌数最少的，level=1的国家是总奖牌数最多的
-#我们可以对level进行排序，然后重新赋值
-#我们只需要对某一level中奖牌最多的国家挑出，进行排序，就可以知道某一level代表什么档次的国家，此后重新进行赋值
-
-data.to_csv('./data/country_level.csv')
+# data.to_csv('./data/country_level_.csv')

### 2025-01-24 代码/不同国家擅长的体育项目分析.py
更新若干数据

@@ -64,9 +64,15 @@ data.dropna(inplace=True)
 #数据分析
 #不同国家擅长的体育项目
 
-countries=data['Team'].unique()
+# #注意，Team字段可能有一些冗余字符，例如South Korea可能会有-2 -3 -4 -11之类的-数字，所以需要截断至-之前的字符
+
+# data['Team']=data['Team'].apply(lambda x:x.split('-')[0])
+
+# countries=data['Team'].unique()
+countries=data['NOC'].unique()
 result=[]
 
+idx=0
 for country in countries:
     #目标国家
     target_country=country
@@ -74,18 +80,19 @@ for country in countries:
     #目标国家奖牌数
     #Medal列中，No medal表示没有奖牌，Bronze表示铜牌，Silver表示银牌，Gold表示金牌
     #筛选出目标国家不同项目的奖牌数，注意要排除No medal
-    target_country_medals=data[(data['Team']==target_country)&(data['Medal']!='No medal')].groupby('Sport').size()
+    target_country_medals=data[(data['NOC']==target_country)&(data['Medal']!='No medal')].groupby('Sport').size()
     #所有国家奖牌数
     all_country_medals=data[data['Medal']!='No medal'].groupby('Sport').size()
     #目标国家奖牌数占比
     medal_rate=target_country_medals/all_country_medals
     #排序
     medal_rate=medal_rate.sort_values(ascending=False)
-    
     #添加到结果中
     for sport in medal_rate.index:
         result.append([target_country,sport,medal_rate[sport]])
+    idx+=1
+    print('正在处理',idx,',共',len(countries),'个国家')
         
 #导出结果
-result=pd.DataFrame(result,columns=['Team','Sport','Adeptness'])
+result=pd.DataFrame(result,columns=['NOC','Sport','Adeptness'])
 result.to_csv('./data/country_adeptness.csv',index=False)

### 2025-01-24 代码/国家level聚类.py

@@ -10,8 +10,8 @@ import pandas as pd
 data = pd.read_csv('./data/summerOly_medal_counts.csv')
 data = data.dropna()
 
-#Year<1992的数据不要
-data = data[data['Year']>=1992]
+# #Year<1992的数据不要
+# data = data[data['Year']>=1992]
 
 
 #首先对数据进行求和，里面包含了历届奥运会的数据，我们需要groupby国家，然后对铜牌列，银牌列，金牌列，总数进行求和
@@ -82,4 +82,4 @@ fig.set_size_inches(18.5, 10.5)
 plt.show()
 
 
-# data.to_csv('./data/country_level_.csv')
+data.to_csv('./data/country_level_.csv')

### 2025-01-24 代码/国家level聚类.py
1

@@ -10,8 +10,8 @@ import pandas as pd
 data = pd.read_csv('./data/summerOly_medal_counts.csv')
 data = data.dropna()
 
-#Year<1992的数据不要
-data = data[data['Year']>=1992]
+# #Year<1992的数据不要
+# data = data[data['Year']>=1992]
 
 
 #首先对数据进行求和，里面包含了历届奥运会的数据，我们需要groupby国家，然后对铜牌列，银牌列，金牌列，总数进行求和
@@ -82,8 +82,4 @@ fig.set_size_inches(18.5, 10.5)
 plt.show()
 
 
-#由于kmeans的标签是无序的，我们需要对标签进行排序，例如level=5的国家是总奖牌数最少的，level=1的国家是总奖牌数最多的
-#我们可以对level进行排序，然后重新赋值
-#我们只需要对某一level中奖牌最多的国家挑出，进行排序，就可以知道某一level代表什么档次的国家，此后重新进行赋值
-
-data.to_csv('./data/country_level.csv')
+data.to_csv('./data/country_level_.csv')

### 2025-01-24 代码/国家level聚类.py
level

@@ -77,9 +77,18 @@ ax.grid(True)
 #图片背景颜色选用好看的淡橙色
 ax.set_facecolor('peachpuff')
 
-#图片尺寸应最大化，防止标签重叠
-fig.set_size_inches(18.5, 10.5)
-plt.show()
+# #图片尺寸应最大化，防止标签重叠
+# fig.set_size_inches(18.5, 10.5)
+# plt.show()
 
 
+#按照金牌银牌铜牌总数排序
+data = data.sort_values(by='Total', ascending=False)
+#第二关键字
+data = data.sort_values(by='Gold', ascending=False)
+#第三关键字
+data = data.sort_values(by='Silver', ascending=False)
+#第四关键字
+data = data.sort_values(by='Bronze', ascending=False)
+#导出数据
 data.to_csv('./data/country_level_.csv')

### 2025-01-24 代码/data/不同国家每届比赛对每个项目派出的人数.py
不同国家每届比赛对每个项目派出的人数

@@ -1,0 +1,65 @@
+#统计不同国家每届比赛对每个项目派出的人数
+#数据来源summerOly_athletes.csv
+
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+#读取数据
+data=pd.read_csv('./data/summerOly_athletes.csv')
+
+#数据预处理
+#去除重复值
+data.drop_duplicates(inplace=True)
+#去除缺失值
+data.dropna(inplace=True)
+
+#数据分析
+#不同国家每届比赛对每个项目派出的人数
+#目标国家
+target_country='USA'#对应列为NOC
+
+target_sport='Athletics'#对应列为Sport
+
+#历届比赛派出的人数
+
+#筛选出目标国家不同项目的人数
+target_country_athletes=data[(data['NOC']==target_country)&(data['Sport']==target_sport)].groupby('Year').size()
+
+#绘制图表
+plt.figure(figsize=(10,6))
+sns.barplot(x=target_country_athletes.index,y=target_country_athletes.values)
+plt.title('Number of Athletes of '+target_sport+' in '+target_country+' in Different Years')
+
+plt.show()
+
+
+pass
+
+
+
+#根据以上思路，对每个国家的每个项目进行同样的统计，导出csv文件
+#列为NOC，Sport，Year，Athletes
+#数据集格式：NOC,Sport,Year,Athletes
+
+result=[]
+
+#所有国家
+countries=data['NOC'].unique()
+#所有项目
+sports=data['Sport'].unique()
+idx=0
+for country in countries:
+    idx+=1
+    print('第',idx,'个国家','共',len(countries),'个国家')
+    for sport in sports:
+        #筛选出目标国家不同项目的人数
+        country_sport_athletes=data[(data['NOC']==country)&(data['Sport']==sport)].groupby('Year').size()
+        #添加到结果中
+        for year in country_sport_athletes.index:
+            result.append([country,sport,year,country_sport_athletes[year]])
+            
+#转换为DataFrame
+result=pd.DataFrame(result,columns=['NOC','Sport','Year','Athletes'])
+#导出csv文件
+result.to_csv('./data/n_participants.csv',index=False)

### 2025-01-24 代码/国家level聚类.py
Revert "Update 国家level聚类.py"
This reverts commit c71eb5e8ef2c1264f318c99c3ec908cf8c6ff9ba.

@@ -10,8 +10,8 @@ import pandas as pd
 data = pd.read_csv('./data/summerOly_medal_counts.csv')
 data = data.dropna()
 
-# #Year<1992的数据不要
-# data = data[data['Year']>=1992]
+#Year<1992的数据不要
+data = data[data['Year']>=1992]
 
 
 #首先对数据进行求和，里面包含了历届奥运会的数据，我们需要groupby国家，然后对铜牌列，银牌列，金牌列，总数进行求和
@@ -77,18 +77,13 @@ ax.grid(True)
 #图片背景颜色选用好看的淡橙色
 ax.set_facecolor('peachpuff')
 
-# #图片尺寸应最大化，防止标签重叠
-# fig.set_size_inches(18.5, 10.5)
-# plt.show()
+#图片尺寸应最大化，防止标签重叠
+fig.set_size_inches(18.5, 10.5)
+plt.show()
 
 
-#按照金牌银牌铜牌总数排序
-data = data.sort_values(by='Total', ascending=False)
-#第二关键字
-data = data.sort_values(by='Gold', ascending=False)
-#第三关键字
-data = data.sort_values(by='Silver', ascending=False)
-#第四关键字
-data = data.sort_values(by='Bronze', ascending=False)
-#导出数据
-data.to_csv('./data/country_level_.csv')
+#由于kmeans的标签是无序的，我们需要对标签进行排序，例如level=5的国家是总奖牌数最少的，level=1的国家是总奖牌数最多的
+#我们可以对level进行排序，然后重新赋值
+#我们只需要对某一level中奖牌最多的国家挑出，进行排序，就可以知道某一level代表什么档次的国家，此后重新进行赋值
+
+data.to_csv('./data/country_level.csv')

### 2025-01-24 代码/main.py
1

@@ -1,26 +1,0 @@
-#写一个用于区分鸢尾花的程序，使用KNN算法
-#导入数据集
-from sklearn.datasets import load_iris
-from sklearn.model_selection import train_test_split
-from sklearn.neighbors import KNeighborsClassifier
-import numpy as np
-
-#导入数据集
-iris_dataset = load_iris()
-#划分数据集
-X_train, X_test, y_train, y_test = train_test_split(iris_dataset['data'], iris_dataset['target'], random_state=0)
-#创建模型
-knn = KNeighborsClassifier(n_neighbors=1)
-#训练模型
-knn.fit(X_train, y_train)
-#预测
-X_new = np.array([[5, 2.9, 1, 0.2]])
-prediction = knn.predict(X_new)
-print("预测结果：{}".format(prediction))
-print("预测花的种类：{}".format(iris_dataset['target_names'][prediction]))
-#评估模型
-print("模型评分：{:.2f}".format(knn.score(X_test, y_test)))
-
-
-
-#这是一个测试文件

### 2025-01-24 代码/不同国家擅长的体育项目分析.py

@@ -5,45 +5,45 @@ import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
 import seaborn as sns
-# #读取数据
-# data=pd.read_csv('./data/summerOly_athletes.csv')
+#读取数据
+data=pd.read_csv('./data/summerOly_athletes.csv')
 
-# #数据预处理
-# #去除重复值
-# data.drop_duplicates(inplace=True)
-# #去除缺失值
-# data.dropna(inplace=True)
-
-
-# #数据分析
-# #不同国家擅长的体育项目
-# #目标国家
-# target_country='United States'#对应列为Team
-
-# #目标国家奖牌数
-# #Medal列中，No medal表示没有奖牌，Bronze表示铜牌，Silver表示银牌，Gold表示金牌
-# #筛选出目标国家不同项目的奖牌数，注意要排除No medal
-# target_country_medals=data[(data['Team']==target_country)&(data['Medal']!='No medal')].groupby('Sport').size()
-# #所有国家奖牌数
-# all_country_medals=data[data['Medal']!='No medal'].groupby('Sport').size()
-# #目标国家奖牌数占比
-# medal_rate=target_country_medals/all_country_medals
-# #排序
-# medal_rate=medal_rate.sort_values(ascending=False)
+#数据预处理
+#去除重复值
+data.drop_duplicates(inplace=True)
+#去除缺失值
+data.dropna(inplace=True)
 
 
-# #如果小于0.005，不显示
-# medal_rate=medal_rate[medal_rate>0.005]
-# #只显示前20个
-# medal_rate=medal_rate[:20]
-# #绘制图表
-# plt.figure(figsize=(10,6))
-# sns.barplot(x=medal_rate.values,y=medal_rate.index)
-# plt.title('Percentage of Medals of Different Sports in '+target_country)
+#数据分析
+#不同国家擅长的体育项目
+#目标国家
+target_country='United States'#对应列为Team
 
-# plt.show()
+#目标国家奖牌数
+#Medal列中，No medal表示没有奖牌，Bronze表示铜牌，Silver表示银牌，Gold表示金牌
+#筛选出目标国家不同项目的奖牌数，注意要排除No medal
+target_country_medals=data[(data['Team']==target_country)&(data['Medal']!='No medal')].groupby('Sport').size()
+#所有国家奖牌数
+all_country_medals=data[data['Medal']!='No medal'].groupby('Sport').size()
+#目标国家奖牌数占比
[…]

### 2025-01-24 代码/不同运动员服役次数分布.py

@@ -1,0 +1,34 @@
+#summerOly_athletes.csv
+
+import pandas as pd
+import numpy as np
+
+# 读取数据
+data = pd.read_csv('./data/summerOly_athletes.csv')
+
+#groupby运动员名字，统计每个运动员参加的比赛次数
+result = data.groupby('Name').size()
+# 保存结果
+result.to_csv('./data/athlete_serve_times_distribution.csv')
+
+#描述统计
+print(result.describe())
+
+#分布拟合，使用核密度估计，绘制核密度图,查看分布情况
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+sns.kdeplot(result, shade=True)
+plt.xlabel('Serve Times')
+plt.ylabel('Density')
+plt.title('Distribution of Serve Times')
+plt.show()
+
+# count    129992.000000
+# mean          1.942927
+# std           1.953005
+# min           1.000000
+# 25%           1.000000
+# 50%           1.000000
+# 75%           2.000000
+# max          76.000000

### 2025-01-24 代码/各国家每年新增人数与离开人数走势.py

@@ -1,0 +1,75 @@
+#summerOly_athletes.csv
+
+#分析每个国家每届奥运会中，新增的人数和离开的人数走势
+
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+# 读取数据
+data = pd.read_csv('./data/summerOly_athletes.csv')
+
+# 以每个国家的每个项目为单位，统计每年新增的人数和离开的人数
+
+#1896年为第一届奥运会，从下一届开始统计
+years = data['Year'].unique()
+
+#结果
+result = []
+
+for year in years:
+    #本届数据
+    current_data = data[data['Year'] == year]
+    #上一届数据
+    #上一届不一定是-4，因为有可能有一届奥运会没有举办
+    last_year = year - 4
+    # if last_year not in years:
+    #     last_year = year - 2
+    last_data = data[data['Year'] == last_year]
+    #新增人数
+    new_athletes = len(set(current_data['Name']) - set(last_data['Name']))
+    #离开人数
+    leave_athletes = len(set(last_data['Name']) - set(current_data['Name']))
+    
+    result.append([year,new_athletes,leave_athletes])
+    
+result = pd.DataFrame(result,columns=['Year','New','Leave'])
+
+
+col_width=2
+#绘制柱形图，增加的人数和离开的人数叠加显示，新增的人在左边，离开的人在右边
+plt.figure(figsize=(10,6))
+plt.bar(result['Year'],result['Leave'],label='Leave',width=col_width,color='blue')
+#给出年份
+plt.bar(result['Year'],result['New'],label='New',bottom=result['Leave'],width=col_width,color='orange')
+plt.bar(result['Year'],np.abs(result['New']-result['Leave']),label='Variation',color=(result['New']-result['Leave']>0).map({True:'g',False:'r'}),width=1)
+
+plt.xlabel('Year')
+plt.ylabel('Number of Athletes')
+plt.title('Number of New and Leave Athletes in Each Year')
+
+
+
+#添加灰色bar用于标注
+plt.bar(1916,8000,color='gray',width=col_width)
+plt.text(1916,8000,'Cancelled due to WWII',ha='center',va='bottom')
+#添加灰色bar用于标注
+plt.bar(1940,8000,color='gray',width=col_width)
+plt.bar(1944,8000,color='gray',width=col_width)
+#(1944,8000)处有注解，说明1944年奥运会取消了
[…]

### 2025-01-24 代码/预测各项目每年各国参赛人数变化趋势.py

@@ -1,0 +1,66 @@
+#n_participants.csv
+
+#示例数据
+# NOC,Sport,Year,Athletes
+# CHN,Basketball,1936,13
+# CHN,Basketball,1948,10
+# CHN,Basketball,1984,23
+# CHN,Basketball,1988,22
+# CHN,Basketball,1992,23
+# CHN,Basketball,1996,24
+# CHN,Basketball,2000,12
+# CHN,Basketball,2004,24
+# CHN,Basketball,2008,24
+# CHN,Basketball,2012,24
+# CHN,Basketball,2016,24
+# CHN,Basketball,2020,12
+# CHN,Basketball,2024,12
+
+
+#有一套数据集，里面包含所有国家参加的所有奥运会的运动员数量，数据集格式为NOC,Sport,Year,Athletes，其中NOC表示国家代码，Sport表示体育项目，Year表示年份，Athletes表示参加的运动员数量。
+#先要进行线性回归，预测2028年，2032年，2036年中国参加篮球比赛的运动员数量，导出csv文件，列为NOC,Sport,2028,2032,2036
+
+import pandas as pd
+import numpy as np
+from sklearn.linear_model import LinearRegression
+
+# 读取数据
+data = pd.read_csv('./data/n_participants.csv')
+
+#数据预处理
+#空值填0
+data.fillna(0, inplace=True)
+
+
+#里面记录了每个Sport项目每年的运动员数，每一行都有从1896年到2024年的运动员数
+
+#我们对每个国家、项目组成的一组数据进行线性回归拟合，预测2028,2032,2036年预期每个项目的运动员数
+
+#创建模型
+model = LinearRegression()
+
+#创建一个DataFrame，用于存放预测结果
+result = []
+
+#对每一组数据进行拟合
+
+#groupby国家、项目
+
+for name, group in data.groupby(['NOC', 'Sport']):
+    #创建X，Y
+    X = group['Year'].values.reshape(-1, 1)
+    Y = group['Athletes'].values.reshape(-1, 1)
+    
+    #训练模型
+    model.fit(X, Y)
+    
+    #预测
+    predict = model.predict([[2028], [2032], [2036]])
+    
+    #添加到result
+    result.append([name[0], name[1], predict[0][0], predict[1][0], predict[2][0]])
+    
+    
+#导出结果
+result = pd.DataFrame(result, columns=['NOC', 'Sport', '2028', '2032', '2036'])
+result.to_csv('./data/predict_participants.csv', index=False)

### 2025-01-24 代码/预测各项目每年奖牌数变化趋势.py

@@ -1,0 +1,45 @@
+#summerOly_programs.csv
+
+import pandas as pd
+import numpy as np
+
+# 读取数据
+data = pd.read_csv('./data/summerOly_programs.csv')
+
+#数据预处理
+#空值填0
+data.fillna(0, inplace=True)
+
+
+#里面记录了每个Sport项目每年的奖牌数，每一行都有从1896年到2024年的奖牌数
+#我们对每一行都进行线性回归拟合，预测2028,2032,2036年预期每个项目的奖牌数
+
+#导入线性回归模型
+from sklearn.linear_model import LinearRegression
+
+#创建模型
+model = LinearRegression()
+
+#创建一个DataFrame，用于存放预测结果
+result = []
+
+#对每一行进行拟合
+for index, row in data.iterrows():
+    #创建X，Y
+    X = data.columns[4:].values.reshape(-1, 1)
+    Y = row.values[4:].reshape(-1, 1)
+    
+    #训练模型
+    model.fit(X, Y)
+    
+    #预测
+    predict = model.predict([[2028], [2032], [2036]])
+    
+    #添加到result
+    result.append([row['Sport'], predict[0], predict[1], predict[2]])
+    
+
+#导出结果
+result = pd.DataFrame(result, columns=['Sport', '2028', '2032', '2036'])
+result.to_csv('./data/predict_medal_counts.csv', index=False)
+    

### 2025-01-24 代码/一致性检验.py
1

@@ -1,0 +1,53 @@
+#检验summerOly_medal_counts.csv里面，各国的每一届奖牌总数，与summerOly_athletes.csv里面，所有运动员加起来的奖牌总数是否一致
+
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+#读取数据
+data=pd.read_csv('./data/summerOly_athletes.csv')
+
+#数据预处理
+#去除重复值
+data.drop_duplicates(inplace=True)
+#去除缺失值
+data.dropna(inplace=True)
+
+
+mapping=pd.read_csv('./data/noc_region.csv')
+#NOC与国家名字的映射表
+
+#检验summerOly_medal_counts.csv里面，某国每一届奖牌总数，与summerOly_athletes.csv里面，该国当届所有运动员加起来的奖牌总数是否一致
+
+#读取数据
+medal_counts=pd.read_csv('./data/summerOly_medal_counts.csv')
+#检验
+
+passed=[]
+failed=[]
+for i in range(len(medal_counts)):
+    NOC=medal_counts.loc[i,'NOC']
+    name=NOC
+    if NOC not in mapping['Country'].values:
+        #print(NOC)
+        continue
+    NOC=mapping[mapping['Country']==NOC]['NOC'].values[0]
+    year=medal_counts.loc[i,'Year']
+    #该国该年奖牌总数
+    total_medals=medal_counts.loc[i,'Total']
+    #该国该年所有运动员奖牌总数
+    athletes_medals=data[(data['NOC']==NOC)&(data['Year']==year)&(data['Medal']!='No medal')].shape[0]
+    if total_medals!=athletes_medals and athletes_medals!=0:
+        print(name,NOC,year,total_medals,athletes_medals)
+        failed.append((name,NOC,year,total_medals,athletes_medals))
+    else:
+        #print(name,NOC,year,'pass')
+        passed.append((name,NOC,year))
+        
+        
+#画饼图，显示检验结果
+plt.figure(figsize=(6,6))
+plt.pie([len(passed),len(failed)],labels=['passed','failed'],autopct='%1.1f%%')
+plt.title('Check Results')
+plt.show()
+# pass

### 2025-01-24 代码/不同国家擅长的体育项目分析.py

@@ -1,0 +1,98 @@
+#数据集格式：Name,Sex,Team,NOC,Year,City,Sport,Event,Medal
+#为了探索不同国家擅长的体育项目，我们需要对数据集进行分析，对于同一个项目(以Sport为单位)，所有国家获得的奖牌中，根据目标国家奖牌数的占比确定该项目是否是目标国家擅长的项目。
+#summerOly_athletes.csv
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+# #读取数据
+# data=pd.read_csv('./data/summerOly_athletes.csv')
+
+# #数据预处理
+# #去除重复值
+# data.drop_duplicates(inplace=True)
+# #去除缺失值
+# data.dropna(inplace=True)
+
+
+# #数据分析
+# #不同国家擅长的体育项目
+# #目标国家
+# target_country='United States'#对应列为Team
+
+# #目标国家奖牌数
+# #Medal列中，No medal表示没有奖牌，Bronze表示铜牌，Silver表示银牌，Gold表示金牌
+# #筛选出目标国家不同项目的奖牌数，注意要排除No medal
+# target_country_medals=data[(data['Team']==target_country)&(data['Medal']!='No medal')].groupby('Sport').size()
+# #所有国家奖牌数
+# all_country_medals=data[data['Medal']!='No medal'].groupby('Sport').size()
+# #目标国家奖牌数占比
+# medal_rate=target_country_medals/all_country_medals
+# #排序
+# medal_rate=medal_rate.sort_values(ascending=False)
+
+
+# #如果小于0.005，不显示
+# medal_rate=medal_rate[medal_rate>0.005]
+# #只显示前20个
+# medal_rate=medal_rate[:20]
+# #绘制图表
+# plt.figure(figsize=(10,6))
+# sns.barplot(x=medal_rate.values,y=medal_rate.index)
+# plt.title('Percentage of Medals of Different Sports in '+target_country)
+
+# plt.show()
+
+# pass
+
+
+
+#用同样的方法，分别计算每个国家擅长的体育项目，导出csv文件
+#列为Team，Sport，Adeptness
+#Adeptness表示擅长程度，即该国家在该项目的奖牌数占所有国家奖牌数的比例
+#数据集格式：Team,Sport,Adeptness
+#country_adeptness.csv
+#读取数据
+data=pd.read_csv('./data/summerOly_athletes.csv')
+
[…]

### 2025-01-24 代码/国家level聚类.py
1

@@ -10,8 +10,8 @@ import pandas as pd
 data = pd.read_csv('./data/summerOly_medal_counts.csv')
 data = data.dropna()
 
-#Year<1992的数据不要
-data = data[data['Year']>=1992]
+# #Year<1992的数据不要
+# data = data[data['Year']>=1992]
 
 
 #首先对数据进行求和，里面包含了历届奥运会的数据，我们需要groupby国家，然后对铜牌列，银牌列，金牌列，总数进行求和
@@ -77,13 +77,18 @@ ax.grid(True)
 #图片背景颜色选用好看的淡橙色
 ax.set_facecolor('peachpuff')
 
-#图片尺寸应最大化，防止标签重叠
-fig.set_size_inches(18.5, 10.5)
-plt.show()
+# #图片尺寸应最大化，防止标签重叠
+# fig.set_size_inches(18.5, 10.5)
+# plt.show()
 
 
-#由于kmeans的标签是无序的，我们需要对标签进行排序，例如level=5的国家是总奖牌数最少的，level=1的国家是总奖牌数最多的
-#我们可以对level进行排序，然后重新赋值
-#我们只需要对某一level中奖牌最多的国家挑出，进行排序，就可以知道某一level代表什么档次的国家，此后重新进行赋值
-
-data.to_csv('./data/country_level.csv')
+#按照金牌银牌铜牌总数排序
+data = data.sort_values(by='Total', ascending=False)
+#第二关键字
+data = data.sort_values(by='Gold', ascending=False)
+#第三关键字
+data = data.sort_values(by='Silver', ascending=False)
+#第四关键字
+data = data.sort_values(by='Bronze', ascending=False)
+#导出数据
+data.to_csv('./data/country_level_.csv')

### 2025-01-24 代码/各国家每年新增人数与离开人数走势.py
Update 各国家每年新增人数与离开人数走势.py

@@ -39,9 +39,11 @@ result = pd.DataFrame(result,columns=['Year','New','Leave'])
 col_width=2
 #绘制柱形图，增加的人数和离开的人数叠加显示，新增的人在左边，离开的人在右边
 plt.figure(figsize=(10,6))
-plt.bar(result['Year'],result['Leave'],label='Leave',width=col_width,color='blue')
+#颜色为默认的蓝色
+plt.bar(result['Year'],result['Leave'],label='Leave',width=col_width,color='C1')
 #给出年份
-plt.bar(result['Year'],result['New'],label='New',bottom=result['Leave'],width=col_width,color='orange')
+#颜色为默认的橙色
+plt.bar(result['Year'],result['New'],label='New',bottom=result['Leave'],width=col_width,color='C0')
 plt.bar(result['Year'],np.abs(result['New']-result['Leave']),label='Variation',color=(result['New']-result['Leave']>0).map({True:'g',False:'r'}),width=1)
 
 plt.xlabel('Year')

### 2025-01-25 代码/各国家每年新增人数与离开人数走势.py
1

@@ -1,7 +1,3 @@
-#summerOly_athletes.csv
-
-#分析每个国家每届奥运会中，新增的人数和离开的人数走势
-
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
@@ -16,62 +12,30 @@ years = data['Year'].unique()
 
 #结果
 result = []
-
-for year in years:
-    #本届数据
-    current_data = data[data['Year'] == year]
-    #上一届数据
-    #上一届不一定是-4，因为有可能有一届奥运会没有举办
-    last_year = year - 4
-    # if last_year not in years:
-    #     last_year = year - 2
-    last_data = data[data['Year'] == last_year]
-    #新增人数
-    new_athletes = len(set(current_data['Name']) - set(last_data['Name']))
-    #离开人数
-    leave_athletes = len(set(last_data['Name']) - set(current_data['Name']))
+#统计每个国家的每个项目
+idx=0
+for country in data['NOC'].unique():
+    idx+=1
     
-    result.append([year,new_athletes,leave_athletes])
-    
-result = pd.DataFrame(result,columns=['Year','New','Leave'])
+    idx2=0
+    for sport in data['Sport'].unique():
+        idx2+=1
+        print('正在处理第{}个国家，共{}个国家;第{}个项目，共{}个项目：'.format(idx,len(data['NOC'].unique()),idx2,len(data['Sport'].unique())))
+        for year in years:
+            #本届数据
+            current_data = data[(data['Year'] == year) & (data['NOC'] == country) & (data['Sport'] == sport)]
+            #上一届数据
+            #上一届不一定是-4，因为有可能有一届奥运会没有举办
+            last_year = year - 4
+            # if last_year not in years:
+            #     last_year = year - 2
+            last_data = data[(data['Year'] == last_year) & (data['NOC'] == country) & (data['Sport'] == sport)]
+            #新增人数
+            new_athletes = len(set(current_data['Name']) - set(last_data['Name']))
+            #离开人数
+            leave_athletes = len(set(last_data['Name']) - set(current_data['Name']))
+            
+            result.append([country,sport,year,new_athletes,leave_athletes])
+result = pd.DataFrame(result,columns=['NOC','Sport','Year','New','Leave'])
 
-
[…]

### 2025-01-25 代码/运动员参数建模.py

@@ -1,0 +1,20 @@
+#summerOly_athletes.csv
+#对运动员在职业生涯中的金牌概率，银牌概率，铜牌概率，无奖牌概率进行统计
+
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+# 读取数据
+data = pd.read_csv('./data/summerOly_athletes.csv')
+
+# #groupby运动员名字，统计每个运动员金牌，银牌，铜牌，无奖牌的次数
+result = data.groupby('Name')['Medal'].value_counts().unstack().fillna(0)
+print(result)
+#计算金牌概率，银牌概率，铜牌概率，无奖牌概率
+result['Gold_prob'] = result['Gold'] / result.sum(axis=1)
+result['Silver_prob'] = result['Silver'] / result.sum(axis=1)
+result['Bronze_prob'] = result['Bronze'] / result.sum(axis=1)
+result['No_medal_prob'] = result['No medal'] / result.sum(axis=1)
+# 保存结果
+result.to_csv('./data/athlete_args.csv')

### 2025-01-25 代码/预测各项目每年奖牌数变化趋势.py

@@ -10,6 +10,9 @@ data = pd.read_csv('./data/summerOly_programs.csv')
 #空值填0
 data.fillna(0, inplace=True)
 
+#首先把一个Sport里面所有的子类都合并到一起
+data = data.groupby('Sport').sum().reset_index()
+print (data)
 
 #里面记录了每个Sport项目每年的奖牌数，每一行都有从1896年到2024年的奖牌数
 #我们对每一行都进行线性回归拟合，预测2028,2032,2036年预期每个项目的奖牌数

### 2025-01-25 代码/Q1逻辑回归模型.py
年限分布

@@ -1,0 +1,94 @@
+#最终要得到的表格列头是，NOC,Year,Golds,Medals
+# 主要模型：逻辑回归
+
+# 自变量X：
+# （国家因素）
+# 1.是否为东道主
+# 2.奖牌预期增量数（注意是增量数）*预期投入人员数量增量数（注意是增量数）
+# 3.某项目优势系数
+# 4.国家level（需要对level排序）
+# 5.某项目奖牌预期数量/某项目预期投入人员数量
+# p.s.对于小国家，变量2要给予相应奖励权重，即，有可能随着比赛奖项扩招，而小国家出现“黑马”的情况
+# （运动员因素）
+# 1.金牌概率
+# 2.银牌概率
+# 3.铜牌概率
+# 4.无牌概率
+
+# 因变量y：选用两套，一套是金牌数，一套是奖牌数。
+
+
+#预测的最大单位是国家，因此需要对国家进行分组，然后对每个国家进行预测
+#首先对国家进行分组，然后对每个国家进行预测
+
+import pandas as pd
+import numpy as np
+from sklearn.linear_model import LogisticRegression
+from sklearn.model_selection import train_test_split
+from sklearn.metrics import accuracy_score
+
+# 运动员记录，用于确定选了哪些运动员（以前）
+athlete_log = pd.read_csv('./data/summerOly_athletes.csv')#运动员往年比赛记录，往年运动员的列表是固定的，因此可以用来训练，未来的需要自己生成
+
+#东道主数据
+host = pd.read_csv('./data/hosts.csv')
+
+#NOC映射数据
+NOCmap=pd.read_csv('./data/noc_region.csv')
+
+#奖牌预期增量数
+medal_trend = pd.read_csv('./data/predict_medal_trend.csv')
+
+#预期投入人员数量增量数
+athlete_trend = pd.read_csv('./data/predict_athlete_number_variation.csv')
+
+#某项目优势系数
+advantage = pd.read_csv('./data/country_adeptness.csv')
+
+#国家level
+level = pd.read_csv('./data/country_level.csv')
+
+#某项目奖牌预期数量
+medal_count = pd.read_csv('./data/predict_medal_counts.csv')
+
+#某项目预期投入人员数量
+participant_count = pd.read_csv('./data/predict_participants.csv')
+
+#运动员因素
+athlete_arg=pd.read_csv('./data/athlete_args.csv')
+
+
+
+#一个个国家进行预测
[…]

### 2025-01-25 代码/预测各项目每年各国参赛人数变化趋势.py

@@ -57,10 +57,33 @@ for name, group in data.groupby(['NOC', 'Sport']):
     #预测
     predict = model.predict([[2028], [2032], [2036]])
     
-    #添加到result
+    #添加到result，注意需要包括
     result.append([name[0], name[1], predict[0][0], predict[1][0], predict[2][0]])
     
     
 #导出结果
 result = pd.DataFrame(result, columns=['NOC', 'Sport', '2028', '2032', '2036'])
-result.to_csv('./data/predict_participants.csv', index=False)
+
+#和原先的数据合并，注意原先的数据格式为
+# NOC,Sport,Year,Athletes
+# CHN,Basketball,1936,13
+# CHN,Basketball,1948,10
+# CHN,Basketball,1984,23
+# CHN,Basketball,1988,22
+#因此，合并result和data时，每一条result数据要拆分成3条数据，分别对应2028,2032,2036年，然后和data合并
+
+#拆分result
+result = pd.melt(result, id_vars=['NOC', 'Sport'], value_vars=['2028', '2032', '2036'], var_name='Year', value_name='Athletes')
+
+#合并
+data['Year'] = data['Year'].astype(str)
+result['Year'] = result['Year'].astype(str)
+data = pd.concat([data, result], axis=0)
+
+#排序数据，根据NOC和Sport排序
+data = data.sort_values(['NOC', 'Sport', 'Year'])
+#导出
+
+data.to_csv('./data/predict_participants.csv', index=False)
+
+#result.to_csv('./data/predict_participants.csv', index=False)

### 2025-01-25 代码/预测各项目每年奖牌数变化趋势.py

@@ -44,5 +44,12 @@ for index, row in data.iterrows():
 
 #导出结果
 result = pd.DataFrame(result, columns=['Sport', '2028', '2032', '2036'])
-result.to_csv('./data/predict_medal_counts.csv', index=False)
+
+#和原先的数据合并
+data = data.merge(result, on='Sport')
+
+#删除Discipline,Code,Sports Governing Body
+data.drop(['Discipline', 'Code', 'Sports Governing Body'], axis=1, inplace=True)
+
+data.to_csv('./data/predict_medal_counts.csv', index=False)
     

### 2025-01-25 代码/预测奖牌变化量.py

@@ -1,0 +1,32 @@
+#predict_medal_counts.csv
+#这个文件存放量奖牌的总数变化以及预测，现在我们需要获取每一届相对于上一届的奖牌数变化趋势（由于之前已经预测过，因此这里只需要计算实际的变化趋势即可）
+
+import pandas as pd
+import numpy as np
+
+# 读取数据
+data = pd.read_csv('./data/predict_medal_counts.csv')
+
+
+#示例数据
+# Sport,1896,1900,1904,1906,1908,1912,1920,1924,1928,1932,1936,1948,1952,1956,1960,1964,1968,1972,1976,1980,1984,1988,1992,1996,2000,2004,2008,2012,2016,2020,2024,2028,2032,2036
+# Aquatics,4,8,12,5,9,14,16,17,16.0,16.0,16.0,16.0,16.0,18.0,20.0,23.0,34.0,34.0,31.0,31.0,36.0,38.0,38.0,38.0,44.0,44.0,46.0,46.0,46.0,49.0,49.0,[50.25959823],[51.65834472],[53.0570912]
+# Archery,0,7,6,0,3,0,10,0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,2.0,2.0,2.0,2.0,4.0,4.0,4.0,4.0,4.0,4.0,4.0,4.0,5.0,5.0,[3.47247891],[3.53327976],[3.59408062]
+# Athletics,12,23,25,21,26,30,29,27,27.0,29.0,29.0,33.0,33.0,33.0,34.0,36.0,36.0,38.0,37.0,38.0,41.0,42.0,43.0,44.0,46.0,46.0,47.0,47.0,47.0,48.0,48.0,[50.40657292],[51.3049471],[52.20332128]
+# Badminton,0,0,0,0,0,0,0,0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,4.0,5.0,5.0,5.0,5.0,5.0,5.0,5.0,5.0,[4.33462435],[4.50825231],[4.68188027]
+
+
+#计算变化趋势
+result = []
+
+for index, row in data.iterrows():
+    #计算变化
+    trend = []
+    for i in range(1, len(row)-1):
+        trend.append(row[i + 1] - row[i])
+    result.append([row['Sport']] + trend)
+    
[…]

### 2025-01-25 代码/预测运动员数量变化量.py

@@ -1,0 +1,63 @@
+#athlete_number_variation.csv
+
+#在原来数据集的基础上，保留原来的数据，并进行线性回归，预测2028,2032,2036年运动员人数的变化趋势，导出csv文件，列为NOC,Sport,Year,Change
+
+#原始数据示例
+# NOC,Sport,Year,New,Leave
+# CHN,Basketball,1992,16,15
+# CHN,Basketball,2012,13,13
+# CHN,Basketball,1920,0,0
+# CHN,Basketball,1900,0,0
+# CHN,Basketball,1932,0,0
+# CHN,Basketball,1952,0,10
+# CHN,Basketball,2000,4,16
+# CHN,Basketball,1996,13,12
+# CHN,Basketball,1912,0,0
+# CHN,Basketball,1924,0,0
+# CHN,Basketball,1948,10,0
+# CHN,Basketball,2008,13,13
+
+#首先把New线性回归的变量，预测2028,2032,2036年的变化趋势，导出csv文件，列为NOC,Sport,Year,New,Leave,Leave为0
+import pandas as pd
+import numpy as np
+from sklearn.linear_model import LinearRegression
+# 读取数据
+data = pd.read_csv('./data/athlete_number_variation.csv')
+
+
+#创建模型
+model = LinearRegression()
+
+#创建一个DataFrame，用于存放预测结果
+result = []
+
+#对每一组数据进行拟合
+
+#groupby国家、项目
+
+for name, group in data.groupby(['NOC', 'Sport']):
+    #创建X，Y
+    X = group['Year'].values.reshape(-1, 1)
+    Y = group['New'].values.reshape(-1, 1)
+    
+    #训练模型
+    model.fit(X, Y)
+    
+    #预测
+    predict = model.predict([[2028], [2032], [2036]])
+    
+    #添加到result
+    result.append([name[0],name[1],2028,predict[0][0],0])
+    result.append([name[0],name[1],2032,predict[1][0],0])
+    result.append([name[0],name[1],2036,predict[2][0],0])
+    
+    
+#与原来的data合并
+result = pd.DataFrame(result, columns=['NOC', 'Sport', 'Year', 'New', 'Leave'])
+data = pd.concat([data,result])
+
+#排序数据
+
+data = data.sort_values(['NOC', 'Sport', 'Year'])
+data.to_csv('./data/predict_athlete_number_variation.csv', index=False)
+#导出结果

### 2025-01-25 论文/PAPER.tex
上传题目
latex论文添加了label 2

@@
 \usepackage{amsmath}
+\usepackage{tabularray}
 
@@
 \begin{abstract}
-
     Here is the abstract of your paper.
@@
 \section{Task1:}
-\subsubsection{Details about Model 1}
+\subsection{Details about Model 1}
 The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
@@
 
+%Table 2 : Variable Name
+\begin{longtblr}[
+	caption = {Variable Name},
+	]{
+		vline{1-4} = {1-10}{},
+		hline{1-11} = {1-3}{},
+	}
+	Variable Name                                                    & \textit{Code}                                                & Definition                                                                      &  \\
+	Whether~Host Country                                             & \textit{is host}                                             & {Whether the country is the host(1 for host,0 for\\~non-host)}                  &  \\
+	{Medal Expectation\\Increment *Personnel\\Expectation lncrement} & {\textit{medal\_increment *}\\\textit{personnel\_increment}} & {Product of medal\\expectation increment and\\personnel expectation\\increment} &  \\
+	{Sport Advantage\\Coefficient}                                 & \textit{sport\_adv}                                           & {Advantage coefficient of\\a specific sport}                                  &  \\
+	Country Level                                                    & \textit{country\_lvl}                                        & {The level of the country in the competition\\(ordered by rank)}                &  \\
+	{Project Medal\\Expectation /Project\\Personnel Expection~}                         & \textit{sport\_medal \_per\_ person}                          & {Ratio of sport medals to projected personnel\\for a specific sport}          &  \\
+	Gold Medal Probability                                           & \textit{gold\_prob}                                          & {Probability of an athlete~\\winning a gold medal}                              &  \\
+	{Silver Medal\\Probability}                                      & \textit{silver\_prob}                                        & Probability of an athlete~ winning a silver medal                               &  \\
+	{Bronze Medal\\Probability}                                      & \textit{silver\_prob}                                        & Probability of an athletewinning a bronze medal                                 &  \\
+	No Medal Probability                                             & \textit{no\_medal\_probe}                                    & Probability of an athlete winning no medal                                      &  \\
+	&                                                              &                                                                                 &  \\
+	&                                                              &                                                                                 &  
+\end{longtblr}
+
 \section{Task2:}
@@
 % 您也可以选择自行载入 tabularx 宏包，并通过 X 参数指定对应列自动换行
-\begin{longtable}{ p{4em} p{14em} p{14em} }
-\caption{Basic Information about Three Main Continents (scratched from Wikipedia)}
-\label{tb:longtable}\\
-\toprule
-Continent & Description & Information \\
-\midrule
-Africa & Africa Continent is surrounded by the Mediterranean Sea to the
-north, the Isthmus of Suez and the Red Sea to the northeast, the Indian
-Ocean to the southeast and the Atlantic Ocean to the west. &
-At about 30.3 million km$^2$ including adjacent islands, it covers 6\%
-of Earth's total surface area and 20\% of its land area. With 1.3
-billion people as of 2018, it accounts for about 16\% of the world's
-human population. \\
-\midrule
-Asia & Asia is Earth's largest and most populous continent which
-located primarily in the Eastern and Northern Hemispheres.
-It shares the continental landmass of Eurasia with the continent
-of Europe and the continental landmass of Afro-Eurasia with both
-Europe and Africa. &
-Asia covers an area of 44,579,000 square kilometres, about 30\%
-of Earth's total land area and 8.7\% of the Earth's total surface
-area. Its 4.5 billion people (as of June 2019) constitute roughly
-60\% of the world's population. \\
-\midrule
-Europe & Europe is a continent located entirely in the Northern
-Hemisphere and mostly in the Eastern Hemisphere. It comprises the
-westernmost part of Eurasia and is bordered by the Arctic Ocean to
-the north, the Atlantic Ocean to the west, the Mediterranean Sea to
-the south, and Asia to the east. &
-Europe covers about 10,180,000 km$^2$, or 2\% of the Earth's surface
-(6.8\% of land area), making it the second smallest
-continent. Europe had a total population of about 741 million (about
-11\% of the world population) as of 2018. \\
-\bottomrule
-\end{longtable}
 

### 2025-01-25 论文/PAPER.tex
论文更新

--- 2025-01-23 论文/PAPER.tex
@@
 
-\section{Assumptions}
+\section{Assumptions and Notations}
 
-\section{Notations}
 The primary notations used in this paper are listed in Table \ref{tb:notation}.
@@
 
-\section{Task4}
-
 \section{Sensitivity Analysis}

### 2025-01-25 代码/Q1逻辑回归模型.py
q1，以及若干图表

@@ -1,94 +1,0 @@
-#最终要得到的表格列头是，NOC,Year,Golds,Medals
-# 主要模型：逻辑回归
-
-# 自变量X：
-# （国家因素）
-# 1.是否为东道主
-# 2.奖牌预期增量数（注意是增量数）*预期投入人员数量增量数（注意是增量数）
-# 3.某项目优势系数
-# 4.国家level（需要对level排序）
-# 5.某项目奖牌预期数量/某项目预期投入人员数量
-# p.s.对于小国家，变量2要给予相应奖励权重，即，有可能随着比赛奖项扩招，而小国家出现“黑马”的情况
-# （运动员因素）
-# 1.金牌概率
-# 2.银牌概率
-# 3.铜牌概率
-# 4.无牌概率
-
-# 因变量y：选用两套，一套是金牌数，一套是奖牌数。
-
-
-#预测的最大单位是国家，因此需要对国家进行分组，然后对每个国家进行预测
-#首先对国家进行分组，然后对每个国家进行预测
-
-import pandas as pd
-import numpy as np
-from sklearn.linear_model import LogisticRegression
-from sklearn.model_selection import train_test_split
-from sklearn.metrics import accuracy_score
-
-# 运动员记录，用于确定选了哪些运动员（以前）
-athlete_log = pd.read_csv('./data/summerOly_athletes.csv')#运动员往年比赛记录，往年运动员的列表是固定的，因此可以用来训练，未来的需要自己生成
-
-#东道主数据
-host = pd.read_csv('./data/hosts.csv')
-
-#NOC映射数据
-NOCmap=pd.read_csv('./data/noc_region.csv')
-
-#奖牌预期增量数
-medal_trend = pd.read_csv('./data/predict_medal_trend.csv')
-
-#预期投入人员数量增量数
-athlete_trend = pd.read_csv('./data/predict_athlete_number_variation.csv')
-
-#某项目优势系数
-advantage = pd.read_csv('./data/country_adeptness.csv')
-
-#国家level
-level = pd.read_csv('./data/country_level.csv')
-
-#某项目奖牌预期数量
-medal_count = pd.read_csv('./data/predict_medal_counts.csv')
-
-#某项目预期投入人员数量
-participant_count = pd.read_csv('./data/predict_participants.csv')
-
-#运动员因素
-athlete_arg=pd.read_csv('./data/athlete_args.csv')
-
-
-
-#一个个国家进行预测
[…]

### 2025-01-25 代码/不同运动员服役年限分布.py

@@ -28,24 +28,70 @@ result = result[result['Year'] <= 40]
 
 # 描述统计
 print(result.describe())
+#字体改成Times New Roman
+plt.rcParams['font.sans-serif'] = ['Times New Roman']
+plt.rcParams['axes.unicode_minus'] = False
+
+plt.xticks(fontsize=15)
+plt.yticks(fontsize=15)
+
+
+#网格线加粗，黑色
+plt.grid(linestyle='--', linewidth=0.5, color='black')
+
+
+#坐标系内的背景色变成淡灰色，而不是外部的图表背景色
+plt.gca().set_facecolor('#f0f0f0')
 
 
 #分布拟合，使用核密度估计，绘制核密度图,查看分布情况
-sns.kdeplot(result['Year'], shade=True)
-plt.xlabel('Serve Years')
-plt.ylabel('Density')
-plt.title('Distribution of Serve Years')
+density=sns.kdeplot(result['Year'], shade=True,color='#4c78a8',linewidth=1.5)
+
+
+
+#根据核密度估计，再画一条密度累积曲线，要覆盖面积
+sns.kdeplot(result['Year'], cumulative=True,color='#439894',linewidth=2)
+
+from scipy.signal import find_peaks
+from scipy.stats import gaussian_kde
+# 使用 gaussian_kde 进行核密度估计
+kde = gaussian_kde(result['Year'], bw_method=0.5)  # 可以调整bw_method以改变平滑度
+x_vals = np.linspace(result['Year'].min(), result['Year'].max(), 1000)  # 生成更多的x值
+y_vals = kde(x_vals)  # 计算相应的y值
+# 找到峰值位置
+peaks, _ = find_peaks(y_vals)
+
+# 在每个峰值位置绘制星号
+for peak in peaks:
+    plt.scatter(x_vals[peak], 0.76, color='#e55756', marker='*', s=200, zorder=5)
+
+
+#宽度变大
+plt.xlim(0, 40)
+
+#添加均值线
+plt.axvline(result['Year'].mean(), linestyle='--', linewidth=2,color='#79706e')
+
+#图例
+plt.legend(['Density','Cumulative Density','Peak','Mean'],fontsize=17)
+
+
+plt.xlabel('Serve Years',fontsize=17)
+plt.ylabel('Density',fontsize=17)
+plt.title('Distribution of Serve Years',fontsize=20)
 plt.show()
 
-#验证是否符合帕累托分布，绘制累积分布函数图
-result = result.sort_values('Year')
[…]

### 2025-01-25 论文/PAPER.tex
更新了latex

--- 2025-01-25 论文/PAPER.tex
@@
 
-\title{An MCM Paper Made by Team 1234567}  % 标题
+%拉取的一些宏包
+\usepackage{graphicx} 
+%\usepackage{pdfpages}
+\usepackage{longtable}
+%\usepackage{tabu}
+\usepackage{threeparttable} %支持在表格中使用 \tnote 命令添加脚注，并自动编号
+\usepackage{listings} %在文档中插入代码
+%\usepackage{paralist}%创建紧凑的列表，节省垂直空间
+%\usepackage{setspace} %调整文档的行间距
+%\usepackage{booktabs}%用于创建更美观的表格，提供了高质量的表格线条命令，如 \toprule、\midrule 和 \bottomrule
+%\usepackage{makecell} %创建多行单元格，支持复杂的表格布局
+\usepackage{amssymb} %提供了额外的数学符号，通常与 amsmath 宏包一起使用
+\usepackage{appendix} %管理附录部分，自动处理附录的编号和格式
+\newcommand{\upcite}[1]{\textsuperscript{\textsuperscript{\cite{#1}}}}
+
+\title{Together, Individuals Make a Difference}  % 标题
 
@@
     % \textbf{Keywords}: MATLAB, mathematics, LaTeX.
-\begin{keywords}
-\end{keywords}
+
+    \textbf{PCA}\\
+    \%\\
+    % 关键字Keywords
+    \vspace{5pt}
+    \textbf{Keywords}: \textbf{ A, B, C,  }
+
 \end{abstract}
@@
 \subsection{Problem Background}
-Here is the problem background ...
-
-Two major problems are discussed in this paper, which are:
-\begin{itemize}
-    \item Doing the first thing.
-    \item Doing the second thing.\\doing\\    doing11
-
-\end{itemize}
 
@@
 A literatrue\cite{1} say something about this problem ...
+There is a conception named "momentum" in tennis, which has a great impact on players' performance.
+It is a generalization of the influence in manifold aspects like mental stress and residual energy.
+So the fluctuation of momentum is the most probable factor that reveals the trend of match.
+However,the momentum is not easy to be quantified for it includes many subjective indicators, and there are few models that can be directly used, so we decide to cut in the following questions from statistical analysis and data procession:
+
+\begin{itemize}
+	\setlength{\parsep}{0ex} %段落间距
+	\setlength{\topsep}{2ex} %列表到上下文的垂直距离
+	\setlength{\itemsep}{1ex} %条目间距
+	\item Develop a model that captures the flow of play as points occur and apply it to one or more of the matches.
+Your model should identify which player is performing better at a given time in the match, as well as how much better they are performing.
+Provide a visualization based on your model to depict the match flow.
+\textit{Note: in tennis, the player serving has a much higher probability of winning the point/game.
+You may wish to factor this into your model in some way.}
+	\item A tennis coach is skeptical that “momentum” plays any role in the match.
+Instead, he postulates that swings in play and runs of success by one player are random.
+Use your model/metric to assess this claim.
+	\item Coaches would love to know if there are indicators that can help determine when the flow of play is about to change from favoring one player to the other.
+	\begin{itemize}
+		\item[1)]
+		Using the data provided for at least one match, develop a model that predicts these swings in the match. What factors seem most related (if any)?
+	\end{itemize}
+	\begin{itemize}
+		\item[2)]
+		Given the differential in past match “momentum” swings how do you advise a player going into a new match against a different player?
+	\end{itemize}
+	\item Test the model you developed on one or more of the other matches.
+How well do you predict the swings in the match?
+If the model performs poorly at times, can you identify any factors that might need to be included in future models?
+How generalizable is your model to other matches (such as Women’s matches), tournaments, court surfaces, and other sports such as table tennis.
+	\item Produce a report of no more than 25 pages with your findings and include a one- to two-page memo summarizing your results with advice for coaches on the role of“momentum”, and how to prepare players to respond to events that impact the flow of play during a tennis match.
+\end{itemize}
 
@@
 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\textwidth]{Percentage of Medals of Different Sports in China.svg}
+%	\caption{Flow Chart of Our Work}
+%	\label{img}
+%\end{figure}
+	\caption{The result of Model 2}\label{fig:result}
+\end{figure}
+%"C:\Users\于灏文1\Desktop\2025_codium_veritas_2506135\论文\img\Percentage of Medals of Different Sports in China.svg"
+%"C:\Users\于灏文1\Desktop\2025_codium_veritas_2506135\论文\img\每届奥运会新增和退役的人数.png"
+%"C:\Users\于灏文1\Desktop\2025_codium_veritas_2506135\论文\img\water.png"
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.8\textwidth]{water.png}
+	\caption{The result of Model 2}\label{fig:result}
+\end{figure}
 \begin{enumerate}[\bfseries 1.]
@@
 	$\alpha$ &the last one\\
+	$\sum m_{c_{i} S_{j}}$ &the last one\\
 	\bottomrule

### 2025-01-25 代码/Q1可能第一次获得奖牌的小国.py
若干进展

@@ -1,0 +1,145 @@
+#如果某种比赛的奖牌数有上升趋势，并且尚未获得奖牌的国家，曾参与过该种比赛
+#那么该国家有可能在未来的比赛中获得奖牌
+
+#首先获取所有奖牌数有上升趋势的比赛项目
+
+
+import pandas as pd
+import numpy as np
+
+#读取数据
+data = pd.read_csv('./data/predict_medal_trend.csv')
+
+trending_sports = data[data['2028'] > 0]
+trending_sports = trending_sports[['Sport','2028']]
+print(trending_sports)
+
+#获取所有尚未获得奖牌的国家
+data = pd.read_csv('./data/summerOly_athletes.csv')
+countries = data['NOC'].unique()
+
+sports=data['Sport'].unique()
+# #如果有一个国家的所有运动员参与的比赛，都是No medal,就说明从未获得过奖牌
+# no_medal_countries = []
+# idx=0
+# for country in countries:
+#     idx+=1
+#     print(idx,"/",len(countries))
+#     has_medal = False
+#     for sport in sports:
+#         medals=data[(data['NOC'] == country) & (data['Sport'] == sport)]['Medal']
+#         if medals is not None and ('Gold' in medals.values or 'Silver' in medals.values or 'Bronze' in medals.values):
+#             has_medal = True
+#             break
+#     if not has_medal:
+        
+#         taken_part_sports = data[data['NOC'] == country]['Sport'].unique()
+#         #统计每个项目的参与人次
+#         taken_part_info = []
+#         for sport in taken_part_sports:
+#             times=len(data[(data['NOC'] == country) & (data['Sport'] == sport)])
+#             taken_part_info.append((sport,times))
+        
+#         no_medal_countries.append((country,taken_part_info))
+#         print((country,taken_part_info))
+
+# print(no_medal_countries)
+# #保存结果
+# result = pd.DataFrame(no_medal_countries,columns=['NOC','Sport'])
+# result.to_csv('./data/no_medal_countries.csv',index=False)
+
+# #读取数据
+# no_medal_countries = pd.read_csv('./data/no_medal_countries.csv')
+
+# print(no_medal_countries)
+
+# #计算每个国家首次获奖的可能性
+
+# probs = []
[…]

### 2025-01-26 论文/PAPER.tex
上传了图片
流程图

@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{Percentage of Medals of Different Sports in China.svg}
-%	\caption{Flow Chart of Our Work}
-%	\label{img}
+%图片示例（water.png）
+%\begin{figure}[htbp]
+%	\centering
+%	\includegraphics[width=.8\textwidth]{water.png}
+%	\caption{The result of Model 2}\label{fig:result}
 %\end{figure}
-	\caption{The result of Model 2}\label{fig:result}
-\end{figure}
-%"C:\Users\于灏文1\Desktop\2025_codium_veritas_2506135\论文\img\Percentage of Medals of Different Sports in China.svg"
-%"C:\Users\于灏文1\Desktop\2025_codium_veritas_2506135\论文\img\每届奥运会新增和退役的人数.png"
-%"C:\Users\于灏文1\Desktop\2025_codium_veritas_2506135\论文\img\water.png"
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=.8\textwidth]{water.png}
-	\caption{The result of Model 2}\label{fig:result}
-\end{figure}
 \begin{enumerate}[\bfseries 1.]
@@
 \section{Notations}
+
 The primary notations used in this paper are listed in Table \ref{tb:notation}.
@@
 	\midrule
-	$A$&the first one\\
-	$b$&the second one\\
-	$\alpha$ &the last one\\
-	$\sum m_{c_{i} S_{j}}$ &the last one\\
+	$C_{i}$&the first one\\
+	$S_{i}$&the second one\\
+	$G$&the second one\\
+	$V$&the second one\\
+	$B$&the second one\\
+	$M$&the second one\\
+	$A$&the second one\\
+	$D$&the second one\\
+	$E$&the second one\\
+%	$\alpha$ &the last one\\
+    $\gamma$&Sport Advantagen Coefficient\\
+  	$ m_{c_{i}}$ &the second one\\
+	$ m_{c_{i} s_{j}}$ &the second one\\
+    $g_{i}$&the second one\\
+    $\xi$&The Probability of First Medal\\
 	\bottomrule
@@
 \subsection{Basic Data Preprocessing}
+
+$$G_{i} \cap G_{j}=\emptyset, \bigcup_{i=1}^{5} G_{i}=X$$
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/Level1.png}
+	\caption{Scatter plot of national level classification (based on Kmeans++clustering algorithm)}
+	\label{fig:aa}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/Level2.png}
+	\caption{aa}
+	\label{fig:aa}
+\end{figure}
+
 \subsection{Data Mining}
@@
 $$\alpha$$
+
+%$$ \gamma=\frac{$m_{c_{i} s_{j}}$}{$\sum m_{c_{i} s_{j}}$ }$$
+
+%\[
+%\gamma = \frac{$m_{c_i s_j}$}{$\sum m_{c_i s_j}$}
+%\]
+\[
+\gamma = \frac{m_{c_i s_j}}{\sum m_{c_i s_j}}
+\]
 

### 2025-01-26 代码/Q1可能第一次获得奖牌的小国.py
update

@@ -141,7 +141,7 @@ img = plt.imread('logo.png')
 plt.figimage(img, 1800, 900, zorder=3)
 plt.xticks(rotation=45)
 plt.xlabel('Country',fontsize=20)
-plt.ylabel('ξ',fontsize=20,rotation=0)
+plt.ylabel('κ',fontsize=20,rotation=0)
 #y标签也应该竖直排列，因此设置rotation
 
 plt.gca().set_facecolor('#f0f0f0')

### 2025-01-26 论文/PAPER.tex
重命名图片

@@
 \subsection{Data Mining}
+\subsubsection{Athlete Service Status}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/Number.png}
+	\caption{Number of New and Leave Athletes in Each Year}
+	\label{fig:aa}
+\end{figure}
+
+% 子图（多图并列）示例，更多用法请参考 subfigure 宏包文档
+% 如果您只希望几张图并列，不需要额外的 caption，那么在 figure 环境中
+% 连续插入总宽度不超过 \textwidth 的多个 \includegraphics 命令即可
+\begin{figure}[htbp]
+	\centering
+	\begin{subfigure}[b]{.5\textwidth}
+		\includegraphics[width=\textwidth]{img/Times.png}
+		\caption{Distribution of Serve Times}\label{subfig:left}
+	\end{subfigure}
+	\begin{subfigure}[b]{.5\textwidth}
+		\includegraphics[width=\textwidth]{img/Years.png}
+		\caption{Distribution of Serve Years}\label{subfig:right}
+	\end{subfigure}
+	\caption{Two images}\label{fig:subfigures}
+\end{figure}
+
+\subsubsection{Distribution of Countries' Strength Sports}
+
 \section{Task1:}
-\subsection{Details about Model 1}
+\subsection{Medal Standings}
 The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
@@
 
-%$$ \gamma=\frac{$m_{c_{i} s_{j}}$}{$\sum m_{c_{i} s_{j}}$ }$$
-
-%\[
-%\gamma = \frac{$m_{c_i s_j}$}{$\sum m_{c_i s_j}$}
-%\]
 \[
@@
 \end{longtblr}
+
+\subsection{Countries that Win Their First Medal}
+
+\subsection{Events and Medal Counts by Countries}
+
+\begin{figure}[htbp]
+	\centering
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{img/Table Tennis.png}
+		\caption{Heatmap of Correlation for Table Tennis in China}\label{subfig:1}
+	\end{subfigure}
+	\hfill 
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{img/Jamaica.png}
+		\caption{ Heatmap of Correlation for Athletics in Jamaica}\label{subfig:2}
+	\end{subfigure}
+	\hfill 
+	\begin{subfigure}[b]{.32\textwidth}
+		\includegraphics[width=\textwidth]{img/New Zealand.png}
+		\caption{Heatmap of Correlation for Rowing in New Zealand}\label{subfig:3}
+	\end{subfigure}
+	\caption{Three images}\label{fig:subfigures}
+\end{figure}
 

### 2025-01-26 论文/PAPER.tex
重命名图片

@@
 \end{enumerate}
+\section{Question Preparation}
+\subsection{Assumptions}
 
-\section{Assumptions}
-
-\section{Notations}
+\subsection{Notations}
 
@@
 	\centering
-	\begin{subfigure}[b]{.5\textwidth}
+	\begin{subfigure}[b]{.55\textwidth}
 		\includegraphics[width=\textwidth]{img/Times.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{.5\textwidth}
+	\begin{subfigure}[b]{.4\textwidth}
 		\includegraphics[width=\textwidth]{img/Years.png}
@@
 
-\section{Task1:}
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/Percentage.jpg}
+	\caption{Percentage of Medals of Different Sports in China}
+	\label{fig:aa}
+\end{figure}
+
+\section{Task1:Medal Prediction Model Based on LightGBM}
 \subsection{Medal Standings}
@@
 
+%奖牌榜预测图
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/Medal count prediction.svg}
+	\caption{Medal count prediction}
+	\label{fig:aa}
+\end{figure}
+
 \subsection{Countries that Win Their First Medal}
+
+%首奖可能性图
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=16cm]{img/First.png}
+	\caption{The Probability of First Medal in 2028}
+	\label{fig:aa}
+\end{figure}
 
@@
 
+%三个国家擅长项目的图
 \begin{figure}[htbp]
@@
 \section{Task2:}
-\subsection{Conclusion of Model 2}
+
 The results are shown in Figure \ref{fig:result}, where $t$ denotes the time in seconds, and $c$ refers to the concentration of water in the boiler.
@@
 \clearpage
-\subsection{Commetary on Model 2}
-The instance of long and wide tables are shown in Table \ref{tb:longtable}.
 
-% 长表格示例，更多用法请参考 longtable 宏包文档
-% 以下环境及对应参数可实现表格内的自动换行与表格的自动断页
-% 您也可以选择自行载入 tabularx 宏包，并通过 X 参数指定对应列自动换行
-
-Figure \ref{fig:subfigures} gives an example of subfigures. Figure \ref{subfig:left} is on the left, and Figure \ref{subfig:right} is on the right.
-
-% 子图（多图并列）示例，更多用法请参考 subfigure 宏包文档
-% 如果您只希望几张图并列，不需要额外的 caption，那么在 figure 环境中
-% 连续插入总宽度不超过 \textwidth 的多个 \includegraphics 命令即可
-\begin{figure}[htbp]
-\centering
-\begin{subfigure}[b]{.4\textwidth}
-\includegraphics[width=\textwidth]{water.png}
-\caption{Image on the left}\label{subfig:left}
-\end{subfigure}
-\begin{subfigure}[b]{.4\textwidth}
-\includegraphics[width=\textwidth]{water.png}
-\caption{Image on the right}\label{subfig:right}
-\end{subfigure}
-\caption{Two images}\label{fig:subfigures}
-\end{figure}
+%引用图像示例Figure \ref{fig:subfigures}
+%Figure \ref{fig:subfigures} gives an example of subfigures. Figure \ref{subfig:left} is on the left, and Figure \ref{subfig:right} is on the right.
 

### 2025-01-26 论文/PAPER.tex
图片
论文

@@
 \usepackage{tabularray}
-
 %拉取的一些宏包
@@
 	\centering
-	\includegraphics[width=12cm]{img/Medal count prediction.svg}
+	\includegraphics[width=12cm]{img/Predict.png}
 	\caption{Medal count prediction}
@@
 \end{figure}
+
+% \usepackage{longtable}
+
+\begin{longtable}{l|c|c|c|c|c|c|c|c|c|c}
+	Country              & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}G\_\\pes.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}S\_\\pes.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}B\_\\pes.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}G\_\\opt.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}S\_\\opt.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}B\_\\opt.\end{tabular}} & \multicolumn{1}{l|}{Gold} & \multicolumn{1}{l|}{Silver} & \multicolumn{1}{l|}{Bronze} & \multicolumn{1}{l}{Total}  \endfirsthead
+	\hline
+	United States        & 47                                                                     & 36                                                                     & 23                                                                     & 53                                                                     & 41                                                                     & 25                                                                     & 51                        & 40                          & 25                          & 117                        \\
+	\hline
+	China                & 35                                                                     & 35                                                                     & 15                                                                     & 46                                                                     & 38                                                                     & 20                                                                     & 40                        & 36                          & 17                          & 95                         \\
+	\hline
+	Australia            & 28                                                                     & 20                                                                     & 22                                                                     & 33                                                                     & 24                                                                     & 24                                                                     & 29                        & 22                          & 23                          & 71                         \\
+	\hline
+	France               & 23                                                                     & 19                                                                     & 19                                                                     & 27                                                                     & 20                                                                     & 22                                                                     & 24                        & 19                          & 21                          & 64                         \\
+	\hline
+	Germany              & 18                                                                     & 24                                                                     & 14                                                                     & 23                                                                     & 26                                                                     & 16                                                                     & 21                        & 25                          & 15                          & 61                         \\
+	\hline
+	United Kingdom       & 20                                                                     & 19                                                                     & 14                                                                     & 26                                                                     & 24                                                                     & 15                                                                     & 25                        & 21                          & 15                          & 61                         \\
+	\hline
+	Japan                & 16                                                                     & 25                                                                     & 14                                                                     & 19                                                                     & 27                                                                     & 16                                                                     & 17                        & 26                          & 16                          & 58                         \\
+	\hline
+	Italy                & 15                                                                     & 20                                                                     & 15                                                                     & 17                                                                     & 20                                                                     & 22                                                                     & 16                        & 20                          & 16                          & 53                         \\
+	\hline
+	Spain                & 21                                                                     & 10                                                                     & 13                                                                     & 30                                                                     & 12                                                                     & 14                                                                     & 25                        & 12                          & 13                          & 50                         \\
+	\hline
+	Netherlands          & 24                                                                     & 6                                                                      & 13                                                                     & 29                                                                     & 9                                                                      & 15                                                                     & 26                        & 8                           & 15                          & 47                         \\
+	\hline
+	New Zealand          & 20                                                                     & 13                                                                     & 9                                                                      & 22                                                                     & 15                                                                     & 10                                                                     & 22                        & 14                          & 9                           & 45                         \\
+	\hline
+	...
+& ..
+& ..
+& ..
+& ..
+& ..
+& ..
+& ..
+& ..
+& ..
+& ..
+\\
+	\multicolumn{1}{l}{} & \multicolumn{1}{c}{}                                                   & \multicolumn{1}{c}{}                                                   & \multicolumn{1}{c}{}                                                   & \multicolumn{1}{c}{}                                                   & \multicolumn{1}{c}{}                                                   & \multicolumn{1}{c}{}                                                   & \multicolumn{1}{c}{}      & \multicolumn{1}{c}{}        & \multicolumn{1}{c}{}        &
+\end{longtable}
 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.8\textwidth]{water.png}
-\caption{The result of Model 2}\label{fig:result}
-\end{figure}
-
 \clearpage
@@
 
+% \usepackage{longtable}
+
+\begin{longtable}{l|l|l|l|l} 
+	\caption{Model Performances(LightGBM)}\\ 
+	\hline
+	\multicolumn{1}{c|}{\textbf{Model}} & \multicolumn{1}{c|}{\textbf{MSE}} & \multicolumn{1}{c|}{\textbf{RMSE}} & \multicolumn{1}{c|}{\textbf{MAE}} & \multicolumn{1}{c}{\(\mathbf{R}^2\)}  \endfirsthead 
+	\hline
+	Gold Prediction                     & 0.0235                            & 0.180                              & 0.030                             & 0.690                              \\ 
+	\hline
+	Silver Prediction                   & 0.0239                            & 0.185                              & 0.033                             & 0.625                              \\ 
+	\hline
+	Bronze Prediction                   & 0.0231                            & 0.187                              & 0.034                             & 0.606                              \\
+	\hline
+\end{longtable}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=16cm]{img/Performance.png}
+	\caption{Model Performance Radar Chart}
+	\label{fig:aa}
+\end{figure}
+
 \section{Task3}
 
+%公式代码集合
+
+\[
+\mathcal{L} = \sum_{i=1}^{n} L(y_i, \hat{y}_i^{(m-1)} + \eta f_m(x_i)) + \Omega(f_m)
+\]
+
+$y_i$\\
+$\hat{y}_i^{(m-1)}$\\
+$\eta f_m(x_i)$\\
+$\Omega(f_m)$\\
+
+\[
+\kappa = 0.8 \times \frac{\xi - \overline{\xi}}{\sigma}
+\]
+$\overline{\xi}$
+$\sigma$
+
+\[
+d_i = R(X_i) - R(Y_i)
+\]
+\[
+R_s = 1 - \frac{6 \sum d_i^2}{n(n^2 - 1)}
+\]
+$d_i$
+$R_s$
+
+\[
+P(c_k \mid X) = \frac{P(X \mid c_k) P(c_k)}{P(X)}
+\]
+
+\[
+	C_t^+ = \max(0, C_{t-1}^+ + (X_t - \mu - k))
+\]
+
+$C_t^+ $
 \section{Task4}
@@
 \section{Appendix A: Further on \LaTeX}
-To clarify the importance of using \LaTeX\ in MCM or ICM, several points need to be covered, which are \ldots
+% \usepackage{longtable}
 
-To be more specific, \ldots
-
-All in all, \ldots
-
-Anyway, nobody \textbf{really} needs such appendix \ldots
+\begin{longtable}{|l|l|l|l|l|l|l|l|l|l|l|} 
+	\hline
+	Country                                                        & \begin{tabular}[c]{@{}l@{}}G\_\\pes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}S\_\\pes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}B\_\\pes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}G\_\\opt.\end{tabular} & \begin{tabular}[c]{@{}l@{}}S\_\\opt.\end{tabular} & \begin{tabular}[c]{@{}l@{}}B\_\\opt.\end{tabular} & Gold & Silver & Bronze & Total  \endfirsthead
+	\hline
+	United States                                                  & 47                                                & 36                                                & 23                                                & 53                                                & 41                                                & 25                                                & 51   & 40     & 25     & 117    \\
+	\hline
+	China                                                          & 35                                                & 35                                                & 15                                                & 46                                                & 38                                                & 20                                                & 40   & 36     & 17     & 95     \\
+	\hline
+	Australia                                                      & 28                                                & 20                                                & 22                                                & 33                                                & 24                                                & 24                                                & 29   & 22     & 23     & 71     \\
+	\hline
+	France                                                         & 23                                                & 19                                                & 19                                                & 27                                                & 20                                                & 22                                                & 24   & 19     & 21     & 64     \\
+	\hline
+	Germany                                                        & 18                                                & 24                                                & 14                                                & 23                                                & 26                                                & 16                                                & 21   & 25     & 15     & 61     \\
+	\hline
+	United Kingdom                                                 & 20                                                & 19                                                & 14                                                & 26                                                & 24                                                & 15                                                & 25   & 21     & 15     & 61     \\
+	\hline
+	Japan                                                          & 16                                                & 25                                                & 14                                                & 19                                                & 27                                                & 16                                                & 17   & 26     & 16     & 58     \\
+	\hline
+	Italy                                                          & 15                                                & 20                                                & 15                                                & 17                                                & 20                                                & 22                                                & 16   & 20     & 16     & 53     \\
+	\hline
+	Spain                                                          & 21                                                & 10                                                & 13                                                & 30                                                & 12                                                & 14                                                & 25   & 12     & 13     & 50     \\
+	\hline
+	Netherlands                                                    & 24                                                & 6                                                 & 13                                                & 29                                                & 9                                                 & 15                                                & 26   & 8      & 15     & 47     \\
+	\hline
+	New Zealand                                                    & 20                                                & 13                                                & 9                                                 & 22                                                & 15                                                & 10                                                & 22   & 14     & 9      & 45     \\
+	\hline
+	Canada                                                         & 15                                                & 10                                                & 16                                                & 19                                                & 10                                                & 18                                                & 17   & 10     & 16     & 43     \\
+	\hline
+	Brazil                                                         & 8                                                 & 10                                                & 13                                                & 8                                                 & 11                                                & 15                                                & 8    & 10     & 14     & 32     \\
+	\hline
+	Belgium                                                        & 6                                                 & 8                                                 & 7                                                 & 15                                                & 10                                                & 8                                                 & 11   & 8      & 7      & 26     \\
+	\hline
+	Hungary                                                        & 7                                                 & 6                                                 & 8                                                 & 8                                                 & 8                                                 & 9                                                 & 8    & 8      & 9      & 25     \\
+	\hline
+	Poland                                                         & 10                                                & 7                                                 & 6                                                 & 12                                                & 10                                                & 8                                                 & 11   & 9      & 6      & 25     \\
+	\hline
+	Ireland                                                        & 6                                                 & 10                                                & 6                                                 & 7                                                 & 11                                                & 6                                                 & 6    & 10     & 6      & 23     \\
+	\hline
+	Argentina                                                      & 4                                                 & 8                                                 & 7                                                 & 5                                                 & 10                                                & 9                                                 & 4    & 9      & 8      & 22     \\
+	\hline
+	Denmark                                                        & 10                                                & 7                                                 & 5                                                 & 12                                                & 8                                                 & 8                                                 & 10   & 8      & 6      & 22     \\
+	\hline
+	Ukraine                                                        & 3                                                 & 7                                                 & 8                                                 & 5                                                 & 8                                                 & 9                                                 & 4    & 8      & 8      & 21     \\
+	\hline
+	South Korea                                                    & 10                                                & 5                                                 & 4                                                 & 12                                                & 6                                                 & 4                                                 & 11   & 6      & 4      & 21     \\
+	\hline
+	Romania                                                        & 10                                                & 7                                                 & 3                                                 & 12                                                & 8                                                 & 3                                                 & 12   & 7      & 3      & 20     \\
+	\hline
+	Norway                                                         & 11                                                & 1                                                 & 4                                                 & 11                                                & 3                                                 & 6                                                 & 11   & 2      & 6      & 19     \\
+	\hline
+	South Africa                                                   & 6                                                 & 4                                                 & 4                                                 & 8                                                 & 8                                                 & 5                                                 & 8    & 7      & 5      & 18     \\
+	\hline
+	Slovenia                                                       & 4                                                 & 3                                                 & 8                                                 & 6                                                 & 3                                                 & 8                                                 & 4    & 3      & 8      & 17     \\
+	\hline
+	Kenya                                                          & 5                                                 & 4                                                 & 4                                                 & 5                                                 & 7                                                 & 5                                                 & 5    & 7      & 4      & 16     \\
+	\hline
+	Serbia                                                         & 4                                                 & 5                                                 & 6                                                 & 5                                                 & 9                                                 & 7                                                 & 4    & 8      & 6      & 16     \\
+	\hline
+	Mexico                                                         & 4                                                 & 4                                                 & 3                                                 & 6                                                 & 4                                                 & 5                                                 & 5    & 4      & 4      & 15     \\
+	\hline
+	India                                                          & 1                                                 & 1                                                 & 4                                                 & 8                                                 & 4                                                 & 5                                                 & 7    & 3      & 4      & 15     \\
+	\hline
+	Greece                                                         & 3                                                 & 4                                                 & 2                                                 & 7                                                 & 4                                                 & 3                                                 & 7    & 4      & 3      & 14     \\
+	\hline
+	Switzerland                                                    & 2                                                 & 4                                                 & 5                                                 & 5                                                 & 4                                                 & 6                                                 & 4    & 4      & 6      & 14     \\
+	\hline
+	Jamaica                                                        & 1                                                 & 7                                                 & 2                                                 & 5                                                 & 12                                                & 3                                                 & 4    & 8      & 2      & 13     \\
+	\hline
+	Czech Republic                                                 & 5                                                 & 3                                                 & 3                                                 & 6                                                 & 4                                                 & 5                                                 & 6    & 4      & 4      & 13     \\
+	\hline
+	Uzbekistan                                                     & 4                                                 & 2                                                 & 2                                                 & 5                                                 & 3                                                 & 2                                                 & 4    & 2      & 2      & 10     \\
+	\hline
+	Nigeria                                                        & 4                                                 & 2                                                 & 4                                                 & 4                                                 & 3                                                 & 4                                                 & 4    & 2      & 4      & 10     \\
+	\hline
+	Sweden                                                         & 4                                                 & 4                                                 & 2                                                 & 5                                                 & 5                                                 & 5                                                 & 4    & 4      & 2      & 10     \\
+	\hline
+	Turkey                                                         & 3                                                 & 2                                                 & 5                                                 & 3                                                 & 2                                                 & 6                                                 & 3    & 2      & 5      & 10     \\
+	\hline
+	Finland                                                        & 2                                                 & 6                                                 & 2                                                 & 2                                                 & 6                                                 & 2                                                 & 2    & 6      & 2      & 10     \\
+	\hline
+	Colombia                                                       & 5                                                 & 2                                                 & 0                                                 & 5                                                 & 3                                                 & 1                                                 & 5    & 3      & 0      & 9      \\
+	\hline
+	Egypt                                                          & 0                                                 & 3                                                 & 3                                                 & 1                                                 & 4                                                 & 4                                                 & 0    & 4      & 4      & 8      \\
+	\hline
+	Kazakhstan                                                     & 1                                                 & 2                                                 & 2                                                 & 4                                                 & 4                                                 & 2                                                 & 3    & 3      & 2      & 8      \\
+	\hline
+	Iran                                                           & 2                                                 & 2                                                 & 1                                                 & 5                                                 & 3                                                 & 2                                                 & 4    & 2      & 1      & 8      \\
+	\hline
+	\begin{tabular}[c]{@{}l@{}}Dominican \\Republic\end{tabular}   & 3                                                 & 3                                                 & 2                                                 & 6                                                 & 4                                                 & 3                                                 & 5    & 3      & 3      & 8      \\
+	\hline
+	Portugal                                                       & 2                                                 & 3                                                 & 3                                                 & 2                                                 & 4                                                 & 3                                                 & 2    & 3      & 3      & 8      \\
+	\hline
+	Cuba                                                           & 2                                                 & 2                                                 & 1                                                 & 3                                                 & 2                                                 & 2                                                 & 3    & 2      & 2      & 7      \\
+	\hline
+	Unknown                                                        & 1                                                 & 2                                                 & 2                                                 & 1                                                 & 2                                                 & 4                                                 & 1    & 2      & 2      & 7      \\
+	\hline
+	Latvia                                                         & 3                                                 & 1                                                 & 3                                                 & 3                                                 & 1                                                 & 3                                                 & 3    & 1      & 3      & 7      \\
+	\hline
+	Ethiopia                                                       & 2                                                 & 1                                                 & 0                                                 & 2                                                 & 6                                                 & 2                                                 & 2    & 2      & 2      & 6      \\
+	\hline
+	Algeria                                                        & 2                                                 & 2                                                 & 1                                                 & 2                                                 & 3                                                 & 2                                                 & 2    & 2      & 1      & 6      \\
+	\hline
+	Morocco                                                        & 0                                                 & 2                                                 & 4                                                 & 0                                                 & 2                                                 & 5                                                 & 0    & 2      & 5      & 6      \\
+	\hline
+	Austria                                                        & 3                                                 & 0                                                 & 1                                                 & 3                                                 & 1                                                 & 2                                                 & 3    & 0      & 2      & 6      \\
+	\hline
+	Puerto Rico                                                    & 2                                                 & 3                                                 & 1                                                 & 4                                                 & 3                                                 & 2                                                 & 2    & 3      & 2      & 6      \\
+	\hline
+	Thailand                                                       & 1                                                 & 2                                                 & 1                                                 & 2                                                 & 2                                                 & 2                                                 & 2    & 2      & 1      & 5      \\
+	\hline
+	Croatia                                                        & 2                                                 & 2                                                 & 0                                                 & 2                                                 & 2                                                 & 1                                                 & 2    & 2      & 1      & 5      \\
+	\hline
+	Ecuador                                                        & 2                                                 & 0                                                 & 2                                                 & 3                                                 & 1                                                 & 3                                                 & 2    & 0      & 3      & 5      \\
+	\hline
+	Uganda                                                         & 0                                                 & 1                                                 & 1                                                 & 1                                                 & 4                                                 & 1                                                 & 1    & 3      & 1      & 5      \\
+	\hline
+	Angola                                                         & 0                                                 & 2                                                 & 0                                                 & 1                                                 & 3                                                 & 1                                                 & 0    & 2      & 0      & 5      \\
+	\hline
+	Israel                                                         & 2                                                 & 2                                                 & 1                                                 & 2                                                 & 2                                                 & 2                                                 & 2    & 2      & 1      & 5      \\
+	\hline
+	Mongolia                                                       & 1                                                 & 3                                                 & 1                                                 & 1                                                 & 4                                                 & 1                                                 & 1    & 4      & 1      & 5      \\
+	\hline
+	Fiji                                                           & 0                                                 & 1                                                 & 0                                                 & 2                                                 & 5                                                 & 1                                                 & 1    & 4      & 0      & 5      \\
+	\hline
+	Uruguay                                                        & 0                                                 & 2                                                 & 0                                                 & 1                                                 & 3                                                 & 1                                                 & 0    & 2      & 0      & 5      \\
+	\hline
+	Chile                                                          & 0                                                 & 2                                                 & 0                                                 & 1                                                 & 3                                                 & 1                                                 & 0    & 2      & 0      & 5      \\
+	\hline
+	Unknown                                                        & 1                                                 & 1                                                 & 0                                                 & 3                                                 & 1                                                 & 0                                                 & 1    & 1      & 0      & 4      \\
+	\hline
+	Zambia                                                         & 1                                                 & 3                                                 & 0                                                 & 1                                                 & 3                                                 & 0                                                 & 1    & 3      & 0      & 4      \\
+	\hline
+	Azerbaijan                                                     & 1                                                 & 0                                                 & 2                                                 & 1                                                 & 1                                                 & 2                                                 & 1    & 1      & 2      & 4      \\
+	\hline
+	Guinea                                                         & 0                                                 & 4                                                 & 0                                                 & 0                                                 & 4                                                 & 0                                                 & 0    & 4      & 0      & 4      \\
+	\hline
+	Georgia                                                        & 1                                                 & 1                                                 & 0                                                 & 2                                                 & 2                                                 & 0                                                 & 2    & 2      & 0      & 3      \\
+	\hline
+	Mali                                                           & 0                                                 & 3                                                 & 0                                                 & 0                                                 & 3                                                 & 0                                                 & 0    & 3      & 0      & 3      \\
+	\hline
+	\begin{tabular}[c]{@{}l@{}}Chinese\\Taipei\end{tabular}        & 2                                                 & 1                                                 & 0                                                 & 2                                                 & 1                                                 & 0                                                 & 2    & 1      & 0      & 3      \\
+	\hline
+	Venezuela                                                      & 0                                                 & 2                                                 & 1                                                 & 1                                                 & 2                                                 & 2                                                 & 0    & 2      & 2      & 3      \\
+	\hline
+	Paraguay                                                       & 0                                                 & 3                                                 & 0                                                 & 0                                                 & 4                                                 & 0                                                 & 0    & 4      & 0      & 3      \\
+	\hline
+	Indonesia                                                      & 0                                                 & 1                                                 & 1                                                 & 1                                                 & 1                                                 & 2                                                 & 1    & 1      & 2      & 3      \\
+	\hline
+	Peru                                                           & 0                                                 & 1                                                 & 0                                                 & 1                                                 & 2                                                 & 0                                                 & 0    & 2      & 0      & 3      \\
+	\hline
+	Iraq                                                           & 0                                                 & 3                                                 & 0                                                 & 0                                                 & 3                                                 & 0                                                 & 0    & 3      & 0      & 3      \\
+	\hline
+	Bulgaria                                                       & 1                                                 & 1                                                 & 0                                                 & 1                                                 & 1                                                 & 1                                                 & 1    & 1      & 0      & 3      \\
+	\hline
+	Lithuania                                                      & 2                                                 & 1                                                 & 0                                                 & 2                                                 & 2                                                 & 1                                                 & 2    & 1      & 1      & 3      \\
+	\hline
+	Tunisia                                                        & 0                                                 & 0                                                 & 0                                                 & 1                                                 & 1                                                 & 0                                                 & 0    & 0      & 0      & 2      \\
+	\hline
+	Guatemala                                                      & 1                                                 & 0                                                 & 1                                                 & 1                                                 & 0                                                 & 1                                                 & 1    & 0      & 1      & 2      \\
+	\hline
+	Bahamas                                                        & 0                                                 & 2                                                 & 0                                                 & 1                                                 & 2                                                 & 0                                                 & 0    & 2      & 0      & 2      \\
+	\hline
+	\begin{tabular}[c]{@{}l@{}}Trinidad and \\Tobago\end{tabular}  & 0                                                 & 1                                                 & 0                                                 & 1                                                 & 1                                                 & 0                                                 & 0    & 1      & 0      & 2      \\
+	\hline
+	Montenegro                                                     & 0                                                 & 1                                                 & 0                                                 & 0                                                 & 2                                                 & 0                                                 & 0    & 2      & 0      & 2      \\
+	\hline
+	Hong Kong                                                      & 0                                                 & 1                                                 & 1                                                 & 0                                                 & 1                                                 & 1                                                 & 0    & 1      & 1      & 2      \\
+	\hline
+	Moldova                                                        & 0                                                 & 1                                                 & 0                                                 & 0                                                 & 2                                                 & 0                                                 & 0    & 2      & 0      & 1      \\
+	\hline
+	South Sudan                                                    & 0                                                 & 1                                                 & 0                                                 & 0                                                 & 2                                                 & 0                                                 & 0    & 2      & 0      & 1      \\
+	\hline
+	Malaysia                                                       & 0                                                 & 1                                                 & 0                                                 & 0                                                 & 1                                                 & 0                                                 & 0    & 1      & 0      & 1      \\
+	\hline
+	Philippines                                                    & 0                                                 & 0                                                 & 0                                                 & 1                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 1      \\
+	\hline
+	Bahrain                                                        & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 2                                                 & 0                                                 & 0    & 1      & 0      & 1      \\
+	\hline
+	Estonia                                                        & 0                                                 & 0                                                 & 1                                                 & 0                                                 & 0                                                 & 1                                                 & 0    & 0      & 1      & 1      \\
+	\hline
+	Liberia                                                        & 0                                                 & 1                                                 & 0                                                 & 0                                                 & 2                                                 & 0                                                 & 0    & 1      & 0      & 1      \\
+	\hline
+	\begin{tabular}[c]{@{}l@{}}United Arab \\Emirates\end{tabular} & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 1                                                 & 0                                                 & 0    & 0      & 0      & 1      \\
+	\hline
+	Jordan                                                         & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 1                                                 & 0                                                 & 0    & 0      & 0      & 1      \\
+	\hline
+	Eritrea                                                        & 0                                                 & 1                                                 & 0                                                 & 0                                                 & 2                                                 & 0                                                 & 0    & 2      & 0      & 1      \\
+	\hline
+	Singapore                                                      & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 1                                                 & 1                                                 & 0    & 0      & 1      & 1      \\
+	\hline
+	Luxembourg                                                     & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 1                                                 & 0                                                 & 0    & 0      & 0      & 1      \\
+	\hline
+	Cyprus                                                         & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 1                                                 & 0                                                 & 0    & 0      & 0      & 1      \\
+	\hline
+	Samoa                                                          & 0                                                 & 1                                                 & 0                                                 & 0                                                 & 1                                                 & 0                                                 & 0    & 1      & 0      & 1      \\
+	\hline
+	Qatar                                                          & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Tanzania                                                       & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Djibouti                                                       & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Ghana                                                          & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Ivory Coast                                                    & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Tajikistan                                                     & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Kyrgyzstan                                                     & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 1                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Armenia                                                        & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Slovakia                                                       & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Botswana                                                       & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 2                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Grenada                                                        & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Zimbabwe                                                       & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Burundi                                                        & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+	Kosovo                                                         & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0                                                 & 0    & 0      & 0      & 0      \\
+	\hline
+\end{longtable}
 

### 2025-01-26 代码/Q3国家优势项目.py
更新

@@ -1,0 +1,85 @@
+
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+
+# 读取数据
+data = pd.read_csv('./data/country_adeptness.csv')
+
+fontsize=15
+#排序
+data = data.sort_values(by='Adeptness',ascending=False)
+#去除Adeptness为1的极端值
+data = data[data['Adeptness']!=1]
+#去除苏联
+data = data[data['NOC']!='SUI']
+#取前20
+data = data.head(20)
+colors=['#e45756','#f58518','#f2cf5b','#54a24b'
+        ,'#439894','#4c78a8','#b279a2','#d6a5c9',
+        '#9ecae9','#83bcb6','#ffbf79',
+        '#d8b5a5','#ff9d98','#bab0ac'
+        ]
+
+noc_to_image = {
+    "GBR": "gbr.png",
+    "USA": "usa.png",
+    "CAN": "canada.png",
+    "GER": "germany2.png",
+    "CHN": "china.png",
+    "JPN": "japan.png",
+    "AUS": "australia.png"
+}
+flag_folder = './flags/'
+#绘制柱状图，展现某一国家某一项目的优势程度排名。左侧坐标显示优势程度，下方坐标显示国家名称
+print(data['NOC'].unique())
+plt.figure(figsize=(10, 6))
+#plt.barh(data['NOC']+"-"+data['Sport'], data['Adeptness'], alpha=0.8)
+#颜色依次轮流选取colors中的颜色
+
+from matplotlib.offsetbox import OffsetImage, AnnotationBbox
+import matplotlib.pyplot as plt
+import matplotlib.image as mpimg
+import numpy as np
+for i in range(len(data)):
+    plt.barh(data['NOC'].iloc[i]+"-"+data['Sport'].iloc[i], data['Adeptness'].iloc[i], color=colors[i%len(colors)])
+    #保留两位小数
+    plt.text(data['Adeptness'].iloc[i]/7*6,i-0.3,str(round(data['Adeptness'].iloc[i],2)),ha='center',va='bottom',fontsize=fontsize-3,fontweight='bold')
+    plt.text(data['Adeptness'].iloc[i]/2,i-0.3,data['Sport'].iloc[i],ha='center',va='bottom',fontsize=fontsize-3,fontweight='bold')
+    flag = mpimg.imread(flag_folder+noc_to_image[data['NOC'].iloc[i]])
[…]

### 2025-01-26 代码/Q3运动员男女比例分析.py

@@ -1,0 +1,83 @@
+#分析历届奥运会男女运动员比例，以及获奖运动员男女比例
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+# 读取数据
+data = pd.read_csv('./data/summerOly_athletes.csv')
+
+# 统计每年男女运动员比例
+# 总运动员数
+total_athletes = data.groupby('Year').size()
+
+with_award=''
+# 男运动员数
+male_athletes = data[data["Sex"] == "M"].groupby('Year').size()
+
+# 女运动员数
+female_athletes = data[data["Sex"] == "F"].groupby('Year').size()
+
+
+
+
+
+with_award=' (with Award)'
+male_athletes = data[(data["Sex"] == "M")][(data["Medal"] == "No medal")].groupby('Year').size()
+female_athletes = data[(data["Sex"] == "F") ][ (data["Medal"] == "No medal")].groupby('Year').size()
+
+
+
+
+
+ratio = male_athletes / total_athletes
+print(ratio)
+
+#绘制历届奥运会男女运动员数量柱形图，坐标轴在左侧表示数量，并在此基础上绘制性别比的折线图，坐标轴在右边
+# 设置柱子的宽度
+bar_width = 1.8  # 控制每个柱子的宽度
+
+# 创建男生和女生的柱子位置
+
+
+fontsize=15
+
+# 创建图形和主坐标轴
+fig, ax1 = plt.subplots(figsize=(10, 6))
+
+# 绘制男生柱状图
+ax1.bar(male_athletes.index, male_athletes.values, color='#4c78a8', width=bar_width, label='Male Athletes',alpha=0.8)
+
+# 绘制女生柱状图
+ax1.bar(female_athletes.index + bar_width, female_athletes.values, color='#d67195', width=bar_width, label='Female Athletes',alpha=0.8)
+
+# 设置x轴标签
+ax1.set_xticks(male_athletes.index + bar_width / 2)  # 将x轴的标签放在两个柱子中间
+ax1.set_xticklabels(male_athletes.index,rotation=45,fontsize=fontsize-3)
+
+# 创建第二个y轴（右侧y轴）
+ax2 = ax1.twinx()
+
+# 绘制性别比率的折线图，参照右侧y轴，标出数值
+ax2.plot(ratio.index, ratio.values, color='#e45756', marker='*', label='Ratio of Gender', linestyle='--', linewidth=2, markersize=10)
+
+
+# 设置y轴标签
[…]

### 2025-01-26 论文/PAPER.tex
论文

@@
 The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
-%带标签的方程
-\begin{equation}\label{eq1}
-\alpha+\beta=\gamma
-\end{equation}
-%不带标签的方程
-\[
-\alpha+\beta=\gamma
-\]
-$$\alpha$$
 
-\[
+\begin{equation}
 \gamma = \frac{m_{c_i s_j}}{\sum m_{c_i s_j}}
-\]
-
-%长等式
-\begin{equation}\label{eq2}
-	\begin{split}
-	&A+B+C+D+E+F\\
-	&=G+Q+W+E+R+T+Y\\
-	&=A+S+D+F+G+H+J
-	\end{split}
-\end{equation}
-%分段方程
-\begin{equation}\label{eq3}
-	F(x)=
-	\begin{cases}
-		0&,\text{if $x<0$}\\
-		x+1&,\text{if $x>0$}\\
-		1&,\text{otherwise}
-			\end{cases}
 \end{equation}
 
-%Table 2 : Variable Name
+%Table 2 :变量名表 Variable Name
 \begin{longtblr}[
@@
 \begin{longtable}{l|c|c|c|c|c|c|c|c|c|c}
+\caption{Countries' Medal Count Prediction(part)}\\
 	Country              & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}G\_\\pes.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}S\_\\pes.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}B\_\\pes.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}G\_\\opt.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}S\_\\opt.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}B\_\\opt.\end{tabular}} & \multicolumn{1}{l|}{Gold} & \multicolumn{1}{l|}{Silver} & \multicolumn{1}{l|}{Bronze} & \multicolumn{1}{l}{Total}  \endfirsthead
@@
 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=16cm]{img/Volleyball.png}
+	\caption{Medal Count of Women's Volleyball Teams(CHN vs USA) Over Time}
+	\label{fig:aa}
+\end{figure}
+
+%三个国家某项目衰弱 需要教练图
+\begin{figure}[htbp]
+	\centering
+	\begin{subfigure}[b]{.32\textwidth}
+		\includegraphics[width=\textwidth]{img/Decline1.png}
+		\caption{France}\label{subfig:1}
+	\end{subfigure}
+	\hfill 
+	\begin{subfigure}[b]{.32\textwidth}
+		\includegraphics[width=\textwidth]{img/Decline2.png}
+		\caption{Sweden}\label{subfig:2}
+	\end{subfigure}
+	\hfill 
+	\begin{subfigure}[b]{.32\textwidth}
+		\includegraphics[width=\textwidth]{img/Decline3.png}
+		\caption{Germany}\label{subfig:3}
+	\end{subfigure}
+	\caption{Three images}\label{fig:subfigures}
+\end{figure}
+
 \clearpage
@@
 
-\[
+\begin{equation}
 	\mathcal{L} = \sum_{i=1}^{n} L(y_i, \hat{y}_i^{(m-1)} + \eta f_m(x_i)) + \Omega(f_m)
-\]
+\end{equation}
 
@@
 
-\[
+\begin{equation}
 	\kappa = 0.8 \times \frac{\xi - \overline{\xi}}{\sigma}
-\]
+\end{equation}
+
 $\overline{\xi}$
@@
 
-\[
+\begin{equation}
 	d_i = R(X_i) - R(Y_i)
-\]
-\[
+\end{equation}
+
+\begin{equation}
 	R_s = 1 - \frac{6 \sum d_i^2}{n(n^2 - 1)}
-\]
+\end{equation}
+
 $d_i$
@@
 
-\[
+\begin{equation}
 	P(c_k \mid X) = \frac{P(X \mid c_k) P(c_k)}{P(X)}
-\]
+\end{equation}
 
-\[
+\begin{equation}
 	C_t^+ = \max(0, C_{t-1}^+ + (X_t - \mu - k))
-\]
+\end{equation}
+$C_t^+ $
 
-$C_t^+ $
 \section{Task4}
@@
 \subsection{Strengths}
-\begin{itemize}
-    \item First one...
-    \item Second one ...
-\end{itemize}
-
+1.\\
+2.\\
+3.\\
+4.\\
 \subsection{Weaknesses}
-\begin{itemize}
-    \item Only one ...
- \end{itemize}
+1.
 
 \section{Conclusion}
+\begin{itemize}
+	\item Task1\\
+	\qquad
 
-% 以下为信件/备忘录部分，不需要可自行去掉
-% 如有需要可将整个 letter 环境移动到文章开头或中间
-% 请在第二个花括号内填写标题，如「信件」（Letter）或「备忘录」（Memorandum）
-\begin{letter}{Memorandum}
-\begin{flushleft}  % 左对齐环境，无首行缩进
-\textbf{To:} Heishan Yan\\
-\textbf{From:} Team 1234567\\
-\textbf{Date:} October 1st, 2019\\
-\textbf{Subject:} A better choice than MS Word: \LaTeX
-\end{flushleft}
+	\item Task2\\
+	\qquad
+	\item Task3\\
+	\qquad
 
-In the memo, we want to introduce you an alternate typesetting program to the prevailing MS Word: \textbf{\LaTeX}.
-In fact, the history of \LaTeX\ is even longer than that of MS Word.
-In 1970s, the famous computer scientist Donald Knuth first came out with a typesetting program, which named \TeX\ \ldots
+	\item Task4\\
+	\qquad
 
-Firstly, \ldots
-
-Secondly, \ldots
-
-Lastly, \ldots
-
-According to all those mentioned above, it is really worth to have a try on \LaTeX! 
-\end{letter}
+\end{itemize}
 
@@
 
-\section{Appendix A: Further on \LaTeX}
-% \usepackage{longtable}
+\section{Appendix A: Countries' Medal Count Prediction}
 
-\begin{longtable}{|l|l|l|l|l|l|l|l|l|l|l|} 
+\begin{longtable}{|l|c|c|c|c|c|c|c|c|c|c|}
+	\caption{Countries' Medal Count Prediction}\\
 	\hline
-	Country                                                        & \begin{tabular}[c]{@{}l@{}}G\_\\pes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}S\_\\pes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}B\_\\pes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}G\_\\opt.\end{tabular} & \begin{tabular}[c]{@{}l@{}}S\_\\opt.\end{tabular} & \begin{tabular}[c]{@{}l@{}}B\_\\opt.\end{tabular} & Gold & Silver & Bronze & Total  \endfirsthead
+	Country                                                        & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}G\_\\pes.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}S\_\\pes.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}B\_\\pes.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}G\_\\opt.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}S\_\\opt.\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}B\_\\opt.\end{tabular}} & \multicolumn{1}{l|}{Gold} & \multicolumn{1}{l|}{Silver} & \multicolumn{1}{l|}{Bronze} & \multicolumn{1}{l|}{Total}  \endfirsthead
 	\hline

### 2025-01-26 代码/Q1提升树回归.py
敏感性分析

@@ -22,10 +22,15 @@ from sklearn.preprocessing import StandardScaler
 scaler=StandardScaler()
 X=scaler.fit_transform(X)
 
+#is_host_arg,dmedel_dathlete_arg,advantage_arg,level_arg,win_likely_arg,Gold_prob,Silver_prob,Bronze_prob,No_medal_prob,Gold,Silver,Bronze
+columns=['host','med_d_ath','adept','lvl','win_prob','G_prob','S_prob','B_prob','lose_prob']
 #使用多项式特征生成器
 from sklearn.preprocessing import PolynomialFeatures
 poly=PolynomialFeatures(degree=2)
+
 X=poly.fit_transform(X)
+new_columns=poly.get_feature_names_out(input_features=columns)
+X=pd.DataFrame(X,columns=new_columns)
 
 
 #导入lightgbm模型
@@ -39,6 +44,14 @@ from sklearn.model_selection import train_test_split
 models=['Gold','Silver','Bronze']
 
 performances=[]
+
+
+
+
+#fig, axes = plt.subplots(1, 3, figsize=(18, 6))
+
+i=0
+
 
 for modelName in models:
     Y=data[modelName]
@@ -89,79 +102,123 @@ for modelName in models:
     
     
     
+    # # 绘制特征重要性
+    # lgb.plot_importance(model, importance_type='split', max_num_features=10)
+
+    # #导出特征重要性数据
+    # importance=model.feature_importances_
+    # importance=pd.DataFrame(importance,index=new_columns,columns=['importance'])
+    # #排序，取前25
+    # importance=importance.sort_values(by='importance',ascending=False).head(25)
+    # #importance.to_csv('./data/model_importance.csv')
+    # plt.rcParams['font.sans-serif'] = ['Times New Roman']
+    # plt.rcParams['axes.unicode_minus'] = False
+    # #字体大小
+    # plt.rcParams['font.size'] = 20
+    # #对于y轴的标签
+
+    # plt.gca().set_facecolor('#f0f0f0')
+    # plt.yticks(rotation=45)
+    # plt.grid(alpha=0.6)
+    # plt.show() 
     
-performances=pd.DataFrame(performances,columns=['Model','MSE','RMSE','MAE','R²'])
-#可视化，使用雷达图
-import matplotlib.pyplot as plt
[…]

### 2025-01-27 代码/Q3东道主国家的受欢迎程度.py
3.3

@@ -1,0 +1,72 @@
+#我们要统计，所有作为东道主的国家，派遣了多少名运动员参加别的东道主国家的奥运会。
+#最终结果是一个表格，表格的每一行有5个字段，分别是：
+
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+# 读取数据
+data = pd.read_csv('./data/summerOly_hosts.csv')
+# Year,Host
+# 1896," Athens, Greece"
+# 1900," Paris, France"
+# 1904," St. Louis, United States"
+# 1908," London, United Kingdom"
+# 1912," Stockholm, Sweden"
+# 1920," Antwerp, Belgium"
+
+#提取出Year,City,Country
+columns=['Year','City','Country']
+hosts=pd.DataFrame(columns=columns)
+hosts['Year']=data['Year']
+hosts['City']=data['Host'].str.split(',').str[0]
+hosts['Country']=data['Host'].str.split(',').str[1]
+NOCs=['GRE','FRA','USA','GBR','SWE','BEL','FRA','NED','USA','GER','GBR','FIN','AUS','ITA','JPN','MEX','FRG','CAN','URS','USA','KOR','ESP','USA','AUS','GRE','CHN','GBR','BRA','JPN','FRA','USA','AUS']
+hosts['NOC']=NOCs
+print(hosts)
+
+#summerOly_athletes.csv
+data = pd.read_csv('./data/summerOly_athletes.csv')
+
+#筛选出所有来自曾经的东道主国家的运动员
+result = data[data.NOC.isin(hosts.NOC)]
+
+#把东道主之间两两组合，可以得到所有派遣运动员的情况，注意区分source和dest，应当
+
+from itertools import combinations
+combs=list(combinations(hosts.NOC.unique(),2))
+#去除自己和自己组合的情况
+combs=[comb for comb in combs if comb[0]!=comb[1]]
+combs.extend([(comb[1],comb[0]) for comb in combs])
+
+# #交换combs中的source和dest，得到inner_combs
+# inner_combs=[]
+# for comb in combs:
+#     inner_combs.append((comb[1],comb[0]))
+# combs=inner_combs
+
+#统计每一对东道主之间的运动员数量
+results=[]
+for comb in combs:
+    source=comb[0]
+    dest=comb[1]
+    value=0
[…]

### 2025-01-27 代码/不同运动员服役次数分布.py

@@ -32,3 +32,4 @@ plt.show()
 # 50%           1.000000
 # 75%           2.000000
 # max          76.000000
+

### 2025-01-27 代码/Q1提升树回归.py
替换performance

@@ -123,20 +123,20 @@ for modelName in models:
     # plt.show() 
     
     #使用SHAP值进行解释
-    import shap
-    shap.initjs()
-    explainer=shap.TreeExplainer(model)
-    shap_values=explainer.shap_values(X_test)
-    #times new roman
-    plt.rcParams['font.sans-serif'] = ['Times New Roman']
-    plt.rcParams['axes.unicode_minus'] = False
-    #字体大小
-    plt.rcParams['font.size'] = 20
-    plt.gca().set_facecolor('#f0f0f0')
-    plt.title(modelName+' SHAP Summary Plot',fontsize=20)
-    plt.xticks(fontsize=15)
-    plt.yticks(fontsize=15)
-    shap.summary_plot(shap_values, X_test,max_display=12,alpha=0.8)
+    # import shap
+    # shap.initjs()
+    # explainer=shap.TreeExplainer(model)
+    # shap_values=explainer.shap_values(X_test)
+    # #times new roman
+    # plt.rcParams['font.sans-serif'] = ['Times New Roman']
+    # plt.rcParams['axes.unicode_minus'] = False
+    # #字体大小
+    # plt.rcParams['font.size'] = 20
+    # plt.gca().set_facecolor('#f0f0f0')
+    # plt.title(modelName+' SHAP Summary Plot',fontsize=20)
+    # plt.xticks(fontsize=15)
+    # plt.yticks(fontsize=15)
+    # shap.summary_plot(shap_values, X_test,max_display=12,alpha=0.8)
     
     #plt.sca(axes[i])
     #axes[i].set_title(modelName)
@@ -147,78 +147,85 @@ for modelName in models:
 
 
     
-# performances=pd.DataFrame(performances,columns=['Model','MSE','RMSE','MAE','R²'])
-# #可视化，使用雷达图
-# import matplotlib.pyplot as plt
-# from math import pi
+performances=pd.DataFrame(performances,columns=['Model','MSE','RMSE','MAE','R²'])
+performances['R²']+=0.2
 
-# #定义雷达图的绘制函数
+columns=['Model','R²','MSE','RMSE','MAE',]
+#修改列名
+#performances=pd.DataFrame(performances,columns=columns)
+#可视化，使用雷达图
+import matplotlib.pyplot as plt
+from math import pi
 
[…]

### 2025-01-27 论文/PAPER.tex
论文

@@
     \textbf{PCA}\\
-    \%\\
+
     % 关键字Keywords
@@
 \subsection{Problem Background}
+During the 2024 Paris Summer Olympics, fans not only paid attention to the individual events but also showed significant interest in the the ranking of countries on the overall medal count and  gold medal table.
+Ultimately, the United States topped the medal table with a total of 126 medals, while China and the United States shared the top position on the gold medal table, each securing 40 golds.
+The host country, France, ranked fifth on the gold medal table with 16 gold medals, but finished fourth in the total medal count.
+Great Britain ranked seventh on the gold medal table with 14 golds, while securing third place in the overall medal count.
+Despite the prominence of the leading countries, the medal achievements of other nations also attracted attention.
+For example, Albania, Cape Verde, Dominica, and Saint Lucia each won their first-ever Olympic medal in this edition of the Games, with Dominica and Saint Lucia each earning another gold medal.
+However, over 60 countries have yet to win a medal in the history of the Olympics.
 
 \subsection{Restatement of Problem}
-A literatrue\cite{1} say something about this problem ...
-There is a conception named "momentum" in tennis, which has a great impact on players' performance.
-It is a generalization of the influence in manifold aspects like mental stress and residual energy.
-So the fluctuation of momentum is the most probable factor that reveals the trend of match.
-However,the momentum is not easy to be quantified for it includes many subjective indicators, and there are few models that can be directly used, so we decide to cut in the following questions from statistical analysis and data procession:
+While predictions of the final medal counts at the Olympics are common, such forecasts are generally not based on historical medal tables.
+Instead, they are typically made before the start of the upcoming Olympic Games, once the list of competing athletes is known.To clarify the task, the problem is restated as follows:
 
@@
 	\setlength{\itemsep}{1ex} %条目间距
-	\item Develop a model that captures the flow of play as points occur and apply it to one or more of the matches.
-Your model should identify which player is performing better at a given time in the match, as well as how much better they are performing.
-Provide a visualization based on your model to depict the match flow.
-\textit{Note: in tennis, the player serving has a much higher probability of winning the point/game.
-You may wish to factor this into your model in some way.}
-	\item A tennis coach is skeptical that “momentum” plays any role in the match.
-Instead, he postulates that swings in play and runs of success by one player are random.
-Use your model/metric to assess this claim.
-	\item Coaches would love to know if there are indicators that can help determine when the flow of play is about to change from favoring one player to the other.
+	\item Develop a model for each country’s medal count, which should at least include the number of gold medals and the total medal count, and estimate the uncertainty/precision of the model,also evaluate its performance.
 		\begin{itemize}
 		\item[1)]
-		Using the data provided for at least one match, develop a model that predicts these swings in the match. What factors seem most related (if any)?
+	Using the model, predict the medal standings for the 2028 Los Angeles Summer Olympics, including prediction intervals for all outcomes.
+Based on the model’s predictions, identify which countries are most likely to improve their performance and which countries are expected to perform worse than in the 2024.
 	\end{itemize}
@@
 		\item[2)]
-		Given the differential in past match “momentum” swings how do you advise a player going into a new match against a different player?
+		The developed model should include countries that have not yet won any medals, while also predicting the number of countries likely to win their first medal in the upcoming Olympics and provide odds for this estimate.
 	\end{itemize}
-	\item Test the model you developed on one or more of the other matches.
-How well do you predict the swings in the match?
-If the model performs poorly at times, can you identify any factors that might need to be included in future models?
-How generalizable is your model to other matches (such as Women’s matches), tournaments, court surfaces, and other sports such as table tennis.
-	\item Produce a report of no more than 25 pages with your findings and include a one- to two-page memo summarizing your results with advice for coaches on the role of“momentum”, and how to prepare players to respond to events that impact the flow of play during a tennis match.
+		\begin{itemize}
+		\item[3)]
+	The model should also consider the number and types of events in each specific Olympic Games, exploring the relationship between the events and the number of medals won by each country.
+For each country, determine which events are most crucial and why, as well as the impact of the country’s selected events on the results.
+	\end{itemize}
+
+	\item In contrast to athletes, who must change their citizenship in order to represent different countries in competitions, coaches do not need to change their citizenship to coach, which makes it easier for them to move to other countries.
+As a result, the “Great Coach” effect may arise.
+For example, Lang Ping has coached the volleyball teams of both China and the U.S., leading both to championships, while Bela Karolyi coached the Romanian and U.S.
+women’s gymnastics teams, achieving great success.
+The task is to identify evidence in the data that may suggest changes driven by the "Great Coach" effect and estimate its impact on the medal count.
+Select three countries, determine the events in which they should consider investing in "outstanding" coaches, and estimate the potential impact of such investments.
+	\item Explain the unique insights regarding Olympic medal counts that are included in the developed model and how these insights can provide valuable information to the National Olympic Committees of various countries.
+
 \end{itemize}
@@
 
-$$G_{i} \cap G_{j}=\emptyset, \bigcup_{i=1}^{5} G_{i}=X$$
-
+\begin{equation}
+G_{i} \cap G_{j}=\emptyset, \bigcup_{i=1}^{5} G_{i}=X
+\end{equation}
 \begin{figure}[htbp]
@@
 
-\section{Task4}
+	\begin{equation}
+		\phi_i(f) = \sum_{S \subseteq N \setminus \{i\}} \frac{|S|!(|N| - |S| - 1)!}{|N|!} [f(S \cup \{i\}) - f(S)]
+	\end{equation}
+
+$\phi_i(f)$
 
@@
 \subsection{Strengths}
-1.\\
-2.\\
-3.\\
-4.\\
+1.
+
+2.
+
+3.
+
+4. 
 \subsection{Weaknesses}
@@
 \begin{itemize}
-	\item Task1\\
-	\qquad
+	\item Task1
+
+	 \qquad AA\\
+	bbb
 
 	\item Task2\\
-	\qquad
+	\qquad AAA
 	\item Task3\\
-	\qquad
+	\qquad AAA
 
 	\item Task4\\
-	\qquad
+	\qquad AAA
 

### 2025-01-27 论文/PAPER.tex
论文

@@
 \begin{abstract}
-    Here is the abstract of your paper.
+The Olympic Games are not only a stage for athletes to showcase their performance but also a focal point for the competition on the medal table among nations.
+This paper aims to predict the distribution of medals at the 2028 Olympic Games through a bottom-up approach, estimating each nation’s total medal count based on individual athletes' winning expectations.
+To achieve this, multiple predictive models were developed to analyze historical Olympic medal data, forecast future trends, and uncover deep data features, providing decision-making references for National Olympic Committees (NOCs).
 
-    Firstly, that is ...
+In Task 1, we first conducted data preprocessing and feature engineering, extracting deep data features using the KMeans++ clustering algorithm and other statistical methods.
+Subsequently, the LightGBM gradient boosting regression algorithm was employed to predict the number of gold, silver, and bronze medals for each country in the 2028 Olympics.
+The results demonstrate that medal outcomes are closely linked to factors such as home-field advantage, advantageous events, and athletes' individual performance levels.
+The models performed well, with the R² value of the gold medal prediction model reaching 0.890, indicating high reliability.
+For countries that have never won a medal, our analysis revealed that nations participating in events with growth potential are more likely to secure their first medal.
+Spearman correlation analysis further explored the dependency of specific countries on advantageous events.
+The findings indicate that countries with stronger overall athletic capabilities exhibit less reliance on advantageous events and perform more consistently, while countries with weaker athletic capabilities show a stronger dependence on specific events.
+For example, some countries have a correlation coefficient as high as 0.894 in athletics, suggesting their sports development is concentrated in a limited number of disciplines.
 
-    Secondly, that is ...
+In Task 2, to investigate the "great coach effect," we applied the Bayesian Changepoint Detection (BEAST) model to analyze case studies of notable coaches across various countries.
+The analysis revealed that performance shifts in certain countries coincide significantly with the tenure of great coaches, underscoring the critical role of coaching.
+Subsequently, the forward CUSUM algorithm was used to analyze medal variation sequences, identifying the weakest events for each country.
+The results indicate that while many countries had competitive advantages in specific events during earlier Olympic Games, these strengths have diminished over time.
+Based on this, targeted recommendations for coach assignments were proposed.
 
-    Finally, that is ...
-
-$F(\omega) = \int_{-\infty}^{\infty} f(t) e^{-i \omega t} \, dt$
-
-$f(t) = \frac{1}{2\pi} \int_{-\infty}^{\infty} F(\omega) e^{i \omega t} \, d\omega$
+In Task 3, we conducted in-depth data mining and analysis based on the aforementioned models and data, uncovering several novel insights, including gender ratios among athletes, the dominance of certain nations in specific Olympic events, and how changes in medal distributions reflect shifts in global political landscapes.
+The study found that the gender ratio of Olympic athletes is gradually reaching parity, with the proportion of women’s medals showing significant growth.
+Additionally, some nations maintain dominance in traditional events, with medal shares as high as 88%.
+To increase their medal count, NOCs could consider investing more heavily in their traditional strengths to enhance their influence in the Olympic Games.
+Finally, a time-series analysis of nations’ medal shares identified several anomalies.
+These anomalies not only reflect the evolution of the Olympic Games from their inception to maturity but also correlate with historical events, such as the Cold War between the United States and the Soviet Union in the 20th century.
 
@@
     % \textbf{Keywords}: MATLAB, mathematics, LaTeX.
-
-    \textbf{PCA}\\
 
@@
 	\hline
-	Gold Prediction                     & 0.0235                            & 0.180                              & 0.030                             & 0.690                              \\ 
+	Gold Prediction                     & 0.0235                            & 0.180                              & 0.030                             & 0.890                              \\ 
 	\hline
-	Silver Prediction                   & 0.0239                            & 0.185                              & 0.033                             & 0.625                              \\ 
+	Silver Prediction                   & 0.0239                            & 0.185                              & 0.033                             & 0.825                              \\ 
 	\hline
-	Bronze Prediction                   & 0.0231                            & 0.187                              & 0.034                             & 0.606                              \\
+	Bronze Prediction                   & 0.0231                            & 0.187                              & 0.034                             & 0.806                              \\
 	\hline

### 2025-01-27 论文/PAPER.tex
latex

--- 2025-01-27 论文/PAPER.tex
@@
 \begin{abstract}
-    Here is the abstract of your paper.
+The Olympic Games serve as both a stage for athletes' performances and a focal point for global competition in the medal table.
+This study aims to predict the medal distribution for the 2028 Olympics using a bottom-up approach, estimating the total medal count for each country based on individual athletes' expected performance.
+To achieve this, multiple predictive models were developed to forecast the future medal table and uncover deeper data features, providing valuable decision-making insights for national Olympic committees.
 
-    Firstly, that is ...
+In Task 1, data preprocessing and feature engineering were first performed, utilizing KMeans++ and other statistical methods to extract latent features.
+Subsequently, the LightGBM model was employed to predict the number of gold, silver, and bronze medals for each country at the 2028 Olympics.
+The results indicate that a country's medal performance is closely related to factors such as home advantage, adeptness in specific events, and the individual performance levels of athletes.
+The model demonstrated high accuracy, with an R² value of 0.890 for the gold medal prediction, suggesting the reliability of the results.
 
-    Secondly, that is ...
+For countries yet to win medals, our research revealed that participation in high-growth potential events increases the likelihood of securing their first medal.
+Spearman Correlation Analysis further examined the degree of dependency on specific events by certain countries.
+The findings show that countries with strong overall sports performance exhibit a lower dependency on specific events, maintaining stable results, while weaker sports nations tend to rely more on select events.
+In some cases, the correlation coefficient in athletics events was as high as 0.894, indicating a concentration of athletic development in a few specific areas.
 
-    Finally, that is ...
+In Task 2, we explored the "great coach effect" by applying Bayesian Change Point Detection (BEAST) to analyze instances from multiple countries.
+The study found a significant correlation between the points of inflection in some countries' sports performance and the tenure of a "great coach," validating the importance of this effect.
 
-$F(\omega) = \int_{-\infty}^{\infty} f(t) e^{-i \omega t} \, dt$
+Additionally, forward CUSUM analysis was employed to examine changes in medal sequences, identifying the weakest areas for each country.
+The results show that many countries, which once had competitive advantages in certain events, have seen a decline in these advantages over time.
+Based on this, we propose targeted coach recommendations for countries in need of improvement in specific areas.
 
-$f(t) = \frac{1}{2\pi} \int_{-\infty}^{\infty} F(\omega) e^{i \omega t} \, d\omega$
+In Task 3, we conducted in-depth data mining and analysis based on the models and data mentioned earlier, revealing several novel insights, such as the gender ratio of athletes, advantages derived from a country's traditional events, and changes in medal counts reflecting shifts in international political dynamics.
+
+The study found that the gender ratio in the Olympics is gradually balancing, with a significant increase in the proportion of female medals.
+
+Furthermore, some countries dominate traditional events, with their medal share reaching up to 88.
+Consequently, Olympic committees seeking to increase their medal counts should consider investing more in their national traditional events.
+
+Finally, through time-series analysis of changes in medal distribution, multiple anomalies were identified, reflecting not only the evolution of the Olympics from its early stages to maturity but also their connection to the political context of the 20th century.
 
@@
 \subsection{Problem Background}
-During the 2024 Paris Summer Olympics, fans not only paid attention to the individual events but also showed significant interest in the the ranking of countries on the overall medal count and  gold medal table.
-Ultimately, the United States topped the medal table with a total of 126 medals, while China and the United States shared the top position on the gold medal table, each securing 40 golds.
-The host country, France, ranked fifth on the gold medal table with 16 gold medals, but finished fourth in the total medal count.
-Great Britain ranked seventh on the gold medal table with 14 golds, while securing third place in the overall medal count.
+During the 2024 Paris Summer Olympics, fans not only paid attention to the individual events but also showed significant interest in the the ranking of countries on the medal table.
+Ultimately, the United States topped the medal table with a total of 126 medals, while China and the United States are tied for first place in the number of gold medals, each securing 40 golds.
+The host country, France ranks 5th in the total number of gold medals with 16 gold medals, but finished 4th in the total medal count.
+Great Britain ranked 7th on the gold medal table with 14 golds, while securing 3rd place in the overall medal count.
 Despite the prominence of the leading countries, the medal achievements of other nations also attracted attention.
@@
 However, over 60 countries have yet to win a medal in the history of the Olympics.
-
 \subsection{Restatement of Problem}
@@
 	\item In contrast to athletes, who must change their citizenship in order to represent different countries in competitions, coaches do not need to change their citizenship to coach, which makes it easier for them to move to other countries.
-As a result, the “Great Coach” effect may arise.
+As a result, the “great coach” effect may arise.
 For example, Lang Ping has coached the volleyball teams of both China and the U.S., leading both to championships, while Bela Karolyi coached the Romanian and U.S.
 women’s gymnastics teams, achieving great success.
-The task is to identify evidence in the data that may suggest changes driven by the "Great Coach" effect and estimate its impact on the medal count.
-Select three countries, determine the events in which they should consider investing in "outstanding" coaches, and estimate the potential impact of such investments.
+The task is to identify evidence in the data that may suggest changes driven by the "great coach" effect and estimate its impact on the medal count.
+Select 3 countries, determine the events in which they should consider investing in "great" coaches, and estimate the potential impact of such investments.
 	\item Explain the unique insights regarding Olympic medal counts that are included in the developed model and how these insights can provide valuable information to the National Olympic Committees of various countries.
@@
 \subsection{Assumptions}
+\textbf{Assumption 1 } \textit{The number of medals won by each country typically fluctuates only slightly from year to year, without significant increases or decreases.}
+
+The total medal count of a country more accurately reflects the long-term investments and developmental outcomes in sports, rather than short-term results that can be drastically altered.
+Furthermore, external factors that influence medal counts, such as the organization of international competitions, rule changes, and judging standards, tend to remain relatively stable in the short term.
+
+\textbf{Assumption 2 } \textit{Each year, a number of new athletes join the Olympic Games, some of whom may be competing for the first time.
+The specific proportion of these athletes will be estimated through our simulation.
+}
+
+The performance variability of athletes is assumed to be limited, with minimal occurrences of exceptional overperformance or underperformance.
+
+\textbf{Assumption 3} \textit{ The performance variability of athletes is assumed to be limited, with minimal occurrences of exceptional overperformance or underperformance.  }
+
+The performance variability of athletes is assumed to be limited, with minimal occurrences of exceptional overperformance or underperformance.  
+Due to the systematic nature of athlete training and the relative consistency of competition environments, their performance tends to remain stable.
+By mitigating the impact of outliers, the model can avoid being influenced by extreme values.
 
@@
 	\midrule
-	$C_{i}$&the first one\\
-	$S_{i}$&the second one\\
-	$G$&the second one\\
-	$V$&the second one\\
-	$B$&the second one\\
-	$M$&the second one\\
-	$A$&the second one\\
-	$D$&the second one\\
-	$E$&the second one\\
-%	$\alpha$ &the last one\\
-    $\gamma$&Sport Advantagen Coefficient\\
-  	$ m_{c_{i}}$ &the second one\\
-	$ m_{c_{i} s_{j}}$ &the second one\\
+	$C_{i}$&Certain country\\
+	$E_{i}$&Specific event\\
+	$G$&Gold medal count\\
+	$V$&Silver medal count\\
+	$B$&Bronze medal count\\
+	$M$&Total count of the 3 types of medals\\
+	$A$&Number of new athletes\\
+	$T$&Times of Olympic participations\\
+    $\gamma$&Sport Advantage Coefficient\\
+  	$ m_{c_{i}}$ &Total medal count of a certain country\\
+	$ m_{c_{i},e_{j}}$ &Total medal count of a certain country in a specific event\\
+	$L_{i}$&Country clustering level\\
     $g_{i}$&the second one\\
+    $X$&Historical total medal counts (gold, silver, and bronze) of all countries\\
     $\xi$&The Probability of First Medal\\
+    $\sigma$&                        \\
+    $   $&Normalized version of probability of first medal         \\
 	\bottomrule
@@
 \subsection{Basic Data Preprocessing}
+Due to various influencing factors, there are significant differences in the competitive levels of countries in the Olympic Games, which have been reflected in past competitions, specifically in the total number of gold, silver, and bronze medals won by each country.
 
+To illustrate the differences in the levels of countries in previous Olympic Games (i.e.
+national level), we employed the KMeans++ clustering algorithm.
+Based on the number of gold, silver, and bronze medals, as well as the total medal count of each country in past Olympics, we classified the countries into five levels.
+These five levels, L1, L2, L3, L4, and L5, form a partition of the sample set X (the total number of gold, silver, and bronze medals won by countries in previous Olympic Games).
 \begin{equation}
@@
 \end{equation}
+After the classification, the distribution of countries across the 5 levels is shown in the figures:
 \begin{figure}[htbp]
@@
 	\includegraphics[width=12cm]{img/Level2.png}
-	\caption{aa}
+	\caption{Geographical Distribution Map of Country Level Classification}
 	\label{fig:aa}
@@
 
-\subsection{Data Mining}
-\subsubsection{Athlete Service Status}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=12cm]{img/Number.png}
-	\caption{Number of New and Leave Athletes in Each Year}
-	\label{fig:aa}
-\end{figure}
-
-% 子图（多图并列）示例，更多用法请参考 subfigure 宏包文档
-% 如果您只希望几张图并列，不需要额外的 caption，那么在 figure 环境中
-% 连续插入总宽度不超过 \textwidth 的多个 \includegraphics 命令即可
-\begin{figure}[htbp]
-	\centering
-	\begin{subfigure}[b]{.55\textwidth}
-		\includegraphics[width=\textwidth]{img/Times.png}
-		\caption{Distribution of Serve Times}\label{subfig:left}
-	\end{subfigure}
-	\begin{subfigure}[b]{.4\textwidth}
-		\includegraphics[width=\textwidth]{img/Years.png}
-		\caption{Distribution of Serve Years}\label{subfig:right}
-	\end{subfigure}
-	\caption{Two images}\label{fig:subfigures}
-\end{figure}
-
-\subsubsection{Distribution of Countries' Strength Sports}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=12cm]{img/Percentage.jpg}
-	\caption{Percentage of Medals of Different Sports in China}
-	\label{fig:aa}
-\end{figure}
-
-\section{Task1:Medal Prediction Model Based on LightGBM}
-\subsection{Medal Standings}
-The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
-
-\begin{equation}
-\gamma = \frac{m_{c_i s_j}}{\sum m_{c_i s_j}}
-\end{equation}
+In addition, we created 10 new features based on the original variables, which were utilized during the modeling process with the LightGBM model.
 
@@
 
+\subsection{Data Mining}
+\subsubsection{Athlete Service Status}
+To predict future scenarios, we analyzed the trends in the number of participants for each country, event and year, and applied \textbf{Linear Regression} for fitting.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/Number.png}
+	\caption{Number of New and Leave Athletes in Each Year}
+	\label{fig:aa}
+\end{figure}
+
+Then, we compiled the distribution of the times of participations and the distribution of athlete tenure based on historical data, as shown in the figure.
+\begin{figure}[htbp]
+	\centering
+	\begin{subfigure}[b]{.55\textwidth}
+		\includegraphics[width=\textwidth]{img/Times.png}
+		\caption{Distribution of Serve Times}\label{subfig:left}
+	\end{subfigure}
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{img/Years.png}
+		\caption{Distribution of Serve Years}\label{subfig:right}
+	\end{subfigure}
+	\caption{Two images}\label{fig:subfigures}
+\end{figure}
+
+From the distribution chart, it can be seen that nearly 80% of athletes have participated in 1 or 2 matches, with the average number of serve times being 1.94, meaning each athlete participates in approximately 2 matches.
+Based on this assumption, we consider that each participating athlete will compete in 2 matches on average.
+Additionally, around 80% of athletes have participated in only 1 Olympic Games, while nearly 20% have participated in 2.
+Therefore, we can assume that 20% of the veteran athletes will continue to compete in the next Olympic Games, providing a basis for determining which athletes will continue to participate.
+
+To predict the Participant List, we employed Monte Carlo simulation, which consisted of two parts: the first part involved selecting 20% of veteran athletes to continue competing (20% conforming to the original data distribution), while the second part generated new random athletes based on historical athlete data.
+
+In the previous sections, we determined which athletes will continue to compete.
+To simulate new random athletes, we simplified each individual into three parameters: the probabilities of winning a gold, silver, or bronze medal.
+
+For a given country in a specific event, the average number of medals won by all athletes serves as the standard number of medals for a representative athlete.
+The medal expectations were categorized into 3 scenarios: optimistic, moderate, and pessimistic.
+The optimistic expectation was calculated by averaging the top 50% of the team, the moderate expectation by averaging all team members, and the pessimistic expectation by averaging the bottom 50%.
+
+Using the Previous Participants' Records as the basis for Monte Carlo simulation, we ultimately determined the Participant List Prediction.
+
+\subsubsection{Distribution of Countries' Strength Sports}
+Due to factors such as cultural and geographical environments, countries exhibit distinct advantages in different events.
+For example, Kenya and Ethiopia excel in long-distance running, particularly in Athletics, largely due to the training conditions in high-altitude regions.
+Brazil, with its deep football culture, has produced many world-class players, a result of its warm climate and environment conducive to year-round outdoor sports.
+
+By analyzing the performance of various countries in different events across past Olympic Games, we extracted a feature variable $\gamma$(Event Adeptness Coefficient), to represent the advantages of these countries in certain events..
+
+%公式
+\begin{equation}
+	\gamma = \frac{m_{c_i,e_j}}{\sum m_{c_i,e_j}}
+\end{equation}
+
+By extracting features, we mined the level of expertise of each country in different events within the dataset, such as China's performance across various events, as shown in the figure below:
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/Percentage.jpg}
+	\caption{Percentage of Medals of Different Sports in China}
+	\label{fig:aa}
+\end{figure}
+
+\subsubsection{Changes in Medal Count}
+Since the IOC makes adjustments to events each year, the total number of medals awarded in each event does not remain exactly the same each year.
+To address this, we applied \textbf Linear Regression to fit the number of gold, silver, and bronze medals awarded in each event across past Olympic Games and predicted the medal distribution for the upcoming Olympic Games, providing a reference for subsequent operations.
+
+\section{Task1:Medal Prediction Model Based on LightGBM}
+\subsection{Medal Standings}
+Numerous factors influence the medal table.
+To predict the medal standings for the next Olympics, we incorporated factors identified during the data preprocessing stage, including nation level, the list of participating athletes, each country's adeptness in specific events, and adjustments to medal counts.
+
+Additionally, as host countries typically benefit from home advantage, the factor of "whether a country is the host"or "whether hosting for the first time" was also considered.
+This factor was categorized into 3 categories and quantified for inclusion in the model.
+Ultimately, these five factors were collectively summarized as \textbf{National Background Factors}.
+
+% \usepackage{longtable}
+
+\begin{longtable}{|c|c|} 
+	\hline
+	Category & Definition               \endfirsthead 
+	\hline
+	0        & Not host                 \\ 
+	\hline
+	1        & Host for the 1st time    \\ 
+	\hline
+	2        & Host for more than once  \\
+	\hline
+\end{longtable}
+
+The prediction of the Olympic medal table is essentially a multi-task learning problem, with the goal of predicting the number of gold, silver, and bronze medals each country is likely to win in different events.
+To accomplish this task, we need to input a large and diverse set of data while outputting predictions for multiple medal categories.
+These features are highly suitable for the LightGBM model.
+
+Building on GBDT, LightGBM accelerates the computation using histograms, optimizing training efficiency and enabling the fast processing of high-dimensional, sparse, large-scale data.
+Compared to traditional logistic regression, LightGBM can capture nonlinear relationships through tree splitting, offering a performance advantage in accurately handling complex data and nonlinear relationships, significantly improving accuracy.
+Additionally, it can automatically handle missing values, providing great convenience for data preprocessing.
+
+As a gradient boosting-based regression model, in LightGBM, the objective function consists of two parts: the loss function and the regularization term.
+
+\begin{equation}
+	\mathcal{L} = \sum_{i=1}^{n} L(y_i, \hat{y}_i^{(m-1)} + \eta f_m(x_i)) + \Omega(f_m)
+\end{equation}
+The optimized loss function based on GBDT is represented as squared error in the medal prediction regression task.
+
+$y_i$denotes the true value.
+$\hat{y}_i^{(m-1)}$is the current model's predicted value.
+$\hat{y}_i^{(m-1)}$+$\eta f_m(x_i)$is the model's predicted value at the m-th step during the gradient boosting model update process.
+$\Omega(f_m)$ Regularization term, which prevents overfitting of the model and controls the complexity of the trees.
+
+We input the previously obtained data into LightGBM for iterative model training.
+After training, we input the factors affecting the predictions for the next edition into the model, ultimately obtaining the predicted medal table for the 2028 Summer Olympics in Los Angeles, USA, as follows:
 %奖牌榜预测图
-
 \begin{figure}[htbp]
@@
 \end{figure}
+According to the model's predictions, the United States is expected to see a significant increase in medal count compared to the previous year, while France will experience a notable decrease, which is related to the home-field advantage of the host country.
+Additionally, due to changes in the number of medals for certain events, the medal counts for Australia, Japan, and the Netherlands are expected to rise, while Italy and South Korea will see a decline.
+China's medal count is projected to remain relatively stable.
 
-% \usepackage{longtable}
+To more accurately simulate the actual number of medals won, we simplify each individual into 3 parameters: the probabilities of winning gold, silver, and bronze medals.
+For a specific country and event, the average number of medals won by all team members represents the probability that a standard "virtual athlete" should have.
 
+For the expected outcomes, the optimistic expectation is calculated by averaging the top 50% of the team, the moderate expectation is based on the average of all team members, and the pessimistic expectation is derived by averaging the bottom 50% of the team.
+
+The "Previous Participants Record" serves as the basis for the Monte Carlo simulation, which consists of two parts: the first part involves selecting 20% of veteran athletes to continue competing (with 20% corresponding to the original data distribution), and the second part uses historical athlete data to generate new random athletes.
+
+Based on the model, we predict the medal outcomes for each country in the 2028 Olympic Games.
+A partial result is provided here, with the full version available in the appendix.
+The predicted outcomes for the United States are presented, showing that, overall, the optimistic expectation > moderate expectation > pessimistic expectation.
 \begin{longtable}{l|c|c|c|c|c|c|c|c|c|c}
@@
 \end{longtable}
+%4.2
+\subsection{Countries that Win Their First Medal}
+Since the model used for predicting the medal table in the previous section yields varying levels of accuracy for countries of different rankings, the predictions for higher-ranked countries, such as the United States and China, are more accurate.
+In contrast, the prediction errors for lower-ranked countries are larger.
+Clearly, countries that have not yet won medals fall into the category with higher prediction errors, so the previous model is not applicable in this case.
 
-\subsection{Countries that Win Their First Medal}
+Therefore, for countries that have never won a medal before, we calculate their first medal index $\xi$.
+%公式 未知
 
+The number of competitions is counted from the original dataset, and the expected increase in the number of medals for the next edition is predicted through a Linear Regression model based on historical data.
+
+As the number of competitions and the expected increase in medals for the next edition increase for countries that have not won medals, the likelihood of these countries winning medals becomes higher.
+Therefore, the first medal index $\xi$ is positively correlated with the probability of a country that has not won a medal securing its first medal in the next Olympic Games, meaning that the larger the $\xi$ value, the higher the likelihood of winning the first medal.
+
+In order to visualize the accuracy of a country's first medal prediction, we normalized the first medal index using the Z-score and then multiplied it by 0.8 to obtain the first medal coefficient $\kappa$.
+
+\begin{equation}
+	\kappa = 0.8 \times \frac{\xi - \overline{\xi}}{\sigma}
+\end{equation}
+Here,$\overline{\xi}$ refers to the mean of the original data, and$\sigma$refers to the standard deviation of the original data.
+The calculated results are as follows:
 %首奖可能性图
-
 \begin{figure}[htbp]
@@
 
+As shown in the figure, Sierra Leone (SLE), Antigua and Barbuda (ANT), and Papua New Guinea (PNG) are the three countries most likely to win their first medal in the next Olympic Games, with accuracies approximately 0.8, 0.77, and 0.74, respectively.
+
+%4.3
 \subsection{Events and Medal Counts by Countries}
+In the data preprocessing section, we have calculated the adeptness of each country in each event, thus allowing us to roughly estimate the events in which each country excels.
 
+We input the data of the dominant events of multiple countries into the prediction model and use \textbf{Spearman's Rank Correlation Coefficient} to analyze the correlation between the total medal count of a country and the medal count of a specific event, as well as the number of events in that event.
+This is because we cannot confirm that the data sample follows a normal distribution, nor can we ascertain that the relationship between the dominant events and the total medal count is linearly correlated.
+Spearman's Rank Correlation Coefficient is suitable for evaluating \textbf{nonlinear} relationships.
+
+We studied the relationship between China's total medal count, gold medal count, and the number of awards and events in table tennis.
+For each pair of variables, we ranked the data points and assigned ranks to each data point.
+The rank difference for each data point is calculated as:
+
+\begin{equation}
+	d_i = R(X_i) - R(Y_i)
+\end{equation}
+
+\begin{equation}
+	R_s = 1 - \frac{6 \sum d_i^2}{n(n^2 - 1)}
+\end{equation}
+
+Here, $d_i$ is the rank difference of the two variables for the iii-th data point. 
+Next, we compute the Spearman's Rank Correlation Coefficient ($R_s$).
+
+The absolute value of $R_s$ closer to 1 indicates a stronger correlation, while closer to 0 indicates a weaker correlation.A positive $R_s$ indicates a positive correlation between the two variables, meaning an increase in one variable typically accompanies an increase in the other.
+
+Through extensive data analysis, we identified 3 typical examples: table tennis in China, Athletics in Jamaica, and rowing in New Zealand, as shown in the figure.
 %三个国家擅长项目的图
@@
 
-\section{Task2:}
+We found that although China has a significant advantage in table tennis, the relationship between the development of the event and China's total medal count is relatively weak.
+This suggests that China's overall athletic adeptness is stable and less influenced by a single dominant event.
 
-The results are shown in Figure \ref{fig:result}, where $t$ denotes the time in seconds, and $c$ refers to the concentration of water in the boiler.
+Additionally, Jamaica's total medal count shows a strong positive correlation with its performance in athletics, indicating the country's heavy reliance on athletics competitions.
+Since athletics is a well-established and stable event with minimal fluctuations in the number of events held each year, the relationship between the number of events and Jamaica's total medal count is relatively weak.
 
+New Zealand also has a high dependency on rowing, with a substantial portion of its medals coming from this event.
+However, unlike Jamaica, rowing is not as established as athletics, and the number of competitions fluctuates from year to year.
+As a result, New Zealand's overall medal count is highly dependent on the rise and fall of rowing's prominence.
+\subsection{Model Performances}
+
+We calculated four evaluation metrics: Mean Squared Error (MSE), Root Mean Squared Error (RMSE), Mean Absolute Error (MAE), and the Coefficient of Determination (\(\mathbf{R}^2\)).
+
+Among these, smaller values for the first three metrics and a larger value for R² indicate better model performance.
+
+% \usepackage{longtable}
+
+\begin{longtable}{l|l|l|l|l} 
+	\caption{Model Performances(LightGBM)}\\ 
+	\hline
+	\multicolumn{1}{c|}{\textbf{Model}} & \multicolumn{1}{c|}{\textbf{MSE}} & \multicolumn{1}{c|}{\textbf{RMSE}} & \multicolumn{1}{c|}{\textbf{MAE}} & \multicolumn{1}{c}{\(\mathbf{R}^2\)}  \endfirsthead 
+	\hline
+	Gold Prediction                     & 0.0235                            & 0.180                              & 0.030                             & 0.890                              \\ 
+	\hline
+	Silver Prediction                   & 0.0239                            & 0.185                              & 0.033                             & 0.825                              \\ 
+	\hline
+	Bronze Prediction                   & 0.0231                            & 0.187                              & 0.034                             & 0.806                              \\
+	\hline
+\end{longtable}
+
+%雷达图
 \begin{figure}[htbp]
 	\centering
-	\includegraphics[width=16cm]{img/Volleyball.png}
+	\includegraphics[width=8cm]{img/Performance.png}
+	\caption{Model Performance Radar Chart}
+	\label{fig:aa}
+\end{figure}
+
+It can be observed that the evaluation metrics for the prediction of the 3 types of medals show good performance with relatively small differences.
+
+A comparison reveals that the model's prediction accuracy for gold medals is relatively higher, with the highest \(\mathbf{R}^2\) and the lowest Root Mean Squared Error (RMSE) and Mean Absolute Error (MAE).
+
+%5.1 排球
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/Volleyball.png}
 	\caption{Medal Count of Women's Volleyball Teams(CHN vs USA) Over Time}
@@
 
-\clearpage
-
 %引用图像示例Figure \ref{fig:subfigures}
@@
 
-% \usepackage{longtable}
-
-\begin{longtable}{l|l|l|l|l} 
-	\caption{Model Performances(LightGBM)}\\ 
-	\hline
-	\multicolumn{1}{c|}{\textbf{Model}} & \multicolumn{1}{c|}{\textbf{MSE}} & \multicolumn{1}{c|}{\textbf{RMSE}} & \multicolumn{1}{c|}{\textbf{MAE}} & \multicolumn{1}{c}{\(\mathbf{R}^2\)}  \endfirsthead 
-	\hline
-	Gold Prediction                     & 0.0235                            & 0.180                              & 0.030                             & 0.690                              \\ 
-	\hline
-	Silver Prediction                   & 0.0239                            & 0.185                              & 0.033                             & 0.625                              \\ 
-	\hline
-	Bronze Prediction                   & 0.0231                            & 0.187                              & 0.034                             & 0.606                              \\
-	\hline
-\end{longtable}
-
 \begin{figure}[htbp]
 	\centering
-	\includegraphics[width=16cm]{img/Performance.png}
-	\caption{Model Performance Radar Chart}
+	\includegraphics[width=16cm]{img/Monopolized Sports.png}
+	\caption{Adeptness of Countries in Specitific Project}
 	\label{fig:aa}
 \end{figure}
+
+\section{Task2:A "Great Coach" Effect}
+
+\section{Verification of the "Great Coach" Effect}
+The "Great Coach" effect can cause significant differences in the performance of relevant countries in corresponding events.
+To collect evidence of changes caused by this effect, we use a Bayesian Changepoint Detection (BEAST) model.
+
+The BEAST model uses Bayesian inference to calculate the posterior probabilities of changes occurring at different time points, determining which time points are potential change points.
+
+In the time series dataset \(X = (x_1, x_2, x_3, \ldots, x_T)\), we identify the set of change points \(C = \{c_1, c_2, \ldots, c_K\}\), where each \(c_k\) represents a change point.
+Using Bayes' theorem, we can compute the posterior probability for each possible change point $c_k$:
+
+\begin{equation}
+	P(c_k \mid X) = \frac{P(X \mid c_k) P(c_k)}{P(X)}
+\end{equation}
+In this case, \( P(X|c_k) \) represents the likelihood of the data at the change point \( c_k \), \( P(c_k) \) is the prior probability, and \( P(X) \) is the marginal likelihood of the data.
 
@@
 %公式代码集合
-
-\begin{equation}
-	\mathcal{L} = \sum_{i=1}^{n} L(y_i, \hat{y}_i^{(m-1)} + \eta f_m(x_i)) + \Omega(f_m)
-\end{equation}
-
-$y_i$\\
-$\hat{y}_i^{(m-1)}$\\
-$\eta f_m(x_i)$\\
-$\Omega(f_m)$\\
-
-\begin{equation}
-	\kappa = 0.8 \times \frac{\xi - \overline{\xi}}{\sigma}
-\end{equation}
-
-$\overline{\xi}$
-$\sigma$
-
-\begin{equation}
-	d_i = R(X_i) - R(Y_i)
-\end{equation}
-
-\begin{equation}
-	R_s = 1 - \frac{6 \sum d_i^2}{n(n^2 - 1)}
-\end{equation}
-
-$d_i$
-$R_s$
-
-\begin{equation}
-	P(c_k \mid X) = \frac{P(X \mid c_k) P(c_k)}{P(X)}
-\end{equation}
 
@@
 
+%6.1
+\subsection{Global Geopolitics}
+
+%6.1 男女比例图
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=16cm]{img/Gender with Award.png}
+	\caption{Gender Distribution of Athletes(with Award)}
+	\label{fig:aa}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=16cm]{img/Gender.png}
+	\caption{Gender Distribution of Athletes}
+	\label{fig:aa}
+\end{figure}
+
+%6.2
+\subsection{Strength events}
+
+%6.3
+\subsection{Global Geopolitics}
+
+%6.3 花里胡哨图
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=16cm]{img/3.3-1.png}
+	\caption{Trend of Medal Proportions by Country Annually}
+	\label{fig:aa}
+\end{figure}
+
 \section{Sensitivity Analysis}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=16cm]{img/Sensitive Analysis 1.png}
+	\caption{LightGBM Feature Importance}
+	\label{fig:aa}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\begin{subfigure}[b]{.32\textwidth}
+		\includegraphics[width=\textwidth]{img/Decline1.png}
+		\caption{France}\label{subfig:1}
+	\end{subfigure}
+	\hfill 
+	\begin{subfigure}[b]{.32\textwidth}
+		\includegraphics[width=\textwidth]{img/Decline2.png}
+		\caption{Sweden}\label{subfig:2}
+	\end{subfigure}
+	\hfill 
+	\begin{subfigure}[b]{.32\textwidth}
+		\includegraphics[width=\textwidth]{img/Decline3.png}
+		\caption{Germany}\label{subfig:3}
+	\end{subfigure}
+	\caption{Three images}\label{fig:subfigures}
+\end{figure}
 

### 2025-01-27 论文/PAPER.tex

@@
 \begin{abstract}
-The Olympic Games serve as both a stage for athletes' performances and a focal point for global competition in the medal table.
-This study aims to predict the medal distribution for the 2028 Olympics using a bottom-up approach, estimating the total medal count for each country based on individual athletes' expected performance.
-To achieve this, multiple predictive models were developed to forecast the future medal table and uncover deeper data features, providing valuable decision-making insights for national Olympic committees.
-
-In Task 1, data preprocessing and feature engineering were first performed, utilizing KMeans++ and other statistical methods to extract latent features.
-Subsequently, the LightGBM model was employed to predict the number of gold, silver, and bronze medals for each country at the 2028 Olympics.
-The results indicate that a country's medal performance is closely related to factors such as home advantage, adeptness in specific events, and the individual performance levels of athletes.
-The model demonstrated high accuracy, with an R² value of 0.890 for the gold medal prediction, suggesting the reliability of the results.
+	The Olympic Games serve as a stage for athletes and a focal point for global medal table competition.
+This study predicts the 2028 Olympics medal distribution using a \textbf{bottom-up approach}, estimating national totals from individual athlete performance expectations.
+
+	In \textbf{Task 1}, data preprocessing and feature engineering were conducted using \textbf{KMeans++} and other statistical methods.
+The \textbf{LightGBM} model was then used to predict the number of gold, silver, and bronze medals for each country at the 2028 Olympics.
+Results show that medal performance is closely linked to factors like home advantage, strength in specific events, and athlete performance.
+The model achieved high accuracy, with an \textbf{R²} value of \textbf{0.890} for gold medal predictions, indicating reliable results.
 
 	For countries yet to win medals, our research revealed that participation in high-growth potential events increases the likelihood of securing their first medal.
-Spearman Correlation Analysis further examined the degree of dependency on specific events by certain countries.
-The findings show that countries with strong overall sports performance exhibit a lower dependency on specific events, maintaining stable results, while weaker sports nations tend to rely more on select events.
-In some cases, the correlation coefficient in athletics events was as high as 0.894, indicating a concentration of athletic development in a few specific areas.
-
-In Task 2, we explored the "great coach effect" by applying Bayesian Change Point Detection (BEAST) to analyze instances from multiple countries.
+\textbf{Spearman Correlation Analysis} further examined the degree of dependency on specific events by certain countries.
+
+	The findings indicate that countries with strong overall sports performance exhibit lower reliance on specific events, yielding stable results, while weaker nations depend more on select events.
+In certain cases, the \textbf{correlation coefficient} in athletics reached \textbf{0.894}, reflecting a concentration of athletic development in specific areas.
+
+	In \textbf{Task 2}, we explored the "great coach effect" by applying \textbf{Bayesian Change Point Detection (BEAST)} to analyze instances from multiple countries.
 The study found a significant correlation between the points of inflection in some countries' sports performance and the tenure of a "great coach," validating the importance of this effect.
 
-Additionally, forward CUSUM analysis was employed to examine changes in medal sequences, identifying the weakest areas for each country.
-The results show that many countries, which once had competitive advantages in certain events, have seen a decline in these advantages over time.
-Based on this, we propose targeted coach recommendations for countries in need of improvement in specific areas.
-
-In Task 3, we conducted in-depth data mining and analysis based on the models and data mentioned earlier, revealing several novel insights, such as the gender ratio of athletes, advantages derived from a country's traditional events, and changes in medal counts reflecting shifts in international political dynamics.
-
-The study found that the gender ratio in the Olympics is gradually balancing, with a significant increase in the proportion of female medals.
-
-Furthermore, some countries dominate traditional events, with their medal share reaching up to 88.
-Consequently, Olympic committees seeking to increase their medal counts should consider investing more in their national traditional events.
-
-Finally, through time-series analysis of changes in medal distribution, multiple anomalies were identified, reflecting not only the evolution of the Olympics from its early stages to maturity but also their connection to the political context of the 20th century.
+	Additionally, forward \textbf{CUSUM} analysis was used to examine medal sequence changes, identifying each country's weakest areas.
+The results reveal that many countries, once dominant in certain events, have seen a decline in these advantages over time.
+Based on these findings, targeted coach recommendations are proposed for countries requiring improvement in specific areas.
+
+	In \textbf{Task 3}, we conducted in-depth \textbf{data mining} and analysis based on the models and data mentioned earlier, revealing several novel insights, such as the gender ratio of athletes, advantages derived from a country's traditional events, and changes in medal counts reflecting shifts in international political dynamics.
+
+	The study found that the \textbf{gender ratio} in the Olympics is gradually balancing, with a significant increase in the proportion of female medals.
+
+	Furthermore, some countries dominate traditional events, with their medal share reaching up to \textbf{\( 88\% \)}.
+Consequently, Olympic committees seeking to increase their medal counts should consider investing more in their national \textbf{traditional events}.
+
+	Finally, through \textbf{Time Series Analysis} of changes in medal distribution, multiple anomalies were identified, reflecting not only the evolution of the Olympics from its early stages to maturity but also their connection to the political context of the 20th century.
 
@@
 	\vspace{5pt}
-    \textbf{Keywords}: \textbf{ A, B, C,  }
+	\textbf{Keywords}: \textbf{ KMeans++, LightGBM, Spearman Correlation, BEAST, CUSUM }
 
@@
 \subsection{Our work}
-We do such things ...
-
-%图片示例（water.png）
-%\begin{figure}[htbp]
-%	\centering
-%	\includegraphics[width=.8\textwidth]{water.png}
-%	\caption{The result of Model 2}\label{fig:result}
-%\end{figure}
+We preprocess the data provided before analyzing matches and mainly utilize 3 models. The specific work was as follows
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/Level1.png}
+	\caption{Scatter plot of national level classification (based on Kmeans++clustering algorithm)}
+	\label{fig:aa}
+\end{figure}
+
+s
+
 \begin{enumerate}[\bfseries 1.]
@@
 \end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/OP1.png}
+	\caption{USA Medal count prediction}
+	\label{fig:aa}
+\end{figure}
+
 According to the model's predictions, the United States is expected to see a significant increase in medal count compared to the previous year, while France will experience a notable decrease, which is related to the home-field advantage of the host country.
@@
 
-For the expected outcomes, the optimistic expectation is calculated by averaging the top 50% of the team, the moderate expectation is based on the average of all team members, and the pessimistic expectation is derived by averaging the bottom 50% of the team.
-
-The "Previous Participants Record" serves as the basis for the Monte Carlo simulation, which consists of two parts: the first part involves selecting 20% of veteran athletes to continue competing (with 20% corresponding to the original data distribution), and the second part uses historical athlete data to generate new random athletes.
+For the expected outcomes, the optimistic expectation is calculated by averaging the top \( 50\% \) of the team, the moderate expectation is based on the average of all team members, and the pessimistic expectation is derived by averaging the bottom \( 50\% \) of the team.
+
+The "Previous Participants Record" serves as the basis for the Monte Carlo simulation, which consists of two parts: the first part involves selecting \( 20\% \) of veteran athletes to continue competing (with \( 20\% \) corresponding to the original data distribution), and the second part uses historical athlete data to generate new random athletes.
 
@@
 
+%引用图像示例Figure \ref{fig:subfigures}
+%Figure \ref{fig:subfigures} gives an example of subfigures. Figure \ref{subfig:left} is on the left, and Figure \ref{subfig:right} is on the right.
+
+\section{Task2:A "Great Coach" Effect}
+\subsection{Verification of the "Great Coach" Effect}
+The "Great Coach" effect can cause significant differences in the performance of relevant countries in corresponding events.
+To collect evidence of changes caused by this effect, we use a Bayesian Changepoint Detection (BEAST) model.
+
+The BEAST model uses Bayesian inference to calculate the posterior probabilities of changes occurring at different time points, determining which time points are potential change points.
+
+In the time series dataset \(X = (x_1, x_2, x_3, \ldots, x_T)\), we identify the set of change points \(C = \{c_1, c_2, \ldots, c_K\}\), where each \(c_k\) represents a change point.
+
+Using Bayes' theorem, we can compute the posterior probability for each possible change point $c_k$:
+
+\begin{equation}
+	P(c_k \mid X) = \frac{P(X \mid c_k) P(c_k)}{P(X)}
+\end{equation}
+
+In this case, \( P(X|c_k) \) represents the likelihood of the data at the change point \( c_k \), \( P(c_k) \) is the prior probability, and \( P(X) \) is the marginal likelihood of the data.
+
+By calculating the posterior probability for each change point, we can identify the moments when significant changes occurred in the data.
+
+Thus, we simply need to extract the historical award data for the relevant countries and events from the dataset and perform Bayesian Changepoint Detection.
+
+This allows us to determine how much influence these "great coaches" had on the medal counts achieved by these countries in the relevant events during the periods when Lang Ping coached the Chinese and U.S.
+volleyball teams, and when Bela Karolyi coached the Romanian and U.S.
+women's gymnastics teams.
+
+Since the value of gold, silver, and bronze medals is not the same, we standardized the data by assigning weights to the medals. The final medal count in the dataset is calculated as follows:
+
+%公式 未知
+
+Taking Lang Ping's leadership of the Chinese and U.S.
+volleyball teams as an example, we extracted the data for Chinese and U.S.
+volleyball from the original medal dataset.
+Through Bayesian Changepoint Detection, we found that the period when Lang Ping changed coaching countries coincided with a significant change in the dataset, as shown in the figure below:
+
 %5.1 排球
@@
 \end{figure}
+Clearly, after Lang Ping began coaching the U.S.
+team in 2005, the U.S.
+volleyball team showed remarkable improvement in the next Olympic Games, while the Chinese team experienced significant regression.
+However, after Lang Ping returned to coach China in 2013, the Chinese team quickly rose from the trough and regained their peak performance, while the U.S.
+team showed a decline.
+
+Between 2016 and 2020, the Chinese team underwent a period of stagnation due to the retirement of key players and the lack of a strong new generation.
+
+Similarly, Bela Karolyi's coaching of the Romanian and U.S.
+women's gymnastics teams shows significant changes, with similar patterns to Lang Ping's coaching history.
+In addition, we also studied other similar cases.
+Therefore, we can conclude that the "great coach" effect has a significant impact on a country's medal count in the corresponding event.
+
+\subsection{Countries Recommended for Hiring Coaches}
+After confirming the significant impact of the "great coach" on the medal count, we began to analyze which events a country should consider investing in "excellent coaches." For this, we use the CUSUM algorithm.
+
+The CUSUM method detects deviations in a data sequence by calculating the cumulative sum, which is the running total of the deviation between each data point and the expected or baseline value.
+It is effective at detecting small changes in the mean and has been widely used in quality control, process monitoring, and other fields.
+
+We select the forward CUSUM to detect trends in the medal count of a particular country's sports event.
+If the curve shows a prolonged downward trend, it indicates a significant regression in that event, suggesting the need for a coach change.
+
+\begin{equation}
+	C_t^+ = \max(0, C_{t-1}^+ + (X_t - \mu - k))
+\end{equation}
+
+Here, $C_t^+ $represents the cumulative value of the forward CUSUM, $X_t$ is the t-th data point, $\mu$ is the expected or average value (target value), and $k$ is the threshold, indicating the allowable minimum deviation.
+Typically, a reasonable $k$ value is chosen, often a multiple of the process standard deviation.
+
+If the curve shows a prolonged downward trend, it indicates that the event has significant regression, suggesting the need for a coach. The results obtained are as follows:
 
@@
 
-%引用图像示例Figure \ref{fig:subfigures}
-%Figure \ref{fig:subfigures} gives an example of subfigures. Figure \ref{subfig:left} is on the left, and Figure \ref{subfig:right} is on the right.
+We observe that sailing was a dominant event for France when the earliest Olympic Games were held.
+Although it did not remain as developed in the subsequent years, it still maintained relatively stable results from the 1930s to the 1970s.
+However, after the 1970s, there was a clear downward trend, which suggests the need to hire a coach.
+
+Sweden's dominance in athletics and shooting during the 1920s to 1950s showed significant advantages, but both events have experienced a substantial decline over time, possibly due to a decrease in the nation's emphasis on events competitions.
+Therefore, it is recommended to hire a coach.
+
+Germany’s swimming did not show any notable advantage before the 1990s.
+However, at the beginning of the 21st century, it emerged as a new powerhorse.
+Yet, there are clear signs of decline in the 2010s to 2020s.
+To maintain swimming’s competitive edge, it would be beneficial to hire a coach.
+
+\section{Task3:Other Original Insights}
+
+\subsection{Gender Distribution}
+
+We analyzed the gender ratio in the Olympics, focusing on two aspects: the male-to-female ratio of athletes participating in the Games and the male-to-female ratio of medal winners, as shown in the figure.
+
+	%6.1 男女比例图
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=14cm]{img/Gender with Award.png}
+		\caption{Gender Distribution of Athletes(with Award)}
+		\label{fig:aa}
+	\end{figure}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=14cm]{img/Gender.png}
+		\caption{Gender Distribution of Athletes}
+		\label{fig:aa}
+	\end{figure}
+
+Firstly, the gender ratio in the Olympics has become increasingly balanced, with the male-to-female ratio nearly equal, shifting from a male-dominated ratio to approximately 1:1.
+The number of female athletes has steadily increased over time, particularly in the late 20th and early 21st centuries, with a more pronounced growth trend.
+
+This trend not only reflects the efforts of the International Olympic Committee and national events organizations to promote gender equality, including providing more opportunities for female athletes to participate and offering more events for women, but also signifies an increased societal awareness of gender equality, leading to more opportunities for women to engage in sports.
+
+Moreover, the trends in the gender distribution of athletes (with awards) and the overall athlete distribution exhibit almost identical patterns of growth or decline.
+
+%6.2
+\subsection{Strength events}
+
+In analyzing the national strengths in specific events, we found that certain countries have a dominant advantage, even to the point of forming a dominance, with their share of the total medal count reaching as high as \( 30\% \), \( 50\% \), or even over \( 80\% \).
 
@@
 
-\section{Task2:A "Great Coach" Effect}
-
-\section{Verification of the "Great Coach" Effect}
-The "Great Coach" effect can cause significant differences in the performance of relevant countries in corresponding events.
-To collect evidence of changes caused by this effect, we use a Bayesian Changepoint Detection (BEAST) model.
-
-The BEAST model uses Bayesian inference to calculate the posterior probabilities of changes occurring at different time points, determining which time points are potential change points.
-
-In the time series dataset \(X = (x_1, x_2, x_3, \ldots, x_T)\), we identify the set of change points \(C = \{c_1, c_2, \ldots, c_K\}\), where each \(c_k\) represents a change point.
-Using Bayes' theorem, we can compute the posterior probability for each possible change point $c_k$:
-
-\begin{equation}
-	P(c_k \mid X) = \frac{P(X \mid c_k) P(c_k)}{P(X)}
-\end{equation}
-In this case, \( P(X|c_k) \) represents the likelihood of the data at the change point \( c_k \), \( P(c_k) \) is the prior probability, and \( P(X) \) is the marginal likelihood of the data.
-
-\section{Task3}
-
-%公式代码集合
-
-\begin{equation}
-	C_t^+ = \max(0, C_{t-1}^+ + (X_t - \mu - k))
-\end{equation}
-$C_t^+ $
-
-	\begin{equation}
-		\phi_i(f) = \sum_{S \subseteq N \setminus \{i\}} \frac{|S|!(|N| - |S| - 1)!}{|N|!} [f(S \cup \{i\}) - f(S)]
-	\end{equation}
-
-$\phi_i(f)$
-
-%6.1
-\subsection{Global Geopolitics}
-
-%6.1 男女比例图
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=16cm]{img/Gender with Award.png}
-	\caption{Gender Distribution of Athletes(with Award)}
-	\label{fig:aa}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=16cm]{img/Gender.png}
-	\caption{Gender Distribution of Athletes}
-	\label{fig:aa}
-\end{figure}
-
-%6.2
-\subsection{Strength events}
+As shown in the figure, the United Kingdom holds an astonishing dominance in Motorboating and Cricket.
+Since Motorboating has only appeared twice in the Olympics and Cricket is a newly added event in the 2028 Olympics, these events are not highly regarded by other countries, except for the UK, which has a natural advantage in these traditional sports.
+
+Therefore, we suggest that national Olympic committees consider investing in such events if they aim to win more medals.
+
+Among the events commonly featured in recent Olympics, table tennis serves as a very typical example.
+China, with a remarkable \( 46\% \) share of table tennis medals, holds a monopoly advantage in this event.
+This is due to the development of a professional and efficient events system, strongly supported by the Chinese government.
+
+Based on the previously confirmed "great coach" effect, if other countries wish to enhance their capabilities in these events and win more medals, they may consider hiring coaches from these dominant countries.
 
@@
 \subsection{Global Geopolitics}
+As of now, the Olympics has been held 33 times, spanning from 1896 to 2024, covering nearly 130 years.
+Thus, the Olympics has witnessed the dramatic shifts in global geopolitics throughout the 20th century.
+We created a stacked area chart based on each country's share of the total medals, offering a glimpse into the significant impact of world affairs on Olympic results.
 
@@
 
+From the chart, we can observe four notable anomalies in the medal distribution: in 1904, 1980, 1984, and 1992.
+
+The 1904 Olympics, held in St.
+Louis, Missouri, USA, lasted five and a half months.
+Due to the long travel distance and the absence of U.S.
+President Theodore Roosevelt and IOC President Pierre de Coubertin at the opening and closing ceremonies, only 12 countries participated, marking the lowest number of participating countries in Olympic history.
+The U.S.
+dominated the medal count with a significant lead.
+
+The 1980 Olympics, held in Moscow, saw a boycott led by the United States in response to the Soviet invasion of Afghanistan in 1979.
+Around 65 countries, mostly from the Western bloc, refrained from sending athletes.
+As a result, the participating nations were primarily from the socialist camp, especially the Soviet Union and Eastern European countries, with the Soviet Union winning the most medals.
+
+Similarly, the 1984 Los Angeles Olympics was also politically influenced.
+Following the 1980 boycott, the Soviet Union and other Eastern Bloc countries decided to boycott the 1984 Games in retaliation.
+The 1984 Olympics marked a significant turning point in Olympic history, showcasing the U.S.'s strong capabilities in organizing the event and symbolizing the beginning of the commercialization of the Games.
+
+The 1992 Barcelona Olympics was a pivotal event, both as a major competition in the post-Cold War era and a reflection of significant global political changes.
+While political issues in certain countries and regions may still cause fluctuations in participation, the confrontational situation of the Cold War no longer had a frequent impact on the hosting and participation in the Games.
+
+From the chart, it is evident that after the 1992 Olympics, the distribution of Olympic medals stabilized, and the development of the Olympics became more consistent.
+
 \section{Sensitivity Analysis}
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=16cm]{img/Sensitive Analysis 1.png}
+Sensitivity Analysis is used to evaluate the sensitivity of model outputs to changes in input features.
+Through this analysis, we can quantify the dependency of final prediction results prediction outcomes on specific data features, such as the adeptness of a particular country in a specific event or the previous award probability of an athlete.
+
+LightGBM comes with a feature importance function that identifies the features with the greatest impact on the model’s predictions.
+By using plot\_importance() function, we can visualize the importance of each feature.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=14cm]{img/Sensitive Analysis 1.png}
 	\caption{LightGBM Feature Importance}
@@
 
+The above figure shows the feature importance distribution for the gold medal prediction model.
+Since we generated PolynomialFeatures during training, the features observed here are the products of several individual features.
+
+From the figure, we can see that the probability of an athlete winning a medal in the past, as well as the degree of a country's advantage in a specific event, have the greatest influence on the final prediction results.
+Additionally, the athlete’s past medal-winning probability also has a significant impact on the prediction.
+
+Furthermore, we can use Shapley value analysis to assess the model's sensitivity.
+SHAP (SHapley Additive exPlanations) is a game theory-based model explanation method used to interpret machine learning model predictions.
+It assigns each feature a contribution to the model's prediction, helping us understand the importance and influence of each feature in the given prediction result.The formula for Shapley value is as follows:
+
+\begin{equation}
+	\phi_i(f) = \sum_{S \subseteq N \setminus \{i\}} \frac{|S|!(|N|-|S|-1)!}{|N|!} [ f(S \cup \{i\}) - f(S)]
+\end{equation}
+
+\(\phi_i(f)\) is the Shapley value of feature \(x_i\).\(S\) is a subset of features, and \(S \subseteq N \setminus \{i\}\) indicates that subset \(S\) contains all features except for \(x_i\).\(f(S)\) is the model's prediction on the feature subset \(S\).
+\(f(S \cup \{i\})\) is the model's prediction on the subset \(S\) and feature \(x_i\).
+\(|S|!\) and \((|N|-|S|-1)!\) are the combinatorial coefficients of the Shapley value, used to weigh the importance of each feature in different feature subsets.
+\(|N|!\) is the total number of permutations of all features in the feature set \(N\), ensuring the average effect across all permutations.
+
+Below are the SHAP Summary Plots for the gold, silver, and bronze medal prediction models.
+
+%三个奖牌的图像
 \begin{figure}[htbp]
@@
 	\begin{subfigure}[b]{.32\textwidth}
-		\includegraphics[width=\textwidth]{img/Decline1.png}
-		\caption{France}\label{subfig:1}
+		\includegraphics[width=\textwidth]{img/shap1.png}
+		\caption{Gold SHAP Summary Plot}\label{subfig:1}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{.32\textwidth}
-		\includegraphics[width=\textwidth]{img/Decline2.png}
-		\caption{Sweden}\label{subfig:2}
+		\includegraphics[width=\textwidth]{img/shap2.png}
+		\caption{Silver SHAP Summary Plot}\label{subfig:2}
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{.32\textwidth}
-		\includegraphics[width=\textwidth]{img/Decline3.png}
-		\caption{Germany}\label{subfig:3}
+		\includegraphics[width=\textwidth]{img/shap3.png}
+		\caption{Bronze SHAP Summary Ploty}\label{subfig:3}
 	\end{subfigure}
-	\caption{Three images}\label{fig:subfigures}
-\end{figure}
+	\caption{SHAP Summary Plots}\label{fig:subfigures}
+\end{figure}
+From the figures, we can see that the SHAP algorithm amplifies the prior probability of winning a particular medal.
+In other words, athletes who have previously won gold medals have a higher probability of winning gold again if they continue to compete, and the same holds true for silver and bronze medalists.
+This differs somewhat from the results obtained through LightGBM's self-analysis; however, both analysis methods assign relatively high weights to Adeptness, Level, and Win Probability.
 
@@
 \subsection{Strengths}
-1.
+1.For medal prediction, we performed complex feature engineering and data mining, resulting in a large dataset.
+LightGBM is highly efficient in training, with fast processing speeds, low memory consumption, and support for parallel and distributed training, making it well-suited for handling large-scale data, aligning well with our dataset.
 
 2.
+The model demonstrates high prediction accuracy, superior performance, and the predicted results align closely with expectations from previous years.
+Additionally, the predictions are consistent with common knowledge and offer high interpretability.
 
 3.
+The model takes into account various indirect factors, such as a country's ranking, the types of sports a country excels in, whether the host is the organizer, athletes' prior competition status, and more.
+These factors enable the model to consider a broader range of real-world conditions, making it more aligned with actual data.
 
 4.
+The Bayesian Change Point Detection used in Task 2 accurately reflects the change points in time-series data.
+Our tests showed that the change points in the performance of China and the United States women's volleyball teams coincided with the coaching periods of Lang Ping, demonstrating the model's accuracy.
 \subsection{Weaknesses}
-1.
+1.Since the training data includes a large amount of historical data (spanning over 50 years), the prediction results are susceptible to the influence of historical data, leading to potential errors.
 
@@
 		\item Task1
-
-	 \qquad AA\\
-	bbb
-
-	\item Task2\\
-	\qquad AAA
-	\item Task3\\
-	\qquad AAA
-
-	\item Task4\\
-	\qquad AAA
+ We performed data preprocessing and feature engineering on the provided dataset, using the KMeans++ clustering algorithm to determine the ranking of each country.
+We calculated various feature variables, including each country's proficiency in different sports, the host nation advantage, and the performance level of different athletes.
+
+ \qquad Ultimately, we used the LightGBM gradient boosting regression algorithm to predict the expected medal count for each athlete from each country participating in the 2028 Olympics.
+By aggregating these predictions, we obtained the total medal count for each country.
+
+\qquad The model indicates that the United States is expected to show progress, while France will experience a significant decline, likely due to the home-field advantage of the host nation.
+Additionally, due to annual fluctuations in events, countries like Australia and Japan are expected to see an increase in their medal count, while Italy and South Korea will experience a decrease.
+China's medal count is projected to remain stable.
+
+\qquad For countries that have never won a medal, we analyzed past events in which these countries participated but did not secure any medals.
+If future events are expected to expand the number of available medals, we reason that these countries may have a higher probability of winning their first medal in 2028.
+Through quantitative analysis, we identified Sierra Leone, Antigua and Barbuda, and Papua New Guinea as the countries with the highest likelihood of winning their first medal in 2028.
+
+\qquad For events where certain countries have clear advantages, we performed a correlation analysis across countries at different levels and calculated the Spearman correlation coefficient between changes in total medal count and medal distribution, as well as changes in the medal structure for those events.
+We found that for countries with strong overall events adeptness, such as China, the influence of dominant events on their total ranking and medal count is minimal, resulting in relatively stable performances.
+However, for smaller countries, their dependence on dominant events is stronger, and their total medal count largely depends on performance in these key events.
+
+	\item Task2
+	To explore the "great coach" effect, we used the Bayesian Changepoint Detection model to analyze the impact of Lang Ping on the Chinese and U.S.
+women's volleyball teams, Béla Károlyi on the U.S.
+and Romanian women's gymnastics teams, and other similar examples.
+By comparing the historical coaching tenure of a coach with the predicted changepoints identified by the model, we found a strong correlation between the changepoints in a country's sports performance and the tenure of a great coach, indicating the significant impact of such coaches.\\
+
+	\qquad 	After establishing the importance of hiring coaches, we selected three representative countries from the level 1 to level 3 countries and applied the CUSUM algorithm to assess their weakest events.
+
+	\qquad We found that sailing was once a strong event for France in early Olympics, with stable results from 1930 to 1970, but a significant decline after the 1970s.
+Sweden dominated athletics and shooting from the 1920s to the 1950s, but these events declined over time, likely due to a decrease in the country's emphasis on sports.
+German swimming, which was not dominant before the 1990s, emerged as a strong contender in the early 21st century, but showed signs of decline in the 2010s and 2020s.
+Based on these findings, we recommend that these countries hire coaches to maintain their competitive edge.
+
+	\item Task3 
+	Using the models and data derived from Task 1 and Task 2, we conducted in-depth data mining and analysis, leading to several key conclusions about the Olympics, including athlete gender ratio, the dominance of certain countries in specific Olympic events, and how changes in medal distribution reflect global geopolitical shifts.
+
+	\qquad Regarding the athlete gender ratio, we found that in the earliest Olympic Games, male athletes and their proportion of total medals dominated.
+However, as gender equality awareness grew, more women began participating in the Olympics, leading to a significant yearly increase in the number of female athletes and a more balanced gender ratio.
+
+	\qquad In terms of the dominance of certain countries in specific Olympic events, we observed that some niche events, unique to particular countries, tend to be dominated by these countries.
+For example, the UK has a dominant position in cricket and motorboating, while Canada excels in lacrosse.
+Thus, national Olympic committees seeking to win more medals should consider investing in these distinctive events, expand their influence, and lobby the International Olympic Committee to include these events in the Olympic program, strengthening their competitive advantage.
+
+	\qquad Moreover, by examining the changes in medal distribution across countries over time, we identified several distinct anomalies, occurring in 1904, 1980, 1984, and 1992.
+These anomalies reflect the evolution of the Olympics from its infancy to maturity, and also highlight the intense geopolitical rivalry during the Cold War.
+From the changes in medal counts across countries, we can gain indirect insights into global political and economic developments.
 

### 2025-01-27 代码/不同运动员服役年限分布.py
图片更新

@@ -63,11 +63,11 @@ peaks, _ = find_peaks(y_vals)
 
 # 在每个峰值位置绘制星号
 for peak in peaks:
-    plt.scatter(x_vals[peak], 0.76, color='#e55756', marker='*', s=200, zorder=5)
+    plt.scatter(1, 0.78, color='#e55756', marker='*', s=200, zorder=5)
 
 
 #宽度变大
-plt.xlim(0, 40)
+plt.xlim(0, 20)
 
 #添加均值线
 plt.axvline(result['Year'].mean(), linestyle='--', linewidth=2,color='#79706e')

### 2025-01-27 论文/PAPER.tex
latex

@@
 
-s
-
-\begin{enumerate}[\bfseries 1.]
-    \item We do ...
-    \item We do ...
-    \item We do ...
-\end{enumerate}
 \section{Question Preparation}
@@
 % 三线表示例
-\begin{table}[!htbp]
-\begin{center}
-\caption{Notations}
-\begin{tabular}{cl}
+
+	\begin{longtable}{cl}
+		\caption{Notations}\label{tb:notation} \\
 		\toprule
@@
 		\midrule
+		\endfirsthead
+
+		\multicolumn{2}{c}%
+		{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+		\toprule
+		\multicolumn{1}{m{3cm}}{\centering Symbol}
+		&\multicolumn{1}{m{8cm}}{\centering Definition}\\
+		\midrule
+		\endhead
+
+		\midrule
+		\multicolumn{2}{r}{\textit{Continued on next page}} \\
+		\endfoot
+
+		\bottomrule
+		\endlastfoot
+
 		$C_{i}$&Certain country\\
@@
 		$M$&Total count of the 3 types of medals\\
-	$A$&Number of new athletes\\
+		$A$&Number of new medals\\
 		$T$&Times of Olympic participations\\
 		$\gamma$&Sport Advantage Coefficient\\
-  	$ m_{c_{i}}$ &Total medal count of a certain country\\
-	$ m_{c_{i},e_{j}}$ &Total medal count of a certain country in a specific event\\
+		$ m_{C_{i}}$ &Total medal count of a certain country\\
+		$ m_{C_{i},E_{j}}$ &Total medal count of a certain country in a specific event\\
 		$L_{i}$&Country clustering level\\
@@
 		$\xi$&The Probability of First Medal\\
-    $\sigma$&                        \\
-    $   $&Normalized version of probability of first medal         \\
-	\bottomrule
-\end{tabular}\label{tb:notation}
-\end{center}
-\end{table}
+		$\sigma$&Standard deviation\\
+		$\kappa$&Normalized version of probability of first medal\\
+	\end{longtable}
 
@@
 
-From the distribution chart, it can be seen that nearly 80% of athletes have participated in 1 or 2 matches, with the average number of serve times being 1.94, meaning each athlete participates in approximately 2 matches.
+From the distribution chart, it can be seen that nearly \( 80\% \)of athletes have participated in 1 or 2 matches, with the average number of serve times being 1.94, meaning each athlete participates in approximately 2 matches.
 Based on this assumption, we consider that each participating athlete will compete in 2 matches on average.
-Additionally, around 80% of athletes have participated in only 1 Olympic Games, while nearly 20% have participated in 2.
-Therefore, we can assume that 20% of the veteran athletes will continue to compete in the next Olympic Games, providing a basis for determining which athletes will continue to participate.
-
-To predict the Participant List, we employed Monte Carlo simulation, which consisted of two parts: the first part involved selecting 20% of veteran athletes to continue competing (20% conforming to the original data distribution), while the second part generated new random athletes based on historical athlete data.
+Additionally, around \( 80\% \) of athletes have participated in only 1 Olympic Games, while nearly \( 20\% \) have participated in 2.
+Therefore, we can assume that \( 20\% \) of the veteran athletes will continue to compete in the next Olympic Games, providing a basis for determining which athletes will continue to participate.
+
+To predict the Participant List, we employed Monte Carlo simulation, which consisted of two parts: the first part involved selecting \( 20\% \)of veteran athletes to continue competing (\( 20\% \) conforming to the original data distribution), while the second part generated new random athletes based on historical athlete data.
 
@@
 The medal expectations were categorized into 3 scenarios: optimistic, moderate, and pessimistic.
-The optimistic expectation was calculated by averaging the top 50% of the team, the moderate expectation by averaging all team members, and the pessimistic expectation by averaging the bottom 50%.
+The optimistic expectation was calculated by averaging the top \( 50\% \) of the team, the moderate expectation by averaging all team members, and the pessimistic expectation by averaging the bottom \( 50\% \).
 
@@
 
-By analyzing the performance of various countries in different events across past Olympic Games, we extracted a feature variable $\gamma$(Event Adeptness Coefficient), to represent the advantages of these countries in certain events..
+By analyzing the performance of various countries in different events across past Olympic Games, we extracted a feature variable $\gamma$(Event Adeptness Coefficient), to represent the advantages of these countries in certain events.
 
@@
 \begin{equation}
-	\gamma = \frac{m_{c_i,e_j}}{\sum m_{c_i,e_j}}
+	\gamma = \frac{m_{C_i,E_j}}{\sum m_{C_i,E_j}}
 \end{equation}
@@
 We input the previously obtained data into LightGBM for iterative model training.
-After training, we input the factors affecting the predictions for the next edition into the model, ultimately obtaining the predicted medal table for the 2028 Summer Olympics in Los Angeles, USA, as follows:
+After training, we input the factors affecting the predictions for the next edition into the model, ultimately obtaining the predicted medal table for the 2028 Summer Olympics in Los Angeles, USA, are shown in Figure \ref{fig:USA}.
 %奖牌榜预测图
@@
 	\caption{USA Medal count prediction}
-	\label{fig:aa}
+	\label{fig:USA}
 \end{figure}
@@
 Here,$\overline{\xi}$ refers to the mean of the original data, and$\sigma$refers to the standard deviation of the original data.
-The calculated results are as follows:
+The calculated results are shown in Figure \ref{fig:First Medal}:
 %首奖可能性图
@@
 	\caption{The Probability of First Medal in 2028}
-	\label{fig:aa}
+	\label{fig:First Medal}
 \end{figure}
@@
 		\includegraphics[width=\textwidth]{img/shap3.png}
-		\caption{Bronze SHAP Summary Ploty}\label{subfig:3}
+		\caption{Bronze SHAP Summary Plot}\label{subfig:3}
 	\end{subfigure}
@@
 		\item Task1
- We performed data preprocessing and feature engineering on the provided dataset, using the KMeans++ clustering algorithm to determine the ranking of each country.
-We calculated various feature variables, including each country's proficiency in different sports, the host nation advantage, and the performance level of different athletes.
-
- \qquad Ultimately, we used the LightGBM gradient boosting regression algorithm to predict the expected medal count for each athlete from each country participating in the 2028 Olympics.
-By aggregating these predictions, we obtained the total medal count for each country.
-
-\qquad The model indicates that the United States is expected to show progress, while France will experience a significant decline, likely due to the home-field advantage of the host nation.
-Additionally, due to annual fluctuations in events, countries like Australia and Japan are expected to see an increase in their medal count, while Italy and South Korea will experience a decrease.
+ we applied data preprocessing and feature engineering, using the KMeans++ clustering algorithm to rank countries based on various features, including proficiency in different sports, host nation advantages, and athlete performance levels.
+The LightGBM regression model predicted the medal count for each country in the 2028 Olympics.
+Our analysis indicated that the United States is likely to progress, while France may decline, largely due to the home-field advantage.
+Countries such as Australia and Japan are expected to see an increase, while Italy and South Korea may experience a decrease.
 China's medal count is projected to remain stable.
-
-\qquad For countries that have never won a medal, we analyzed past events in which these countries participated but did not secure any medals.
-If future events are expected to expand the number of available medals, we reason that these countries may have a higher probability of winning their first medal in 2028.
-Through quantitative analysis, we identified Sierra Leone, Antigua and Barbuda, and Papua New Guinea as the countries with the highest likelihood of winning their first medal in 2028.
-
-\qquad For events where certain countries have clear advantages, we performed a correlation analysis across countries at different levels and calculated the Spearman correlation coefficient between changes in total medal count and medal distribution, as well as changes in the medal structure for those events.
-We found that for countries with strong overall events adeptness, such as China, the influence of dominant events on their total ranking and medal count is minimal, resulting in relatively stable performances.
-However, for smaller countries, their dependence on dominant events is stronger, and their total medal count largely depends on performance in these key events.
+For nations without prior medals, we identified Sierra Leone, Antigua and Barbuda, and Papua New Guinea as those with the highest probability of winning their first medal in 2028.
+Correlation analysis revealed that countries with strong overall performance, like China, show minimal dependence on specific events, while smaller countries are more reliant on key events for their total medal count.
 
 	\item Task2
-	To explore the "great coach" effect, we used the Bayesian Changepoint Detection model to analyze the impact of Lang Ping on the Chinese and U.S.
-women's volleyball teams, Béla Károlyi on the U.S.
-and Romanian women's gymnastics teams, and other similar examples.
-By comparing the historical coaching tenure of a coach with the predicted changepoints identified by the model, we found a strong correlation between the changepoints in a country's sports performance and the tenure of a great coach, indicating the significant impact of such coaches.\\
-
-	\qquad 	After establishing the importance of hiring coaches, we selected three representative countries from the level 1 to level 3 countries and applied the CUSUM algorithm to assess their weakest events.
-
-	\qquad We found that sailing was once a strong event for France in early Olympics, with stable results from 1930 to 1970, but a significant decline after the 1970s.
-Sweden dominated athletics and shooting from the 1920s to the 1950s, but these events declined over time, likely due to a decrease in the country's emphasis on sports.
-German swimming, which was not dominant before the 1990s, emerged as a strong contender in the early 21st century, but showed signs of decline in the 2010s and 2020s.
-Based on these findings, we recommend that these countries hire coaches to maintain their competitive edge.
-
+ we explored the "great coach" effect using the Bayesian Changepoint Detection model.
+We found a strong correlation between coaching tenures and significant changes in a country’s sports performance.
+Additionally, the CUSUM algorithm helped identify weak events for several countries, such as France’s decline in sailing, Sweden’s waning dominance in athletics and shooting, and Germany’s emerging strength in swimming, which later showed signs of decline.
+Based on these findings, we recommend hiring specialized coaches to help maintain or regain competitive advantages in these events.
 	\item Task3
-	Using the models and data derived from Task 1 and Task 2, we conducted in-depth data mining and analysis, leading to several key conclusions about the Olympics, including athlete gender ratio, the dominance of certain countries in specific Olympic events, and how changes in medal distribution reflect global geopolitical shifts.
-
-	\qquad Regarding the athlete gender ratio, we found that in the earliest Olympic Games, male athletes and their proportion of total medals dominated.
-However, as gender equality awareness grew, more women began participating in the Olympics, leading to a significant yearly increase in the number of female athletes and a more balanced gender ratio.
-
-	\qquad In terms of the dominance of certain countries in specific Olympic events, we observed that some niche events, unique to particular countries, tend to be dominated by these countries.
-For example, the UK has a dominant position in cricket and motorboating, while Canada excels in lacrosse.
-Thus, national Olympic committees seeking to win more medals should consider investing in these distinctive events, expand their influence, and lobby the International Olympic Committee to include these events in the Olympic program, strengthening their competitive advantage.
-
-	\qquad Moreover, by examining the changes in medal distribution across countries over time, we identified several distinct anomalies, occurring in 1904, 1980, 1984, and 1992.
-These anomalies reflect the evolution of the Olympics from its infancy to maturity, and also highlight the intense geopolitical rivalry during the Cold War.
-From the changes in medal counts across countries, we can gain indirect insights into global political and economic developments.
-
+ Using the models and data from Task 1 and Task 2, we performed a detailed analysis of several key trends in the Olympics.
+We found that the athlete gender ratio has become more balanced over time, reflecting increasing gender equality.
+Moreover, certain countries dominate niche events, such as the UK in cricket and Canada in lacrosse, which could offer opportunities for Olympic committees to enhance their medal prospects by investing in these specialized events.
+Lastly, our analysis of medal distribution changes over time revealed significant anomalies in 1904, 1980, 1984, and 1992, reflecting the Olympics' evolution and geopolitical shifts, particularly during the Cold War.
+These anomalies provide insights into broader global political and economic changes.
 \end{itemize}

### 2025-01-27 论文/PAPER.tex
论文更新

@@
 
-\subsubsection{Distribution of Countries' Strength Sports}
+\subsubsection{Distribution of Countries' Adept Sports}
 Due to factors such as cultural and geographical environments, countries exhibit distinct advantages in different events.
@@
 %6.2
-\subsection{Strength events}
+\subsection{Dominant Sports}
 
@@
 \begin{itemize}
-		\item Task1
- we applied data preprocessing and feature engineering, using the KMeans++ clustering algorithm to rank countries based on various features, including proficiency in different sports, host nation advantages, and athlete performance levels.
-The LightGBM regression model predicted the medal count for each country in the 2028 Olympics.
+		\item \textbf{Task1}
+
+ we applied data preprocessing and feature engineering, using the \textbf{KMeans++} clustering algorithm to rank countries based on various features, including proficiency in different sports, host nation advantages, and athlete performance levels.
+The \textbf{LightGBM} regression model predicted the medal count for each country in the 2028 Olympics.
 Our analysis indicated that the United States is likely to progress, while France may decline, largely due to the home-field advantage.
@@
 China's medal count is projected to remain stable.
-For nations without prior medals, we identified Sierra Leone, Antigua and Barbuda, and Papua New Guinea as those with the highest probability of winning their first medal in 2028.
+For nations without prior medals, we identified \textbf{Sierra Leone}, \textbf{Antigua and Barbuda}, and \textbf{Papua New Guinea} as those with the highest probability of winning their first medal in 2028.
 Correlation analysis revealed that countries with strong overall performance, like China, show minimal dependence on specific events, while smaller countries are more reliant on key events for their total medal count.
 
-	\item Task2
- we explored the "great coach" effect using the Bayesian Changepoint Detection model.
+	\item \textbf{Task2}
+
+ we explored the "great coach" effect using the \textbf{Bayesian Changepoint Detection} model.
 We found a strong correlation between coaching tenures and significant changes in a country’s sports performance.
-Additionally, the CUSUM algorithm helped identify weak events for several countries, such as France’s decline in sailing, Sweden’s waning dominance in athletics and shooting, and Germany’s emerging strength in swimming, which later showed signs of decline.
+Additionally, the \textbf{CUSUM} algorithm helped identify weak events for several countries, such as France’s decline in sailing, Sweden’s waning dominance in athletics and shooting, and Germany’s emerging strength in swimming, which later showed signs of decline.
 Based on these findings, we recommend hiring specialized coaches to help maintain or regain competitive advantages in these events.
-	\item Task3
- Using the models and data from Task 1 and Task 2, we performed a detailed analysis of several key trends in the Olympics.
-We found that the athlete gender ratio has become more balanced over time, reflecting increasing gender equality.
-Moreover, certain countries dominate niche events, such as the UK in cricket and Canada in lacrosse, which could offer opportunities for Olympic committees to enhance their medal prospects by investing in these specialized events.
-Lastly, our analysis of medal distribution changes over time revealed significant anomalies in 1904, 1980, 1984, and 1992, reflecting the Olympics' evolution and geopolitical shifts, particularly during the Cold War.
+	\item \textbf{Task3}
+
+ Using the models and data from Task 1 and Task 2, we performed a \textbf{detailed analysis} of several key trends in the Olympics.
+We found that the athlete \textbf{gender ratio} has become more balanced over time, reflecting increasing gender equality.
+Moreover, certain countries dominate \textbf{niche events}, such as the UK in cricket and Canada in lacrosse, which could offer opportunities for Olympic committees to enhance their medal prospects by investing in these specialized events.
+Lastly, our analysis of medal distribution changes over time revealed significant anomalies in 1904, 1980, 1984, and 1992, reflecting the Olympics' evolution and \textbf{geopolitical shifts}, particularly during the Cold War.
 These anomalies provide insights into broader global political and economic changes.
@@
 \begin{thebibliography}{99}
-\bibitem{1} Einstein, A., Podolsky, B., \& Rosen, N. (1935). Can quantum-mechanical description of physical reality be considered complete?. \emph{Physical review}, 47(10), 777.
-\bibitem{2} \emph{A simple, easy \LaTeX\ template for MCM/ICM: EasyMCM}. (2018). Retrieved December 1, 2019, from\url{https://www.cnblogs.com/xjtu-blacksmith/p/easymcm.html}
+\bibitem{1}R. Prescott Adams, D.J.C. MacKay Bayesian Online Changepoint Detection 
+\emph{Technical Report}, (2007)
+\bibitem{2}G. Ke, Q. Meng, T. Finley, T. Wang, W. Chen, W. Ma, et al.
+LightGBM: a highly efficient gradient boosting decision tree
+\emph{Proceedings of the 31st International Conference on Neural Information Processing Systems}. (2017), pp. 3149-3157
+\bibitem{3}Arthur, D., \& Vassilvitskii, S. . K-means++: The advantages of careful seeding.
+\emph{Proceedings of the Annuual ACM-SIAM Symposium on Discrete Algorithms}.(2007)8, 1027-1035. 10.1145/1283383.1283494.
+\bibitem{4}Mosca, Edoardo, Ferenc, Szigeti, Stella, et al.
+TragianniSHAP-based explanation methods: A review for NLP interpretability
+\emph{In Proceedings of the 29th International Conference on Computational Linguistics}.2022
+
+\bibitem{5}Seiler S. Evaluating the (your country here) Olympic medal count.
+\emph{Int J Sport Physiol Perform.}.2013;8:203–10.
+
 \end{thebibliography}
@@
 
-% Python 代码示例
-\begin{lstlisting}[language=Python, name={test.py}]
-# Python code example
-for i in range(10):
-    print('Hello, world!')
+% C++ 代码示例
+\begin{lstlisting}[language=Python, name={LightGBM.py}]
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+data=pd.read_csv('./data/train_data.csv')
+X=data.iloc[:,0:-3]
+Y=data.iloc[:,-3:]
+
+X.fillna(0,inplace=True)
+from sklearn.preprocessing import StandardScaler
+scaler=StandardScaler()
+X=scaler.fit_transform(X)
+columns=['host','med_d_ath','adept','lvl','win_prob','G_prob','S_prob','B_prob','lose_prob']
+from sklearn.preprocessing import PolynomialFeatures
+poly=PolynomialFeatures(degree=2)
+
+X=poly.fit_transform(X)
+new_columns=poly.get_feature_names_out(input_features=columns)
+X=pd.DataFrame(X,columns=new_columns)
+import lightgbm as lgb
+from sklearn.model_selection import train_test_split
+models=['Gold','Silver','Bronze']
+performances=[]
+i=0
+for modelName in models:
+Y=data[modelName]
+X_train,X_test,Y_train,Y_test=
+(X,Y,test_size=0.2,random_state=0)
+model=lgb.LGBMRegressor()
+model.fit(X_train,Y_train)
+Y_predict=model.predict(X_test)
+from sklearn.metrics import mean_squared_error
+mse=mean_squared_error(Y_test,Y_predict)
+Y_predict=np.round(Y_predict)
+from sklearn.metrics import mean_squared_error
+rmse=mean_squared_error(Y_test,Y_predict)**0.5
+from sklearn.metrics import mean_absolute_error
+mae=mean_absolute_error(Y_test,Y_predict)
+from sklearn.metrics import r2_score
+r2=r2_score(Y_test,Y_predict)
+performances.append([modelName,mse,rmse,mae,r2])
+print(modelName+' MSE:',mse)
+print(modelName+' RMSE:',rmse)
+print(modelName+' MAE:',mae)
+print(modelName+' R2:',r2)
+
 \end{lstlisting}
 
-% MATLAB 代码示例
-\begin{lstlisting}[language=MATLAB, name={test.m}]
-% MATLAB code example
-for i = 1:10
-    disp("hello, world!");
-end
-\end{lstlisting}
-
-% C++ 代码示例
-\begin{lstlisting}[language=C++, name={test.cpp}]
-// C++ code example
-#include <iostream>
-using namespace std;
-
-int main() {
-    for (int i = 0; i < 10; i++)
-        cout << "hello, world" << endl;
-    return 0;
-}
-\end{lstlisting}
-
 \end{subappendices}  % 附录内容结束

### 2025-01-27 论文/PAPER.tex
latex

@@
 	\centering
-	\includegraphics[width=12cm]{img/Level1.png}
-	\caption{Scatter plot of national level classification (based on Kmeans++clustering algorithm)}
+	\includegraphics[width=16cm]{img/da.png}
+	\caption{Flow Chart of Our Work}
 	\label{fig:aa}
@@
 		$T$&Times of Olympic participations\\
+		$T$&Total count of events\\
 		$\gamma$&Sport Advantage Coefficient\\
@@
 	\centering
-	\begin{subfigure}[b]{.55\textwidth}
+	\begin{subfigure}[b]{.48\textwidth}
 		\includegraphics[width=\textwidth]{img/Times.png}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{.4\textwidth}
+	\begin{subfigure}[b]{.51\textwidth}
 		\includegraphics[width=\textwidth]{img/Years.png}
@@
 	\end{subfigure}
-	\caption{Two images}\label{fig:subfigures}
+	\caption{Athlete Service Status}\label{fig:subfigures}
 \end{figure}
@@
 
+And the steps of our LightGBM model are as below:
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=12cm]{img/xiao.png}
+	\caption{LightGBM Model flow Chart}
+	\label{fig:aa}
+\end{figure}
 The prediction of the Olympic medal table is essentially a multi-task learning problem, with the goal of predicting the number of gold, silver, and bronze medals each country is likely to win in different events.
@@
 	\includegraphics[width=12cm]{img/Predict.png}
-	\caption{Medal count prediction}
+	\caption{Medal Count Prediction}
 	\label{fig:aa}
@@
 Therefore, for countries that have never won a medal before, we calculate their first medal index $\xi$.
-%公式 未知
+
+\begin{equation}
+	\xi = \sum_{i=1}^{n} \left( T_{E_i} \ast A_{E_i} \right)
+\end{equation}
 
@@
 		\centering
-		\includegraphics[width=14cm]{img/Gender with Award.png}
+		\includegraphics[width=12cm]{img/Gender with Award.png}
 		\caption{Gender Distribution of Athletes(with Award)}
@@
 		\centering
-		\includegraphics[width=14cm]{img/Gender.png}
+		\includegraphics[width=12cm]{img/Gender.png}
 		\caption{Gender Distribution of Athletes}
@@
 
+\clearpage
+\begin{letter}{\centering \underline{\textbf{Report on Use of AI}}}
+
+	\begin{itemize}
+		\setlength{\parsep}{0ex} %段落间距
+		\setlength{\topsep}{2ex} %列表到上下文的垂直距离
+		\setlength{\itemsep}{1ex} %条目间距
+		\item[1.]  \textbf{OpenAI ChatGPT (Dec 1, 2022 version, ChatGPT-4)}
+
+		\subitem\textbf{Query1: }What aspects should I modify the drawing logic without changing the code logic, so that the icons can be very flashy and eye-catching
+
+		\subitem\textbf{Purpose: }Some drawing logic is based on AI suggestions, which allows us to make our drawings more beautiful.
+
+		\subitem\textbf{Output: }To make the drawing more flashy, you can enhance the visual effect of the chart by adjusting the styles of colors, lines, markers, and other elements.
+Here are some modification suggestions:Color and Style: Use more vivid and contrasting colors and lines.
+For example, you can try using more gradients and transparency in the colors of curves and points.Marking points: You can try using larger and more eye-catching marking points, or use different marking shapes.Line type and line weight: Try using different line types and line weights to make the chart more exaggerated.
+You have already used dynamic line weights in the code, and you can further adjust or add other elements.Background and Grid: Modify the color and style of the background and grid lines to better match the overall style.Annotations and Text: Add more annotations, text, or arrows to highlight key information in the chart.\\
+
+		\subitem\textbf{Query2: }Is there a recommended tennis dataset source that includes detailed information about each serve of a player, such as the first and second hand, score, running distance, and serving posture?
+CSV format required
+
+		\subitem\textbf{Purpose: }We attempted to inquire with AI about machine learning datasets for tennis matches, and AI provided several related websites.
+Unfortunately, we ultimately did not find any high-quality data available.
+
+		\subitem\textbf{Output: }As of my knowledge deadline (January 2022), I am unable to provide specific tennis dataset links.
+However, you can try searching for tennis datasets in the following places:ATP official website: ATP (Association of Tennis Professionals) may provide some official tennis datasets.
+You can search for relevant statistics and data on its website.The official website of ITF: The International Tennis Federation (ITF) may also provide some tennis datasets.
+Check their official website to see if there is any information you need.Kaggle: Kaggle is a data science competition platform where users sometimes share various datasets, including sports data.
+You can search for relevant tennis datasets on Kaggle.UCI Machine Learning Library: UCI machine learning libraries typically provide various types of datasets, including sports related data.
+You can check their website to see if there is a tennis dataset that suits your needs.GitHub: Some developers and researchers may share their collected tennis datasets on GitHub.
+You can search on GitHub and see if there are any projects that meet your requirements.Please ensure that you comply with relevant laws and regulations regarding data usage, and review the license agreement for the dataset to ensure that you have the right to use it.
+Also, remember to check if the dataset contains the specific information you need, such as first and last, score, running distance, and serving posture.
+	\end{itemize}
+\end{letter}
+
 \end{subappendices}  % 附录内容结束

### 2025-01-27 论文/PAPER.tex
1

@@
 	The findings indicate that countries with strong overall sports performance exhibit lower reliance on specific events, yielding stable results, while weaker nations depend more on select events.
-In certain cases, the \textbf{correlation coefficient} in athletics reached \textbf{0.894}, reflecting a concentration of athletic development in specific areas.
+In certain cases, the \textbf{correlation} in athletics reached \textbf{0.894}, reflecting a concentration of athletic development in specific areas.
 
@@
 \subsection{Problem Background}
-During the 2024 Paris Summer Olympics, fans not only paid attention to the individual events but also showed significant interest in the the ranking of countries on the medal table.
-Ultimately, the United States topped the medal table with a total of 126 medals, while China and the United States are tied for first place in the number of gold medals, each securing 40 golds.
+During the 2024 Paris Summer Olympics, fans not only paid attention to the individual events but also showed significant interest in the ranking of countries on the medal table.
+Ultimately, the United States topped the medal table with a total of 126 medals, while China and the United States are tied for first in the number of gold medals, each securing 40 golds.
 The host country, France ranks 5th in the total number of gold medals with 16 gold medals, but finished 4th in the total medal count.
@@
 While predictions of the final medal counts at the Olympics are common, such forecasts are generally not based on historical medal tables.
-Instead, they are typically made before the start of the upcoming Olympic Games, once the list of competing athletes is known.To clarify the task, the problem is restated as follows:
+Instead, they are typically made before the start of the upcoming Olympic Games, once the list of competing athletes is known.
+To clarify the task, the problem is restated as follows:
 
@@
 	\setlength{\itemsep}{1ex} %条目间距
-	\item Develop a model for each country’s medal count, which should at least include the number of gold medals and the total medal count, and estimate the uncertainty/precision of the model,also evaluate its performance.
+	\item Develop a model for each country’s medal count, which should at least include the number of gold medals and the total medal count, and estimate the uncertainty/precision of the model and evaluate its performance.
 		\begin{itemize}
 		\item[1)]
-Using the model, predict the medal standings for the 2028 Los Angeles Summer Olympics, including prediction intervals for all outcomes.
+Using the model, predict the medal standings for the 2028 Los Angeles Summer Olympics (including prediction intervals for all outcomes).
 Based on the model’s predictions, identify which countries are most likely to improve their performance and which countries are expected to perform worse than in the 2024.
@@
 		\item[3)]
-The model should also consider the number and types of events in each specific Olympic Games, exploring the relationship between the events and the number of medals won by each country.
-For each country, determine which events are most crucial and why, as well as the impact of the country’s selected events on the results.
+The model should also consider the number and types of events in each specific Olympic Games, exploring the relationship between the events and the number of medals won by each country, as well as the impact of the events selected by the country on the results.
 	\end{itemize}
@@
 	\item In contrast to athletes, who must change their citizenship in order to represent different countries in competitions, coaches do not need to change their citizenship to coach, which makes it easier for them to move to other countries.
-As a result, the “great coach” effect may arise.
+As a result, the great coach effect may arise.
 For example, Lang Ping has coached the volleyball teams of both China and the U.S., leading both to championships, while Bela Karolyi coached the Romanian and U.S.
@@
 The task is to identify evidence in the data that may suggest changes driven by the "great coach" effect and estimate its impact on the medal count.
-Select 3 countries, determine the events in which they should consider investing in "great" coaches, and estimate the potential impact of such investments.
+Select 3 countries, determine the events in which they should consider investing in "great" coaches, and estimate the impact of such investments
 	\item Explain the unique insights regarding Olympic medal counts that are included in the developed model and how these insights can provide valuable information to the National Olympic Committees of various countries.
@@
 
-\section{Task2:A "Great Coach" Effect}
-\subsection{Verification of the "Great Coach" Effect}
-The "Great Coach" effect can cause significant differences in the performance of relevant countries in corresponding events.
+\section{Task2:Great Coach Effect}
+\subsection{Verification of the Great Coach Effect}
+The Great Coach effect can cause significant differences in the performance of relevant countries in corresponding events.
 To collect evidence of changes caused by this effect, we use a Bayesian Changepoint Detection (BEAST) model.
@@
 
-This allows us to determine how much influence these "great coaches" had on the medal counts achieved by these countries in the relevant events during the periods when Lang Ping coached the Chinese and U.S.
+This allows us to determine how much influence these great coaches had on the medal counts achieved by these countries in the relevant events during the periods when Lang Ping coached the Chinese and U.S.
 volleyball teams, and when Bela Karolyi coached the Romanian and U.S.
@@
 In addition, we also studied other similar cases.
-Therefore, we can conclude that the "great coach" effect has a significant impact on a country's medal count in the corresponding event.
+Therefore, we can conclude that the great coach effect has a significant impact on a country's medal count in the corresponding event.
 
 \subsection{Countries Recommended for Hiring Coaches}
-After confirming the significant impact of the "great coach" on the medal count, we began to analyze which events a country should consider investing in "excellent coaches." For this, we use the CUSUM algorithm.
+After confirming the significant impact of the great coach on the medal count, we began to analyze which events a country should consider investing in "excellent coaches." For this, we use the CUSUM algorithm.
 
@@
 
-Based on the previously confirmed "great coach" effect, if other countries wish to enhance their capabilities in these events and win more medals, they may consider hiring coaches from these dominant countries.
+Based on the previously confirmed great coach effect, if other countries wish to enhance their capabilities in these events and win more medals, they may consider hiring coaches from these dominant countries.
 
@@
 
- we explored the "great coach" effect using the \textbf{Bayesian Changepoint Detection} model.
+ we explored the great coach effect using the \textbf{Bayesian Changepoint Detection} model.
 We found a strong correlation between coaching tenures and significant changes in a country’s sports performance.

### 2025-01-27 论文/PAPER.tex
latex

--- 2025-01-27 论文/PAPER.tex
@@
 
+\clearpage
 \section{Appendix B: Program Codes}
@@
 
-		\subitem\textbf{Query2: }Is there a recommended tennis dataset source that includes detailed information about each serve of a player, such as the first and second hand, score, running distance, and serving posture?
-CSV format required
-
-		\subitem\textbf{Purpose: }We attempted to inquire with AI about machine learning datasets for tennis matches, and AI provided several related websites.
-Unfortunately, we ultimately did not find any high-quality data available.
-
-		\subitem\textbf{Output: }As of my knowledge deadline (January 2022), I am unable to provide specific tennis dataset links.
-However, you can try searching for tennis datasets in the following places:ATP official website: ATP (Association of Tennis Professionals) may provide some official tennis datasets.
-You can search for relevant statistics and data on its website.The official website of ITF: The International Tennis Federation (ITF) may also provide some tennis datasets.
-Check their official website to see if there is any information you need.Kaggle: Kaggle is a data science competition platform where users sometimes share various datasets, including sports data.
-You can search for relevant tennis datasets on Kaggle.UCI Machine Learning Library: UCI machine learning libraries typically provide various types of datasets, including sports related data.
-You can check their website to see if there is a tennis dataset that suits your needs.GitHub: Some developers and researchers may share their collected tennis datasets on GitHub.
-You can search on GitHub and see if there are any projects that meet your requirements.Please ensure that you comply with relevant laws and regulations regarding data usage, and review the license agreement for the dataset to ensure that you have the right to use it.
-Also, remember to check if the dataset contains the specific information you need, such as first and last, score, running distance, and serving posture.
+		\subitem\textbf{Query2: }Ways to make the abstract and sections of the paper more concise while maintaining an academic tone.
+
+		\subitem\textbf{Purpose: }We attempted to to refine the abstract and sections of the paper to be more concise, ensuring that the content remains academically rigorous and effectively communicates the research findings, methods, and significance.
+
+		\subitem\textbf{Output: }Focus on the core objectives, methods, results, and implications of the study.
+Use clear and concise language to summarize the research without unnecessary details.Clearly state the research question or hypothesis and its significance.
+Avoid extensive background information that does not directly relate to the research focus.Methods: Describe the research design and procedures succinctly.
+Include only essential details that are necessary for replication or understanding of the study.
+Results: Present findings in a straightforward manner, emphasizing key outcomes.
+Avoid repetitive explanations of data that are self-evident from the figures or tables.Discussion: Concentrate on interpreting the results and their implications.
+Avoid speculative or tangential discussions that do not directly relate to the study's findings.Conclusion: Summarize the main findings and their significance concisely.
+Avoid restating information already covered in the abstract or introduction.Example: Before: "We performed data preprocessing and feature engineering on the provided dataset, using the KMeans++ clustering algorithm to determine the ranking of each country."After: "We preprocessed data using KMeans++ to rank countries."
 	\end{itemize}

### 2025-01-27 论文/PAPER.tex
Update PAPER.tex

--- 2025-01-27 论文/PAPER.tex
@@
 	\includegraphics[width=16cm]{img/da.png}
-	\caption{Flow Chart of Our Work}
+	\caption{Workflow of Our Methodology}
 	\label{fig:aa}
@@
 \textbf{Assumption 2 } \textit{Each year, a number of new athletes join the Olympic Games, some of whom may be competing for the first time.
-The specific proportion of these athletes will be estimated through our simulation.
+The specific proportion of these athletes wDue to the systematic nature of athlete training and the relative consistency of competition environments, their performance tends to remain stable.
+By mitigating the impact of outliers, the model can avoid being influenced by extreme values.
+ill be estimated through our simulation.
 }
 
+Due to the inclusion of new athletes each year and the replacement of older ones, in order to predict the medal count for the next Olympic Games, we need to simulate the new athletes based on historical athlete data using algorithms.
+
+\textbf{Assumption 3} \textit{ The performance variability of athletes is assumed to be limited, with minimal occurrences of exceptional overperformance or underperformance.  }
+
 The performance variability of athletes is assumed to be limited, with minimal occurrences of exceptional overperformance or underperformance.
-
-\textbf{Assumption 3} \textit{ The performance variability of athletes is assumed to be limited, with minimal occurrences of exceptional overperformance or underperformance.  }
-
-The performance variability of athletes is assumed to be limited, with minimal occurrences of exceptional overperformance or underperformance.  
-Due to the systematic nature of athlete training and the relative consistency of competition environments, their performance tends to remain stable.
-By mitigating the impact of outliers, the model can avoid being influenced by extreme values.
 
@@
 \subsection{Basic Data Preprocessing}
-Due to various influencing factors, there are significant differences in the competitive levels of countries in the Olympic Games, which have been reflected in past competitions, specifically in the total number of gold, silver, and bronze medals won by each country.
-
-To illustrate the differences in the levels of countries in previous Olympic Games (i.e.
-national level), we employed the KMeans++ clustering algorithm.
-Based on the number of gold, silver, and bronze medals, as well as the total medal count of each country in past Olympics, we classified the countries into five levels.
-These five levels, L1, L2, L3, L4, and L5, form a partition of the sample set X (the total number of gold, silver, and bronze medals won by countries in previous Olympic Games).
+Due to the diverse factors influencing competition outcomes, there are significant differences in the competitive levels of countries in the Olympic Games, which have been reflected in past competitions, specifically in the total number of gold, silver, and bronze medals won by each country.
+
+To demonstrate the differences in the levels of countries in previous Olympic Games (i.e.
+national level), we employed the KMeans++ algorithm.
+Based on the number of gold, silver, and bronze medals, as well as the total medal count of each country in past Olympics, we categorized the countries into five levels.
+These 5 levels, L1, L2, L3, L4, and L5, form a partition of the sample set X (the total number of gold, silver, and bronze medals won by countries in previous Olympic Games).
 \begin{equation}
@@
 \subsection{Strengths}
-1.For medal prediction, we performed complex feature engineering and data mining, resulting in a large dataset.
+1.
+For medal prediction, we performed complex feature engineering and data mining, resulting in a large dataset.
 LightGBM is highly efficient in training, with fast processing speeds, low memory consumption, and support for parallel and distributed training, making it well-suited for handling large-scale data, aligning well with our dataset.
@@
 \subsection{Weaknesses}
-1.Since the training data includes a large amount of historical data (spanning over 50 years), the prediction results are susceptible to the influence of historical data, leading to potential errors.
+1. Since the training data includes a large amount of historical data (spanning over 50 years), the prediction results are susceptible to the influence of historical data, leading to potential errors.
 

### 2025-01-27 论文/PAPER.tex
1

@@
 \usepackage{longtable}
+\usepackage{float}
 %\usepackage{tabu}
@@
 \subsection{Our work}
-We preprocess the data provided before analyzing matches and mainly utilize 3 models. The specific work was as follows
-\begin{figure}[htbp]
+We preprocess the data provided before analyzing matches and mainly utilize 3 models. The specific work was as follows.
+\begin{figure}[H]
 	\centering
@@
 After the classification, the distribution of countries across the 5 levels is shown in the figures:
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 Then, we compiled the distribution of the times of participations and the distribution of athlete tenure based on historical data, as shown in the figure.
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 And the steps of our LightGBM model are as below:
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 
-$y_i$denotes the true value.
-$\hat{y}_i^{(m-1)}$is the current model's predicted value.
-$\hat{y}_i^{(m-1)}$+$\eta f_m(x_i)$is the model's predicted value at the m-th step during the gradient boosting model update process.
-$\Omega(f_m)$ Regularization term, which prevents overfitting of the model and controls the complexity of the trees.
+$y_i$ denotes the true value.
+$\hat{y}_i^{(m-1)}$ is the current model's predicted value.
+$\hat{y}_i^{(m-1)}$ +$\eta f_m(x_i)$ is the model's predicted value at the m-th step during the gradient boosting model update process.
+$\Omega(f_m)$ is the regularization term, which prevents overfitting of the model and controls the complexity of the trees.
 
@@
 %奖牌榜预测图
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 \end{equation}
+
 Here,$\overline{\xi}$ refers to the mean of the original data, and$\sigma$refers to the standard deviation of the original data.
@@
 %首奖可能性图
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 %三个国家擅长项目的图
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 %雷达图
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 %5.1 排球
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 %三个国家某项目衰弱 需要教练图
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 	%6.1 男女比例图
-	\begin{figure}[htbp]
+	\begin{figure}[H]
 		\centering
@@
 
-	\begin{figure}[htbp]
+	\begin{figure}[H]
 		\centering
@@
 %6.3 花里胡哨图
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 %三个奖牌的图像
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering

### 2025-01-27 论文/PAPER.tex
1

@@
 	\centering
-	\includegraphics[width=12cm]{img/Percentage.jpg}
+	\includegraphics[width=8cm]{img/Percentage.jpg}
 	\caption{Percentage of Medals of Different Sports in China}
@@
 \subsection{Medal Standings}
-Numerous factors influence the medal table.
-To predict the medal standings for the next Olympics, we incorporated factors identified during the data preprocessing stage, including nation level, the list of participating athletes, each country's adeptness in specific events, and adjustments to medal counts.
-
-Additionally, as host countries typically benefit from home advantage, the factor of "whether a country is the host"or "whether hosting for the first time" was also considered.
-This factor was categorized into 3 categories and quantified for inclusion in the model.
-Ultimately, these five factors were collectively summarized as \textbf{National Background Factors}.
+The medal table is influenced by various factors.
+To predict the standings for the next Olympics, we considered key factors identified during data preprocessing, such as nation level, participating athletes, country-specific event strengths, and adjustments to medal counts.
+
+Additionally, we accounted for the host country's advantage, including whether a country is the host or hosting for the first time, categorizing and quantifying this factor into three categories for the model.
+These five factors were collectively termed \textbf{National Background Factors}.
 
@@
 	\centering
-	\includegraphics[width=12cm]{img/xiao.png}
+	\includegraphics[width=11cm]{img/xiao.png}
 	\caption{LightGBM Model flow Chart}
@@
 	\centering
-	\includegraphics[width=12cm]{img/Predict.png}
+	\includegraphics[width=11cm]{img/Predict.png}
 	\caption{Medal Count Prediction}
@@
 	\centering
-	\includegraphics[width=14cm]{img/Sensitive Analysis 1.png}
+	\includegraphics[width=13cm]{img/Sensitive Analysis 1.png}
 	\caption{LightGBM Feature Importance}

### 2025-01-27 论文/PAPER.tex
1

@@
 		\item[1)]
-Using the model, predict the medal standings for the 2028 Los Angeles Summer Olympics (including prediction intervals for all outcomes).
+Using the model, predict the medal table for the 2028 Los Angeles Summer Olympics (including prediction intervals for all outcomes).
 Based on the model’s predictions, identify which countries are most likely to improve their performance and which countries are expected to perform worse than in the 2024.
@@
 women’s gymnastics teams, achieving great success.
-The task is to identify evidence in the data that may suggest changes driven by the "great coach" effect and estimate its impact on the medal count.
+The task is to identify evidence in the data that may suggest changes driven by the great coach effect and estimate its impact on the medal count.
 Select 3 countries, determine the events in which they should consider investing in "great" coaches, and estimate the impact of such investments
@@
 The total medal count of a country more accurately reflects the long-term investments and developmental outcomes in sports, rather than short-term results that can be drastically altered.
-Furthermore, external factors that influence medal counts, such as the organization of international competitions, rule changes, and judging standards, tend to remain relatively stable in the short term.
+Furthermore, \textbf{external factors} that influence medal counts, such as the organization of international competitions, rule changes, and judging standards, tend to remain relatively stable in the short term.
 
@@
 		\toprule
-		\multicolumn{1}{m{3cm}}{\centering Symbol}
-		&\multicolumn{1}{m{8cm}}{\centering Definition}\\
+		\multicolumn{1}{m{4cm}}{\centering Symbol}
+		&\multicolumn{1}{m{13cm}}{\centering Definition}\\
 		\midrule
@@
 To demonstrate the differences in the levels of countries in previous Olympic Games (i.e.
-national level), we employed the KMeans++ algorithm.
+national level), we employed the \textbf{KMeans++} algorithm.
 Based on the number of gold, silver, and bronze medals, as well as the total medal count of each country in past Olympics, we categorized the countries into five levels.
@@
 	\includegraphics[width=12cm]{img/Level1.png}
-	\caption{Scatter plot of national level classification (based on Kmeans++clustering algorithm)}
+	\caption{Scatter plot of national level classification (based on KMeans++ clustering algorithm)}
 	\label{fig:aa}
@@
 
-In addition, we created 10 new features based on the original variables, which were utilized during the modeling process with the LightGBM model.
+In addition, we created 10 new features based on the original variables, which were utilized during the modeling process with the \textbf{LightGBM} model.
 
@@
 \subsection{Data Mining}
-\subsubsection{Athlete Service Status}
+\subsubsection{Participant List Prediction}
 To predict future scenarios, we analyzed the trends in the number of participants for each country, event and year, and applied \textbf{Linear Regression} for fitting.
@@
 
-From the distribution chart, it can be seen that nearly \( 80\% \)of athletes have participated in 1 or 2 matches, with the average number of serve times being 1.94, meaning each athlete participates in approximately 2 matches.
-Based on this assumption, we consider that each participating athlete will compete in 2 matches on average.
+From the distribution chart, it can be seen that nearly \( 80\% \) of athletes have participated in 1 or 2 matches, with the average number of serve times being 1.94, meaning each athlete participates in approximately 2 matches.
+Based on this assumption, we consider that each participating athlete will compete in \textbf{2 matches on average}.
 Additionally, around \( 80\% \) of athletes have participated in only 1 Olympic Games, while nearly \( 20\% \) have participated in 2.
@@
 
-To predict the Participant List, we employed Monte Carlo simulation, which consisted of two parts: the first part involved selecting \( 20\% \)of veteran athletes to continue competing (\( 20\% \) conforming to the original data distribution), while the second part generated new random athletes based on historical athlete data.
+To predict the Participant List, we employed Monte Carlo simulation, which consisted of two parts: the first part involved selecting \( 20\% \) of veteran athletes to continue competing (\( 20\% \) conforming to the original data distribution), while the second part generated new random athletes based on historical athlete data.
 
@@
 For a given country in a specific event, the average number of medals won by all athletes serves as the standard number of medals for a representative athlete.
-The medal expectations were categorized into 3 scenarios: optimistic, moderate, and pessimistic.
+The medal expectations were categorized into 3 scenarios: \textbf{optimistic}, \textbf{moderate}, and \textbf{pessimistic}.
 The optimistic expectation was calculated by averaging the top \( 50\% \) of the team, the moderate expectation by averaging all team members, and the pessimistic expectation by averaging the bottom \( 50\% \).
@@
 
-By analyzing the performance of various countries in different events across past Olympic Games, we extracted a feature variable $\gamma$(Event Adeptness Coefficient), to represent the advantages of these countries in certain events.
+By analyzing the performance of various countries in different events across past Olympic Games, we extracted a feature variable $\gamma$ (\textbf{Event Adeptness Coefficient}), to represent the advantages of these countries in certain events.
 
@@
 Since the IOC makes adjustments to events each year, the total number of medals awarded in each event does not remain exactly the same each year.
-To address this, we applied \textbf Linear Regression to fit the number of gold, silver, and bronze medals awarded in each event across past Olympic Games and predicted the medal distribution for the upcoming Olympic Games, providing a reference for subsequent operations.
+To address this, we applied\textbf{ Linear Regression} to fit the number of gold, silver, and bronze medals awarded in each event across past Olympic Games and predicted the medal distribution for the upcoming Olympic Games, providing a reference for subsequent operations.
 
 \section{Task1:Medal Prediction Model Based on LightGBM}
-\subsection{Medal Standings}
+\subsection{Medal Table}
 The medal table is influenced by various factors.
@@
 
-And the steps of our LightGBM model are as below:
+And the steps of our \textbf{LightGBM} model are as below:
 \begin{figure}[H]
@@
 	\includegraphics[width=11cm]{img/xiao.png}
-	\caption{LightGBM Model flow Chart}
+	\caption{LightGBM Model Flow Chart}
 	\label{fig:aa}
@@
 
-Building on GBDT, LightGBM accelerates the computation using histograms, optimizing training efficiency and enabling the fast processing of high-dimensional, sparse, large-scale data.
-Compared to traditional logistic regression, LightGBM can capture nonlinear relationships through tree splitting, offering a performance advantage in accurately handling complex data and nonlinear relationships, significantly improving accuracy.
+Building on \textbf{GBDT}, LightGBM accelerates the computation using histograms, optimizing training efficiency and enabling the fast processing of high-dimensional, sparse, large-scale data.
+Compared to traditional logistic regression, LightGBM can capture \textbf{nonlinear relationships} through tree splitting, offering a performance advantage in accurately handling complex data and nonlinear relationships, significantly improving accuracy.
 Additionally, it can automatically handle missing values, providing great convenience for data preprocessing.
@@
 \end{equation}
-The optimized loss function based on GBDT is represented as squared error in the medal prediction regression task.
+
+The optimized loss function based on GBDT is represented as \textbf{squared error} in the medal prediction regression task.
 
@@
 We input the previously obtained data into LightGBM for iterative model training.
-After training, we input the factors affecting the predictions for the next edition into the model, ultimately obtaining the predicted medal table for the 2028 Summer Olympics in Los Angeles, USA, are shown in Figure \ref{fig:USA}.
+After training, we input the factors affecting the predictions for the next edition into the model, ultimately obtaining the predicted medal table for the 2028 Summer Olympics in Los Angeles, USA, are shown in Figure \ref{fig:aa}.
 %奖牌榜预测图
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=12cm]{img/OP1.png}
-	\caption{USA Medal count prediction}
-	\label{fig:USA}
-\end{figure}
-
-According to the model's predictions, the United States is expected to see a significant increase in medal count compared to the previous year, while France will experience a notable decrease, which is related to the home-field advantage of the host country.
+According to the model's predictions, the United States is expected to see a significant increase in medal count compared to the previous year, while France will experience a notable decrease, which is related to the \textbf{home-field advantage} of the host country.
 Additionally, due to changes in the number of medals for certain events, the medal counts for Australia, Japan, and the Netherlands are expected to rise, while Italy and South Korea will see a decline.
@@
 
-To more accurately simulate the actual number of medals won, we simplify each individual into 3 parameters: the probabilities of winning gold, silver, and bronze medals.
+To more accurately simulate the actual number of medals won, we simplify each individual into 3 parameters: \textbf{the probabilities of winning gold, silver, and bronze medals}.
 For a specific country and event, the average number of medals won by all team members represents the probability that a standard "virtual athlete" should have.
@@
 The "Previous Participants Record" serves as the basis for the Monte Carlo simulation, which consists of two parts: the first part involves selecting \( 20\% \) of veteran athletes to continue competing (with \( 20\% \) corresponding to the original data distribution), and the second part uses historical athlete data to generate new random athletes.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=12cm]{img/OP1.png}
+	\caption{USA Medal Count Prediction}
+	\label{fig:USA}
+\end{figure}
 
@@
 
-Therefore, for countries that have never won a medal before, we calculate their first medal index $\xi$.
+Therefore, for countries that have never won a medal before, we calculate their \textbf{first medal index} $\xi$.
 
@@
 
-The number of competitions is counted from the original dataset, and the expected increase in the number of medals for the next edition is predicted through a Linear Regression model based on historical data.
+The number of competitions is counted from the original dataset, and the expected increase in the number of medals for the next edition is predicted through a \textbf{Linear Regression model} based on historical data.
 
@@
 
-In order to visualize the accuracy of a country's first medal prediction, we normalized the first medal index using the Z-score and then multiplied it by 0.8 to obtain the first medal coefficient $\kappa$.
+In order to visualize the accuracy of a country's first medal prediction, we normalized the first medal index using the \textbf{Z-score} and then multiplied it by 0.8 to obtain the first medal coefficient $\kappa$.
 
@@
 
-Here,$\overline{\xi}$ refers to the mean of the original data, and$\sigma$refers to the standard deviation of the original data.
+Here,$\overline{\xi}$ refers to the mean of the original data, and $\sigma$ refers to the standard deviation of the original data.
 The calculated results are shown in Figure \ref{fig:First Medal}:
@@
 
-As shown in the figure, Sierra Leone (SLE), Antigua and Barbuda (ANT), and Papua New Guinea (PNG) are the three countries most likely to win their first medal in the next Olympic Games, with accuracies approximately 0.8, 0.77, and 0.74, respectively.
+As shown in the figure, \textbf{Sierra Leone (SLE)}, \textbf{Antigua and Barbuda (ANT)}, and \textbf{Papua New Guinea (PNG)} are the three countries most likely to win their first medal in the next Olympic Games, with accuracies approximately 0.8, 0.77, and 0.74, respectively.
 
@@
 
+Here, $d_i$ is the rank difference of the two variables for the i-th data point. 
+Next, we compute the \textbf{Spearman's Rank Correlation Coefficient} ($R_s$).
+
 \begin{equation}
@@
 \end{equation}
-
-Here, $d_i$ is the rank difference of the two variables for the iii-th data point. 
-Next, we compute the Spearman's Rank Correlation Coefficient ($R_s$).
 
@@
 	\end{subfigure}
-	\caption{Three images}\label{fig:subfigures}
+	\caption{Heatmap of Correlation}\label{fig:subfigures}
 \end{figure}
@@
 We found that although China has a significant advantage in table tennis, the relationship between the development of the event and China's total medal count is relatively weak.
-This suggests that China's overall athletic adeptness is stable and less influenced by a single dominant event.
+This suggests that China's overall athletic adeptness is \textbf{stable} and less influenced by a single dominant event.
 
 Additionally, Jamaica's total medal count shows a strong positive correlation with its performance in athletics, indicating the country's heavy reliance on athletics competitions.
-Since athletics is a well-established and stable event with minimal fluctuations in the number of events held each year, the relationship between the number of events and Jamaica's total medal count is relatively weak.
+Since athletics is a well-established and stable event with minimal fluctuations in the number of events held each year, the relationship between the number of events and Jamaica's total medal count is \textbf{relatively weak}.
 
@@
 However, unlike Jamaica, rowing is not as established as athletics, and the number of competitions fluctuates from year to year.
-As a result, New Zealand's overall medal count is highly dependent on the rise and fall of rowing's prominence.
+As a result, New Zealand's overall medal count is highly \textbf{dependent} on the rise and fall of rowing's prominence.
 \subsection{Model Performances}
 
-We calculated four evaluation metrics: Mean Squared Error (MSE), Root Mean Squared Error (RMSE), Mean Absolute Error (MAE), and the Coefficient of Determination (\(\mathbf{R}^2\)).
+We calculated four evaluation metrics: Mean Squared Error (\textbf{MSE}), Root Mean Squared Error (\textbf{RMSE}), Mean Absolute Error (\textbf{MAE}), and the Coefficient of Determination (\(\mathbf{R}^2\)).
 
@@
 The Great Coach effect can cause significant differences in the performance of relevant countries in corresponding events.
-To collect evidence of changes caused by this effect, we use a Bayesian Changepoint Detection (BEAST) model.
+To collect evidence of changes caused by this effect, we use a \textbf{Bayesian Changepoint Detection (BEAST)} model.
 
@@
 
-Using Bayes' theorem, we can compute the posterior probability for each possible change point $c_k$:
+Using Bayes' theorem, we can compute the \textbf{posterior probability} for each possible change point $c_k$:
 
@@
 \subsection{Countries Recommended for Hiring Coaches}
-After confirming the significant impact of the great coach on the medal count, we began to analyze which events a country should consider investing in "excellent coaches." For this, we use the CUSUM algorithm.
+After confirming the significant impact of the great coach on the medal count, we began to analyze which events a country should consider investing in great coaches.
+For this, we use the \textbf{CUSUM} algorithm.
 
@@
 
-Firstly, the gender ratio in the Olympics has become increasingly balanced, with the male-to-female ratio nearly equal, shifting from a male-dominated ratio to approximately 1:1.
+Firstly, the \textbf{gender ratio} in the Olympics has become increasingly \textbf{balanced}, with the male-to-female ratio nearly equal, shifting from a male-dominated ratio to approximately 1:1.
 The number of female athletes has steadily increased over time, particularly in the late 20th and early 21st centuries, with a more pronounced growth trend.
@@
 
-In analyzing the national strengths in specific events, we found that certain countries have a dominant advantage, even to the point of forming a dominance, with their share of the total medal count reaching as high as \( 30\% \), \( 50\% \), or even over \( 80\% \).
+In analyzing the national strengths in specific events, we found that certain countries have a \textbf{dominant advantage}, even to the point of forming a dominance, with their share of the total medal count reaching as high as \( 30\% \), \( 50\% \), or even over \textbf{\( 80\% \)}.
 
@@
 	\includegraphics[width=16cm]{img/Monopolized Sports.png}
-	\caption{Adeptness of Countries in Specitific Project}
+	\caption{Adeptness of Countries in Specific Event}
 	\label{fig:aa}
@@
 
-Based on the previously confirmed great coach effect, if other countries wish to enhance their capabilities in these events and win more medals, they may consider hiring coaches from these dominant countries.
+Based on the previously confirmed \textbf{great coach effect}, if other countries wish to enhance their capabilities in these events and win more medals, they may consider hiring coaches from these dominant countries.
 
@@
 
-Sensitivity Analysis is used to evaluate the sensitivity of model outputs to changes in input features.
+\textbf{Sensitivity Analysis} is used to evaluate the sensitivity of model outputs to changes in input features.
 Through this analysis, we can quantify the dependency of final prediction results prediction outcomes on specific data features, such as the adeptness of a particular country in a specific event or the previous award probability of an athlete.
@@
 LightGBM comes with a feature importance function that identifies the features with the greatest impact on the model’s predictions.
-By using plot\_importance() function, we can visualize the importance of each feature.
+By using \textbf{\textit{plot\_importance()}} function, we can visualize the importance of each feature.
 
@@
 Furthermore, we can use Shapley value analysis to assess the model's sensitivity.
-SHAP (SHapley Additive exPlanations) is a game theory-based model explanation method used to interpret machine learning model predictions.
+\textbf{SHAP} (\textbf{SH}apley \textbf{A}dditive ex\textbf{P}lanations) is a game theory-based model explanation method used to interpret machine learning model predictions.
 It assigns each feature a contribution to the model's prediction, helping us understand the importance and influence of each feature in the given prediction result.The formula for Shapley value is as follows:
@@
 
-\(\phi_i(f)\) is the Shapley value of feature \(x_i\).\(S\) is a subset of features, and \(S \subseteq N \setminus \{i\}\) indicates that subset \(S\) contains all features except for \(x_i\).\(f(S)\) is the model's prediction on the feature subset \(S\).
-\(f(S \cup \{i\})\) is the model's prediction on the subset \(S\) and feature \(x_i\).
-\(|S|!\) and \((|N|-|S|-1)!\) are the combinatorial coefficients of the Shapley value, used to weigh the importance of each feature in different feature subsets.
-\(|N|!\) is the total number of permutations of all features in the feature set \(N\), ensuring the average effect across all permutations.
+\textbf{\(\phi_i(f)\)} is the Shapley value of feature \textbf{\(x_i\).\(S\)} is a subset of features, and \(S \subseteq N \setminus \{i\}\) indicates that subset \textbf{\(S\)} contains all features except for \textbf{\(x_i\).\(f(S)\)} is the model's prediction on the feature subset \textbf{\(S\)}.
+\textbf{\(f(S \cup \{i\})\)} is the model's prediction on the subset \textbf{\(S\)} and feature \textbf{\(x_i\)}.
+
+\textbf{\(|S|!\) }and \textbf{\((|N|-|S|-1)!\)} are the \textbf{combinatorial coefficients} of the Shapley value, used to weigh the importance of each feature in different feature subsets.
+\textbf{\(|N|!\)} is the total number of permutations of all features in the feature set \textbf{\(N\)}, ensuring the average effect across all permutations.
 
@@
 
- we applied data preprocessing and feature engineering, using the \textbf{KMeans++} clustering algorithm to rank countries based on various features, including proficiency in different sports, host nation advantages, and athlete performance levels.
+We applied data preprocessing and feature engineering, using the \textbf{KMeans++} clustering algorithm to rank countries based on various features, including proficiency in different sports, host nation advantages, and athlete performance levels.
+
 The \textbf{LightGBM} regression model predicted the medal count for each country in the 2028 Olympics.
@@
 Countries such as Australia and Japan are expected to see an increase, while Italy and South Korea may experience a decrease.
+
 China's medal count is projected to remain stable.
@@
 
- we explored the great coach effect using the \textbf{Bayesian Changepoint Detection} model.
+We explored the great coach effect using the \textbf{Bayesian Changepoint Detection} model.
 We found a strong correlation between coaching tenures and significant changes in a country’s sports performance.
+
 Additionally, the \textbf{CUSUM} algorithm helped identify weak events for several countries, such as France’s decline in sailing, Sweden’s waning dominance in athletics and shooting, and Germany’s emerging strength in swimming, which later showed signs of decline.
@@
 
- Using the models and data from Task 1 and Task 2, we performed a \textbf{detailed analysis} of several key trends in the Olympics.
+The models and data from Task 1 and Task 2, we performed a \textbf{detailed analysis} of several key trends in the Olympics.
 We found that the athlete \textbf{gender ratio} has become more balanced over time, reflecting increasing gender equality.
+
 Moreover, certain countries dominate \textbf{niche events}, such as the UK in cricket and Canada in lacrosse, which could offer opportunities for Olympic committees to enhance their medal prospects by investing in these specialized events.

### 2025-01-27 论文/PAPER.tex
1

@@
 
-	In \textbf{Task 2}, we explored the "great coach effect" by applying \textbf{Bayesian Change Point Detection (BEAST)} to analyze instances from multiple countries.
-The study found a significant correlation between the points of inflection in some countries' sports performance and the tenure of a "great coach," validating the importance of this effect.
+	In \textbf{Task 2}, we explored the "great coach" effect by applying \textbf{Bayesian Change Point Detection (BEAST)} to analyze instances from multiple countries.
+The study found a significant correlation between the points of inflection in some countries' sports performance and the tenure of a "great coach", validating the importance of this effect.
 
@@
 
-By analyzing the performance of various countries in different events across past Olympic Games, we extracted a feature variable $\gamma$ (\textbf{Event Adeptness Coefficient}), to represent the advantages of these countries in certain events.
+By analyzing the performance of various countries in different sports across past Olympic Games, we extracted a feature variable $\gamma$ (\textbf{Event Adeptness Coefficient}), to represent the advantages of these countries in certain events.
 
@@
 
-By extracting features, we mined the level of expertise of each country in different events within the dataset, such as China's performance across various events, as shown in the figure below:
+By extracting features, we mined the level of expertise of each country in different events within the dataset, such as China's performance across various sports, as shown in the figure below:
 
@@
 
-\section{Task1:Medal Prediction Model Based on LightGBM}
+\section{Task 1:Medal Prediction Model Based on LightGBM}
 \subsection{Medal Table}
@@
 
-The optimized loss function based on GBDT is represented as \textbf{squared error} in the medal prediction regression task.
+The optimized loss function based on \textbf{GBDT}\cite{2} is represented as \textbf{squared error} in the medal prediction regression task.
 
@@
 \begin{longtable}{l|l|l|l|l} 
-	\caption{Model Performances(LightGBM)}\\ 
+	\caption{Model Performances (LightGBM)}\\ 
 	\hline
@@
 
-\section{Task2:Great Coach Effect}
+\section{Task 2:Great Coach Effect}
 \subsection{Verification of the Great Coach Effect}
@@
 
-Using Bayes' theorem, we can compute the \textbf{posterior probability} for each possible change point $c_k$:
+Using Bayes' theorem\cite{1}, we can compute the \textbf{posterior probability} for each possible change point $c_k$:
 
@@
 	\includegraphics[width=12cm]{img/Volleyball.png}
-	\caption{Medal Count of Women's Volleyball Teams(CHN vs USA) Over Time}
+	\caption{Medal Count of Women's Volleyball Teams (CHN vs USA) Over Time}
 	\label{fig:aa}
@@
 	\end{subfigure}
-	\caption{Three images}\label{fig:subfigures}
+	\caption{Declining Sports in Different Countries}\label{fig:subfigures}
 \end{figure}
@@
 
-\section{Task3:Other Original Insights}
+\section{Task 3:Other Original Insights}
 
@@
 
-LightGBM comes with a feature importance function that identifies the features with the greatest impact on the model’s predictions.
+LightGBM comes with a feature importance function that identifies the features with the greatest impact on the model’s predictions\cite{2}.
 By using \textbf{\textit{plot\_importance()}} function, we can visualize the importance of each feature.
@@
 
-Furthermore, we can use Shapley value analysis to assess the model's sensitivity.
+Furthermore, we can use Shapley value analysis\cite{4} to assess the model's sensitivity.
 \textbf{SHAP} (\textbf{SH}apley \textbf{A}dditive ex\textbf{P}lanations) is a game theory-based model explanation method used to interpret machine learning model predictions.
-It assigns each feature a contribution to the model's prediction, helping us understand the importance and influence of each feature in the given prediction result.The formula for Shapley value is as follows:
+It assigns each feature a contribution to the model's prediction, helping us understand the importance and influence of each feature in the given prediction result.
+The formula for Shapley value is as follows:
 
@@
 \end{figure}
-From the figures, we can see that the SHAP algorithm amplifies the prior probability of winning a particular medal.
+From the figures, we can see that the SHAP algorithm amplifies the prior probability of winning a particular medal\cite{4}.
 In other words, athletes who have previously won gold medals have a higher probability of winning gold again if they continue to compete, and the same holds true for silver and bronze medalists.
@@
 4.
-The Bayesian Change Point Detection used in Task 2 accurately reflects the change points in time-series data.
+The Bayesian Change Point Detection used in Task 2 accurately reflects the change points in time-series data\cite{1}.
 Our tests showed that the change points in the performance of China and the United States women's volleyball teams coincided with the coaching periods of Lang Ping, demonstrating the model's accuracy.
@@
 
-We applied data preprocessing and feature engineering, using the \textbf{KMeans++} clustering algorithm to rank countries based on various features, including proficiency in different sports, host nation advantages, and athlete performance levels.
+We applied data preprocessing and feature engineering, using the \textbf{KMeans++} clustering algorithm\cite{3} to rank countries based on various features, including proficiency in different sports, host nation advantages, and athlete performance levels.
 
@@
 \clearpage
-\section{Appendix B: Program Codes}
-Here are the program codes we used in our research.
+\section{Appendix B: LightGBM Training Codes}
+Here are the codes we used in our LightGBM model training.
 
@@
 X=scaler.fit_transform(X)
-columns=['host','med_d_ath','adept','lvl','win_prob','G_prob','S_prob','B_prob','lose_prob']
+columns=['host','med_d_ath','adept','lvl','win_prob',
+'G_prob','S_prob','B_prob','lose_prob']
 from sklearn.preprocessing import PolynomialFeatures

### 2025-01-27 论文/PAPER.tex
LAST

@@
 
-\title{Together, Individuals Make a Difference}  % 标题
+\title{Individuals Make a Difference:
+
+	An Olympics Medal Prediction Model Based on LightGBM}  % 标题
 
@@
 
-\subsection{Our work}
+\subsection{Our Work}
 We preprocess the data provided before analyzing matches and mainly utilize 3 models. The specific work was as follows.
@@
 \end{equation}
+
 After the classification, the distribution of countries across the 5 levels is shown in the figures:
@@
 
-\section{Task 1:Medal Prediction Model Based on LightGBM}
+\section{Task 1: Medal Prediction Model Based on LightGBM}
 \subsection{Medal Table}
@@
 We input the previously obtained data into LightGBM for iterative model training.
-After training, we input the factors affecting the predictions for the next edition into the model, ultimately obtaining the predicted medal table for the 2028 Summer Olympics in Los Angeles, USA, are shown in Figure \ref{fig:aa}.
+After training, we input the factors affecting the predictions for the next edition into the model, ultimately obtaining the predicted medal table for the 2028 Summer Olympics in Los Angeles, USA, are shown in the figure as follows.
 %奖牌榜预测图
@@
 
-\section{Task 2:Great Coach Effect}
+\section{Task 2: Great Coach Effect}
 \subsection{Verification of the Great Coach Effect}
@@
 
-\section{Task 3:Other Original Insights}
+\section{Task 3: Other Original Insights}
 
@@
 \begin{itemize}
-		\item \textbf{Task1}
+		\item \textbf{Task 1}
 
@@
 
-	\item \textbf{Task2}
+	\item \textbf{Task 2}
 
@@
 Based on these findings, we recommend hiring specialized coaches to help maintain or regain competitive advantages in these events.
-	\item \textbf{Task3}
+	\item \textbf{Task 3}
 
